---
title: "fixing data and topic modelling"
author: "Ole Magnus"
format: html
editor: visual
---

# Packages

```{r}

library(data.table)
library(stringi)
library(quanteda)
library(topicmodels)
library(stopwords)
library(ggplot2)
```

# LOAD BASE DATASETS

```{r}

# Convert to data.table
mentions  <- as.data.table(lenta_experts_trf_1999_2024_mentions)
articles  <- as.data.table(lenta_news_1999_2024_translated_all)

# Ensure date formats
mentions[, DateParsed := as.Date(DateParsed)]
articles[, date := as.Date(date)]

# Sanity check: ID alignment

all(unique(mentions$row_id) %in% unique(articles$orig_row_id))


```

# a better filter

```{r}

library(data.table)
library(data.table)
setDT(mentions)

# Ensure numeric
mentions[, mention_country_confidence := as.numeric(mention_country_confidence)]

# Keep only usable country evidence
country_evidence <- mentions[
  !is.na(expert_id) &
  mention_country != "Unknown" &
  !is.na(mention_country_confidence)
]

# Expert master country = country with highest confidence
# (If ties, pick the one appearing most often among tied max)
expert_master_country <- country_evidence[
  ,
  {
    maxc <- max(mention_country_confidence, na.rm = TRUE)
    top <- .SD[mention_country_confidence == maxc]
    # tie-break: most frequent among the max-confidence mentions
    best_country <- top[, .N, by = mention_country][order(-N)][1, mention_country]
    .(expert_country_master = best_country, expert_country_maxconf = maxc)
  },
  by = expert_id
]

CONF_THRESH <- 0.70

mentions <- merge(
  mentions,
  expert_master_country,
  by = "expert_id",
  all.x = TRUE
)

mentions[, mention_country_confidence := as.numeric(mention_country_confidence)]

mentions[, country_final := fifelse(
  mention_country != "Unknown" & !is.na(mention_country_confidence) & mention_country_confidence >= CONF_THRESH,
  mention_country,
  expert_country_master
)]

# If still NA, set to Unknown for clarity
mentions[is.na(country_final), country_final := "Unknown"]

# ── NEW: track where country_final came from ───────────────────────────────────
mentions[, country_final_source := fcase(
  
  # Article-level evidence was strong enough on its own
  mention_country != "Unknown" &
    !is.na(mention_country_confidence) &
    mention_country_confidence >= CONF_THRESH,
  "article_level",
  
  # Majority vote kicked in but master country has high confidence
  # (expert appears many times with strong evidence elsewhere in corpus)
  !is.na(expert_country_master) &
    expert_country_maxconf >= CONF_THRESH,
  "majority_vote_high_conf",
  
  # Majority vote kicked in but master country confidence is low
  # (expert rarely appears with strong evidence)
  !is.na(expert_country_master) &
    expert_country_maxconf > 0 &
    expert_country_maxconf < CONF_THRESH,
  "majority_vote_low_conf",
  
  # Majority vote kicked in but confidence is zero
  # (never had any direct evidence anywhere in corpus, pure frequency)
  !is.na(expert_country_master) &
    expert_country_maxconf == 0,
  "majority_vote_zero_conf",
  
  default = "unknown"
)]
# ──────────────────────────────────────────────────────────────────────────────

mentions[, is_foreign_final := country_final != "Russia" & country_final != "Unknown"]

mentions <- mentions[
  person != "Unknown" &
  country_final != "Unknown"
]

# Check distribution
mentions[, .N, by = country_final_source][
  order(-N)
][, pct := N / sum(N) * 100][] %>%
  print()
fwrite(mentions, "mentions_dataset_for_sentiment.csv")

# After the overwrite, effective confidence for each row is:
# - mention_country_confidence if article_level
# - expert_country_maxconf if majority_vote

mentions[, effective_confidence := fcase(
  country_final_source == "article_level",           mention_country_confidence,
  country_final_source == "majority_vote_high_conf", expert_country_maxconf,
  country_final_source == "majority_vote_low_conf",  expert_country_maxconf,
  default = NA_real_
)]

mentions[, conf_tier := fcase(
  effective_confidence == 0,                                        "Low",
  effective_confidence > 0  & effective_confidence < 0.70,         "Medium",
  effective_confidence >= 0.70 & effective_confidence < 0.85,      "High",
  effective_confidence >= 0.85,                                     "Very high",
  default = NA_character_
)]

mentions[, .N, by = .(conf_tier, effective_confidence)][order(effective_confidence)] %>% print()

# Check total rows in mentions after filtering
nrow(mentions)

# And distribution
mentions[, .N, by = conf_tier][order(conf_tier)]
```

### Testing low confidence removal

```{r}
library(dplyr)

cat("Raw mentions (before any filtering):\n")
print(nrow(lenta_experts_trf_1999_2024_mentions))

cat("\nPerson == Unknown:\n")
print(sum(lenta_experts_trf_1999_2024_mentions$person == "Unknown", na.rm = TRUE))

cat("\nPerson is NA:\n")
print(sum(is.na(lenta_experts_trf_1999_2024_mentions$person)))

cat("\nPerson != Unknown and not NA:\n")
n_with_person <- sum(
  lenta_experts_trf_1999_2024_mentions$person != "Unknown" & 
  !is.na(lenta_experts_trf_1999_2024_mentions$person)
)
print(n_with_person)

cat("\nDropped at country stage (had person, not in final dataset):\n")
print(n_with_person - nrow(mentions))

cat("\nFinal dataset:\n")
print(nrow(mentions))

```

```{r}

# Get the dropped rows - had person but not in final dataset
dropped <- lenta_experts_trf_1999_2024_mentions %>%
  filter(person != "Unknown") %>%
  anti_join(mentions, by = "row_id")

cat("Dropped rows - mention_country distribution:\n")
dropped %>%
  count(mention_country) %>%
  mutate(pct = n / sum(n) * 100) %>%
  arrange(desc(n)) %>%
  print(n = 20)

cat("\nDropped rows - mention_country_confidence distribution:\n")
dropped %>%
  count(mention_country_confidence) %>%
  mutate(pct = n / sum(n) * 100) %>%
  arrange(desc(n)) %>%
  print()

cat("\nDropped rows - mention_country_sources distribution:\n")
dropped %>%
  count(mention_country_sources) %>%
  mutate(pct = n / sum(n) * 100) %>%
  arrange(desc(n)) %>%
  print(n = 20)

cat("Difference between named-person rows and dropped + final:\n")
print(119456 - 37101 - 76938)

cat("Top 30 most frequent persons in dropped rows:\n")
dropped %>%
  count(person) %>%
  arrange(desc(n)) %>%
  print(n = 30)

cat("\nRandom sample of 30 names from dropped rows:\n")
dropped %>%
  distinct(person) %>%
  sample_n(30) %>%
  print()
```

# FILTER VALID EXPERT MENTIONS

# DIRECT MERGE VIA ROW_ID (NO STRING MATCHING)

```{r}

final_data <- merge(
  mentions,
  articles[, .(orig_row_id, text_en, title_en, date)],
  by.x = "row_id",
  by.y = "orig_row_id",
  all.x = TRUE
)


final_data_verify <- merge(
  articles[, .(orig_row_id, text_en, title_en, date)],
  mentions,
  by.x = "orig_row_id",
  by.y = "row_id",
  all.x = TRUE
)

# Remove any unexpected NAs
final_data <- final_data[!is.na(text_en)]
```

# BUILD ARTICLE-LEVEL DATASET

```{r}

article_level <- final_data[
  ,
  .(
    DateParsed = first(DateParsed),
    text_en    = first(text_en),
    title_en   = first(title_en),
    n_mentions = .N,
    mention_sentences = paste(unique(sentence), collapse = " ||| ")
  ),
  by = row_id
]

article_level[, doc_text := paste(title_en, text_en, sep = ". ")]

fwrite(article_level, "article_level_clean.csv")
```

# HARD-NEWS TOPIC MODELLING (TEST 4 CLEAN VERSION)

## Hard-News Filtering

```{r}


article_level[, title_lc := tolower(title_en)]

exclude_pat <- paste0(
  "(",
  paste(c(
    "match","team","league","football","hockey","film","movie","actor",
    "concert","weather","forecast","recipe","diet","fashion","tips"
  ), collapse="|"),
  ")"
)

article_level <- article_level[!stri_detect_regex(title_lc, exclude_pat)]
article_level[, title_lc := NULL]
```

## Tokenization

```{r}

corp <- corpus(article_level$doc_text)

toks <- tokens(
  corp,
  remove_punct = TRUE,
  remove_symbols = TRUE,
  remove_numbers = TRUE
)

toks <- tokens_tolower(toks)

news_stopwords <- c(
  "said","according","earlier","new","one","two",
  "also","can","may","year","years","reported"
)

toks <- tokens_remove(toks, c(stopwords("en"), news_stopwords))

keep_docs <- lengths(toks) > 40
toks <- toks[keep_docs]
article_level <- article_level[keep_docs]
```

## DFM + Trim

```{r}

dfm_all <- dfm_trim(
  dfm_all,
  min_docfreq = 30,
  max_docfreq = 0.6 * ndoc(dfm_all),
  docfreq_type = "count"
)

non_empty <- ntoken(dfm_all) > 0

dfm_all <- dfm_all[non_empty, ]

article_level <- article_level[non_empty]
```

New filtering with better stopwords:

```{r}

# ----------------------------------------------------------
# 1) HARD-NEWS FILTER (Title-based exclusion)
# ----------------------------------------------------------

article_level[, title_lc := tolower(title_en)]

exclude_pat <- paste0(
  "(",
  paste(c(
    # sports
    "match","matches","team","club","coach","league","championship","tournament","football","soccer",
    "hockey","nba","nhl","fifa","olympic","olympics","race","grand prix",
    # culture/entertainment
    "film","movie","cinema","actor","actress","director","singer","concert","album","tv","series",
    "show","theater","theatre","book","novel","literature","festival","premiere","museum",
    # weather
    "weather","forecast","temperature","storm","snow","rain","wind","heat","cold",
    # lifestyle / advice
    "recipe","cook","diet","fitness","beauty","fashion","psychologist","relationship",
    "children","parent","pregnan","doctor recommends","tips","how to"
  ), collapse = "|"),
  ")"
)

article_level <- article_level[!stri_detect_regex(title_lc, exclude_pat)]
article_level[, title_lc := NULL]

gc()

# ----------------------------------------------------------
# 2) Tokenization
# ----------------------------------------------------------

corp <- corpus(article_level$doc_text)

toks <- tokens(
  corp,
  remove_punct = TRUE,
  remove_symbols = TRUE,
  remove_numbers = TRUE
)

toks <- tokens_tolower(toks)

# ----------------------------------------------------------
# 3) Stopwords (stronger cleaning)
# ----------------------------------------------------------

news_stopwords <- c(
  "said","according","earlier","new","one","two","first",
  "also","can","may","time","year","years","reported",
  "found","known","made","way","need","even","many","get","help",
  "people","url","now","however","even","still","today"
)

expert_role_stopwords <- c(
  "expert","experts","specialist","specialists","professor","professors",
  "doctor","doctors","scientist","scientists","researcher","researchers",
  "analyst","analysts","economist","economists","lawyer","lawyers",
  "institute","university","academy","center","centre","department",
  "ministry","director","head"
)

reporting_verbs <- c(
  "said","told","explained","noted","added","stated","called",
  "announced","commented","emphasized","pointed","claimed"
)

toks <- tokens_remove(
  toks,
  c(stopwords("en"),
    news_stopwords,
    expert_role_stopwords,
    reporting_verbs)
)

# Remove ultra-short tokens
toks <- tokens_keep(toks, pattern = "^[a-z]{3,}$", valuetype = "regex")

# ----------------------------------------------------------
# 4) Remove short documents AFTER cleaning
# ----------------------------------------------------------

keep_docs <- lengths(toks) > 50

toks <- toks[keep_docs]
article_level <- article_level[keep_docs]

gc()

# ----------------------------------------------------------
# 5) DFM + Trim
# ----------------------------------------------------------

dfm_all <- dfm(toks)

dfm_all <- dfm_trim(
  dfm_all,
  min_docfreq = 30,
  max_docfreq = 0.6 * ndoc(dfm_all),
  docfreq_type = "count"
)

non_empty <- ntoken(dfm_all) > 0
dfm_all <- dfm_all[non_empty, ]
article_level <- article_level[non_empty]

gc()

```

## LDA

```{r}
dtm <- convert(dfm_all, to = "topicmodels")

K <- 15
set.seed(123)

lda_fit <- LDA(
  dtm,
  k = K,
  method = "Gibbs",
  control = list(iter=1200, burnin=200, thin=100, seed=123)
)

theta <- posterior(lda_fit)$topics
theta_dt <- as.data.table(theta)
setnames(theta_dt, paste0("topic_", 1:K))

hardnews_topics_k15_fast <- cbind(
  article_level[, .(row_id, DateParsed, n_mentions)],
  theta_dt
)
top_terms <- terms(lda_fit, 15)
print(top_terms)

setnames(hardnews_topics_k15_fast,
         old = paste0("topic_", 1:15),
         new = c(
           "macro_economy",
           "media_society",
           "general_news",
           "housing_market",
           "opinion_discourse",
           "covid_health",
           "development_education",
           "energy_sanctions",
           "military_technology",
           "information_services",
           "kremlin_governance",
           "courts_crime",
           "regions_local",
           "ukraine_war",
           "international_geopolitics"
         ))

fwrite(hardnews_topics_k15_fast, "hardnews_topics_k15_fast.csv")
```

## MENTION-LEVEL ±2 SENTENCE CONTEXT WINDOWS

```{r}
results_list <- vector("list", nrow(article_level))

for (i in seq_len(nrow(article_level))) {
  
  full_text <- article_level$text_en[i]
  mentions  <- article_level$mention_sentences[i]
  orig_row_id <- article_level$orig_row_id[i]
  
  if (is.na(full_text) || is.na(mentions)) next
  
  sents <- unlist(stri_split_boundaries(full_text, type = "sentence"))
  sents <- stri_trim_both(sents)
  sents <- sents[nchar(sents) > 0]
  
  mention_list <- unlist(strsplit(mentions, " \\|\\|\\| "))
  mention_list <- stri_trim_both(mention_list)
  
  mention_rows <- list()
  
  for (m in mention_list) {
    
    idx <- which(sents == m)
    if (length(idx) == 0) next
    
    j <- idx[1]
    
    start <- max(1, j - 2)
    end   <- min(length(sents), j + 2)
    
    context_text <- paste(sents[start:end], collapse=" ")
    
    mention_rows[[length(mention_rows)+1]] <- data.table(
      orig_row_id = orig_row_id,
      mention_sentence = m,
      expert_context_text = context_text
    )
  }
  
  if (length(mention_rows) > 0) {
    results_list[[i]] <- rbindlist(mention_rows)
  }
}

expert_mentions_level <- rbindlist(results_list)

fwrite(expert_mentions_level, "expert_mentions_level_hardnews.csv")
```

```{r}

library(data.table)
library(stringi)

setDT(article_level)

# Safety: ensure the key columns exist
stopifnot(all(c("row_id", "text_en", "mention_sentences") %in% names(article_level)))

results_list <- vector("list", nrow(article_level))

for (i in seq_len(nrow(article_level))) {
  
  row_id   <- article_level$row_id[i]
  full_text <- article_level$text_en[i]
  mentions  <- article_level$mention_sentences[i]
  
  if (is.na(full_text) || is.na(mentions)) next
  if (nchar(full_text) < 50 || nchar(mentions) < 5) next
  
  # Split article into sentences
  sents <- unlist(stri_split_boundaries(full_text, type = "sentence"))
  sents <- stri_trim_both(sents)
  sents <- sents[nchar(sents) > 0]
  if (length(sents) == 0) next
  
  # Split mention sentences
  mention_list <- unlist(strsplit(mentions, " \\|\\|\\| "))
  mention_list <- stri_trim_both(mention_list)
  mention_list <- mention_list[nchar(mention_list) > 0]
  if (length(mention_list) == 0) next
  
  mention_rows <- vector("list", length(mention_list))
  out_k <- 0L
  
  for (m in mention_list) {
    
    # Robust match: find sentence(s) that contain m OR where m contains the sentence
    hits1 <- which(stri_detect_fixed(sents, m))
    hits2 <- which(stri_detect_fixed(m, sents))
    idx <- unique(c(hits1, hits2))
    
    if (length(idx) == 0) next
    
    # If multiple hits, choose the closest-length sentence (best match)
    if (length(idx) > 1) {
      lens <- abs(nchar(sents[idx]) - nchar(m))
      j <- idx[which.min(lens)]
    } else {
      j <- idx[1]
    }
    
    # ±2 sentences
    start <- max(1L, j - 2L)
    end   <- min(length(sents), j + 2L)
    
    context_text <- paste(sents[start:end], collapse = " ")
    
    # Cap (optional; keeps embeddings sane)
    if (nchar(context_text) > 3000) {
      context_text <- substr(context_text, 1, 3000)
    }
    
    out_k <- out_k + 1L
    mention_rows[[out_k]] <- data.table(
      row_id = row_id,                 # <-- KEEP THE ID
      mention_sentence = m,
      expert_context_text = context_text
    )
  }
  
  if (out_k > 0L) {
    results_list[[i]] <- rbindlist(mention_rows[1:out_k])
  }
  
  if (i %% 5000 == 0) cat("Processed:", i, "\n")
}

expert_mentions_level <- rbindlist(results_list, use.names = TRUE, fill = TRUE)

# Diagnostics
cat("Rows:", nrow(expert_mentions_level), "\n")
cat("Unique row_id:", length(unique(expert_mentions_level$row_id)), "\n")
print(summary(nchar(expert_mentions_level$expert_context_text)))

# Save
fwrite(expert_mentions_level, "expert_mentions_level_hardnews.csv")

getwd(
)
```

# Merging for full dataset

```{r}

sentiment <- mentions_directed_sentiment_full

topics <- as.data.table(hardnews_topics_k15_fast)

master_dataset <- merge(
  sentiment,
  topics,
  by = "row_id",
  all.x = TRUE
)

sum(is.na(master_dataset$ukraine_war))

topic_cols <- c(
"courts_crime",
"covid_health",
"development_education",
"energy_sanctions",
"general_news",
"housing_market",
"information_services",
"international_geopolitics",
"kremlin_governance",
"macro_economy",
"media_society",
"military_technology",
"opinion_discourse",
"regions_local",
"ukraine_war"
)

master_dataset[topic_cols] <- lapply(master_dataset[topic_cols], function(x) {
  x[is.na(x)] <- 0
  x
})

master_dataset$dominant_topic <- topic_cols[
  max.col(master_dataset[topic_cols], ties.method = "first")
]

table(master_dataset$dominant_topic)

sum(rowSums(master_dataset[topic_cols]) == 0)

master_dataset$dominant_topic[rowSums(master_dataset[topic_cols]) == 0] <- "no_topic"

master_dataset$topic_group <- "other"

master_dataset$topic_group[
master_dataset$dominant_topic %in% c(
"ukraine_war",
"international_geopolitics",
"military_technology",
"energy_sanctions"
)] <- "geopolitics"

master_dataset$topic_group[
master_dataset$dominant_topic %in% c(
"macro_economy",
"housing_market"
)] <- "economy"

master_dataset$topic_group[
master_dataset$dominant_topic %in% c(
"kremlin_governance",
"opinion_discourse",
"media_society"
)] <- "politics"

master_dataset$topic_group[
master_dataset$dominant_topic == "courts_crime"
] <- "crime"


table(master_dataset$topic_group)


master_dataset$anti_west_vs_russia <-
master_dataset$any_anti_west - master_dataset$any_anti_russia

aggregate(anti_west_vs_russia ~ topic_group,
data = master_dataset,
mean)

write.csv(
  master_dataset,
  "C:/Users/olemga/OneDrive - PRIO/Documents/MA Thesis/Methods/Data/expert_topic_sentiment_master.csv",
  row.names = FALSE
)
master_dataset <- expert_topic_sentiment_master

master_dataset$year <- as.integer(format(as.Date(master_dataset$DateParsed.x), "%Y"))

model1 <- lm(
anti_west_vs_russia ~
is_foreign_final +
topic_group +
year,
data = master_dataset
)

summary(model1)

# ------------------------------------------------------------
# CLEAN AND STANDARDIZE MASTER DATASET
# ------------------------------------------------------------

# 1. Standardize variable names
names(master_dataset) <- tolower(names(master_dataset))

# 2. Create clean date variable and remove merge duplicates
master_dataset$date <- as.Date(master_dataset$dateparsed.x)

master_dataset$dateparsed.x <- NULL
master_dataset$dateparsed.y <- NULL

# 3. Create year variable
master_dataset$year <- as.integer(format(master_dataset$date, "%Y"))

# 4. Rename key variables for clarity
names(master_dataset)[names(master_dataset) == "sentence"] <- "mention_sentence"
names(master_dataset)[names(master_dataset) == "country_final"] <- "expert_country"
names(master_dataset)[names(master_dataset) == "is_foreign_final"] <- "foreign_expert"

# 5. Topic columns
topic_cols <- c(
"courts_crime",
"covid_health",
"development_education",
"energy_sanctions",
"general_news",
"housing_market",
"information_services",
"international_geopolitics",
"kremlin_governance",
"macro_economy",
"media_society",
"military_technology",
"opinion_discourse",
"regions_local",
"ukraine_war"
)

# 6. Replace missing topic weights with 0
master_dataset[topic_cols] <- lapply(master_dataset[topic_cols], function(x) {
  x[is.na(x)] <- 0
  x
})

# 7. Create dominant topic
master_dataset$dominant_topic <- topic_cols[
  max.col(master_dataset[topic_cols], ties.method = "first")
]

# 8. Label rows without topic modelling
master_dataset$dominant_topic[rowSums(master_dataset[topic_cols]) == 0] <- "no_topic"

# 9. Rename key sentiment variables
names(master_dataset)[names(master_dataset) == "any_anti_west"] <- "anti_west"
names(master_dataset)[names(master_dataset) == "any_anti_russia"] <- "anti_russia"
names(master_dataset)[names(master_dataset) == "any_anti_ukraine"] <- "anti_ukraine"

# 10. Recreate asymmetry index
master_dataset$anti_west_vs_russia <- master_dataset$anti_west - master_dataset$anti_russia

# 11. Convert important variables to proper types
master_dataset$foreign_expert <- as.integer(master_dataset$foreign_expert)
master_dataset$topic_group <- factor(master_dataset$topic_group)
master_dataset$dominant_topic <- factor(master_dataset$dominant_topic)

# ------------------------------------------------------------
# DATASET IS NOW CLEAN
# ------------------------------------------------------------

```

# Analyses:

share of domestic vs. foreign

```{r}

library(dplyr)
library(ggplot2)

master_dataset %>%
  count(foreign_expert) %>%
  mutate(share = n / sum(n)) %>%
  ggplot(aes(x = factor(foreign_expert, labels = c("Domestic", "Foreign")), y = share)) +
  geom_col() +
  scale_y_continuous(labels = scales::percent) +
  labs(
    x = NULL,
    y = "Share of expert mentions",
    title = "Foreign and domestic experts in the corpus"
  ) +
  theme_minimal()

ggplot(plot_data, aes(x = year, y = share)) +

  # Light raw line (de-emphasized)
  geom_line(color = "#2b6cb0", size = 0.6, alpha = 0.4) +

  # Strong smoothed trend
  geom_smooth(method = "loess",
              se = FALSE,
              color = "black",
              size = 1.2) +

  # Reference line at 50%
  geom_hline(yintercept = 0.5,
             linetype = "dotted",
             color = "grey40") +

  scale_y_continuous(labels = scales::percent,
                     limits = c(0.3, 0.7)) +

  labs(
    x = "Year",
    y = "Share of expert mentions",
    title = "Share of foreign experts over time",
    subtitle = "Foreign experts consistently account for roughly half of expert mentions"
  ) +

  theme_minimal(base_size = 13) +
  theme(
    plot.title = element_text(face = "bold"),
    panel.grid.minor = element_blank()
  )
```

Counts over time

```{r}

library(dplyr)
library(ggplot2)
library(lubridate)
library(scales)

# Prepare data
plot_counts <- master_dataset %>%
  mutate(month = floor_date(date, "month")) %>%
  group_by(month, foreign_expert) %>%
  summarise(n = n(), .groups = "drop") %>%
  mutate(type = ifelse(foreign_expert == 1, "Foreign", "Domestic"))

# Get dynamic y-axis max for annotations
y_max <- max(plot_counts$n, na.rm = TRUE)

# Plot
ggplot(plot_counts, aes(x = month, y = n, color = type)) +

  # Raw monthly lines (light)
  geom_line(size = 0.35, alpha = 0.35) +

  # Smoothed trend (low span to preserve dip)
  geom_smooth(
    se = FALSE,
    size = 1.2,
    span = 0.05
  ) +

  # Vertical lines for key events
  geom_vline(xintercept = as.Date("2014-01-01"),
             linetype = "dashed",
             color = "grey50",
             linewidth = 0.5,
             alpha = 0.7) +

  geom_vline(xintercept = as.Date("2020-03-01"),
             linetype = "dashed",
             color = "grey50",
             linewidth = 0.5,
             alpha = 0.7) +

  geom_vline(xintercept = as.Date("2022-02-24"),
             linetype = "dashed",
             color = "grey50",
             linewidth = 0.5,
             alpha = 0.7) +

  # Labels for events
  annotate("text",
           x = as.Date("2014-01-01"),
           y = y_max * 0.95,
           label = "Editorial change",
           angle = 90,
           vjust = -0.4,
           size = 3,
           color = "grey30") +

  annotate("text",
           x = as.Date("2020-03-01"),
           y = y_max * 0.95,
           label = "COVID-19",
           angle = 90,
           vjust = -0.4,
           size = 3,
           color = "grey30") +

  annotate("text",
           x = as.Date("2022-02-24"),
           y = y_max * 0.95,
           label = "Ukraine invasion",
           angle = 90,
           vjust = -0.4,
           size = 3,
           color = "grey30") +

  # Colors
  scale_color_manual(
    values = c(
      "Domestic" = "#b04a4a",   # muted red
      "Foreign"  = "#2b6cb0"    # blue
    )
  ) +

  # Axis formatting
  scale_y_continuous(labels = comma) +

  # Labels
  labs(
    x = NULL,
    y = "Number of expert mentions",
    color = NULL,
    title = "Number of foreign and domestic expert mentions over time",
    subtitle = "Monthly counts with smoothed trends"
  ) +

  # Theme
  theme_minimal(base_size = 13) +
  theme(
    plot.title = element_text(face = "bold"),
    legend.position = "bottom",
    panel.grid.minor = element_blank()
  )
```

Sentiment by target actor

```{r}
master_dataset %>%
  summarise(
    anti_russia = mean(anti_russia, na.rm = TRUE),
    anti_west = mean(anti_west, na.rm = TRUE),
    anti_ukraine = mean(anti_ukraine, na.rm = TRUE)
  ) %>%
  tidyr::pivot_longer(everything(), names_to = "target", values_to = "rate") %>%
  ggplot(aes(x = target, y = rate)) +
  geom_col() +
  scale_y_continuous(labels = scales::percent) +
  labs(
    x = NULL,
    y = "Share of expert mentions",
    title = "Negative sentiment by target actor"
  ) +
  theme_minimal()



```

Foreign vs domestic experts by target sentiment

```{r}
master_dataset %>%
  group_by(foreign_expert) %>%
  summarise(
    anti_russia = mean(anti_russia, na.rm = TRUE),
    anti_west = mean(anti_west, na.rm = TRUE),
    anti_ukraine = mean(anti_ukraine, na.rm = TRUE)
  ) %>%
  tidyr::pivot_longer(
    cols = c(anti_russia, anti_west, anti_ukraine),
    names_to = "target",
    values_to = "rate"
  ) %>%
  ggplot(aes(x = target, y = rate, fill = factor(foreign_expert, labels = c("Domestic", "Foreign")))) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = scales::percent) +
  labs(
    x = NULL,
    y = "Share of expert mentions",
    fill = NULL,
    title = "Negative sentiment by expert nationality"
  ) +
  theme_minimal()
```

```{r}

library(dplyr)
library(tidyr)
library(ggplot2)
library(scales)

plot_sentiment <- master_dataset %>%
  group_by(foreign_expert) %>%
  summarise(
    Russia = mean(anti_russia, na.rm = TRUE),
    Ukraine = mean(anti_ukraine, na.rm = TRUE),
    West = mean(anti_west, na.rm = TRUE)
  ) %>%
  pivot_longer(
    cols = c(Russia, Ukraine, West),
    names_to = "Target",
    values_to = "Rate"
  ) %>%
  mutate(
    Expert = factor(foreign_expert,
                    levels = c(0, 1),
                    labels = c("Domestic", "Foreign")),
    Target = factor(Target,
                    levels = c("Russia", "Ukraine", "West"))
  )

ggplot(plot_sentiment,
       aes(x = Target, y = Rate, fill = Expert)) +

  geom_col(position = position_dodge(width = 0.7),
           width = 0.6) +

  scale_fill_manual(
    values = c(
      "Domestic" = "#b04a4a",
      "Foreign"  = "#2b6cb0"
    )
  ) +

  scale_y_continuous(
    labels = percent_format(accuracy = 1)
  ) +

  labs(
    x = NULL,
    y = "Share of mentions with negative sentiment",
    fill = NULL,
    title = "Negative sentiment by expert nationality",
    subtitle = "Foreign experts are more likely to express negative sentiment toward Western actors"
  ) +

  theme_minimal(base_size = 13) +
  theme(
    plot.title = element_text(face = "bold"),
    legend.position = "bottom",
    panel.grid.minor = element_blank()
  )
```

Negative sentiment by topic group

```{r}

master_dataset %>%
  group_by(topic_group) %>%
  summarise(
    anti_russia = mean(anti_russia, na.rm = TRUE),
    anti_west = mean(anti_west, na.rm = TRUE),
    anti_ukraine = mean(anti_ukraine, na.rm = TRUE)
  ) %>%
  tidyr::pivot_longer(
    cols = c(anti_russia, anti_west, anti_ukraine),
    names_to = "target",
    values_to = "rate"
  ) %>%
  ggplot(aes(x = topic_group, y = rate, fill = target)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = scales::percent) +
  labs(
    x = NULL,
    y = "Share of expert mentions",
    fill = "Target",
    title = "Negative sentiment across issue areas"
  ) +
  theme_minimal()

```

Negative sentiment by topic group

```{r}

master_dataset %>%
  group_by(topic_group) %>%
  summarise(mean_asymmetry = mean(anti_west_vs_russia, na.rm = TRUE)) %>%
  ggplot(aes(x = reorder(topic_group, mean_asymmetry), y = mean_asymmetry)) +
  geom_col() +
  coord_flip() +
  labs(
    x = NULL,
    y = "Anti-West minus anti-Russia",
    title = "Narrative asymmetry by topic group"
  ) +
  theme_minimal()
```

Foreign expert use over time

```{r}

master_dataset %>%
  group_by(year) %>%
  summarise(foreign_share = mean(foreign_expert, na.rm = TRUE)) %>%
  ggplot(aes(x = year, y = foreign_share)) +
  geom_line() +
  scale_y_continuous(labels = scales::percent) +
  labs(
    x = NULL,
    y = "Share foreign experts",
    title = "Foreign expert use over time"
  ) +
  theme_minimal()
```

Anti-West framing over time

```{r}

master_dataset %>%
  group_by(year) %>%
  summarise(
    anti_west = mean(anti_west, na.rm = TRUE),
    anti_russia = mean(anti_russia, na.rm = TRUE)
  ) %>%
  tidyr::pivot_longer(
    cols = c(anti_west, anti_russia),
    names_to = "target",
    values_to = "rate"
  ) %>%
  ggplot(aes(x = year, y = rate, color = target)) +
  geom_line() +
  scale_y_continuous(labels = scales::percent) +
  labs(
    x = NULL,
    y = "Share of expert mentions",
    color = NULL,
    title = "Negative sentiment toward West and Russia over time"
  ) +
  theme_minimal()
```

Alluvial plot

```{r}

library(dplyr)

master_dataset <- master_dataset %>%
  mutate(sentiment_category = case_when(
    anti_west == 1 ~ "Anti-West",
    anti_russia == 1 ~ "Anti-Russia",
    anti_ukraine == 1 ~ "Anti-Ukraine",
    TRUE ~ "Neutral/Other"
  ))

library(ggalluvial)
library(ggplot2)

alluvial_data <- master_dataset %>%
  count(topic_group, foreign_expert, sentiment_category)

ggplot(
  alluvial_data,
  aes(
    axis1 = topic_group,
    axis2 = factor(foreign_expert, labels = c("Domestic", "Foreign")),
    axis3 = sentiment_category,
    y = n
  )
) +
  geom_alluvium(aes(fill = sentiment_category), width = 1/12) +
  geom_stratum(width = 1/12, fill = "grey85", color = "grey40") +
  geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
  scale_x_discrete(limits = c("Topic", "Expert origin", "Sentiment"), expand = c(.05, .05)) +
  labs(
    y = "Number of mentions",
    title = "Topic, expert nationality, and directed sentiment"
  ) +
  theme_minimal()



alluvial_data <- master_dataset %>%
  filter(sentiment_category != "Neutral/Other") %>%
  count(topic_group, foreign_expert, sentiment_category)



ggplot(
  alluvial_data,
  aes(
    axis1 = topic_group,
    axis2 = factor(foreign_expert, labels = c("Domestic","Foreign")),
    axis3 = sentiment_category,
    y = n
  )
) +
  geom_alluvium(aes(fill = sentiment_category), width = 1/12) +
  geom_stratum(width = 1/12, fill = "grey85", color = "grey40") +
  geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
  scale_x_discrete(
    limits = c("Topic","Expert origin","Sentiment"),
    expand = c(.05,.05)
  ) +
  labs(
    y = "Number of mentions",
    title = "Directed sentiment in expert commentary"
  ) +
  theme_minimal()


```

Issue space coordinates

```{r}
issue_space <- master_dataset %>%
  group_by(dominant_topic) %>%
  summarise(
    foreign_share = mean(foreign_expert),
    crime = mean(courts_crime),
    economy = mean(macro_economy + housing_market),
    geopolitics = mean(ukraine_war + international_geopolitics + military_technology + energy_sanctions),
    politics = mean(kremlin_governance + opinion_discourse + media_society)
  ) %>%
  mutate(
    x_coord = economy - crime,
    y_coord = geopolitics - politics
  )

issue_space <- issue_space %>%
  filter(dominant_topic != "other")

library(ggrepel)

ggplot(issue_space,
       aes(x = x_coord,
           y = y_coord,
           label = dominant_topic,
           color = foreign_share)) +

  geom_point(size = 5) +
  geom_text_repel() +

  scale_color_gradient(
    low = "steelblue",
    high = "darkred",
    name = "Share foreign experts"
  ) +

  labs(
    x = "Crime  ←→  Economy",
    y = "Domestic politics  ←→  Geopolitics",
    title = "Issue-space map of expert discourse"
  ) +

  theme_minimal()
```

```{r}
library(dplyr)

issue_space <- master_dataset %>%
  mutate(

    # X dimension: crime vs economy
    x_coord = (macro_economy + housing_market) - courts_crime,

    # Y dimension: geopolitics vs domestic politics
    y_coord = (ukraine_war +
               international_geopolitics +
               military_technology +
               energy_sanctions) -
              (kremlin_governance +
               opinion_discourse +
               media_society)

  )

library(ggplot2)

plot_data <- issue_space

ggplot(plot_data,
       aes(x = x_coord,
           y = y_coord,
           color = factor(foreign_expert))) +

  geom_point(alpha = 0.25, size = 1.5) +

  scale_color_manual(
    values = c("steelblue", "darkred"),
    labels = c("Domestic", "Foreign"),
    name = "Expert origin"
  ) +

  labs(
    x = "Crime  ←→  Economy",
    y = "Domestic politics  ←→  Geopolitics",
    title = "Issue-space map of expert discourse"
  ) +

  theme_minimal()

ggplot(plot_data,
       aes(x = x_coord,
           y = y_coord,
           color = factor(foreign_expert))) +

  geom_point(alpha = 0.15, size = 1) +

  geom_density_2d() +

  scale_color_manual(
    values = c("steelblue", "darkred"),
    labels = c("Domestic", "Foreign"),
    name = "Expert origin"
  ) +

  labs(
    x = "Crime  ←→  Economy",
    y = "Domestic politics  ←→  Geopolitics",
    title = "Issue-space distribution of foreign and domestic experts"
  ) +

  theme_minimal()
```

Map

```{r}

library(dplyr)
library(countrycode)
library(rnaturalearth)
library(sf)
library(ggplot2)
library(scales)

country_counts <- master_dataset %>%
  filter(!is.na(expert_country_master), expert_country_master != "Unknown") %>%
  count(expert_country_master) %>%
  mutate(
    iso_a3 = countrycode(expert_country_master,
                         origin = "country.name",
                         destination = "iso3c"),
    log_n = log10(n + 1)
  )

world <- rnaturalearth::ne_countries(scale = "medium",
                                     returnclass = "sf")

map_data <- world %>%
  left_join(country_counts, by = c("iso_a3" = "iso_a3"))

ggplot(map_data) +
  geom_sf(aes(fill = log_n),
          color = "white",
          size = 0.1) +

  scale_fill_gradient(
    low = "#f7fbff",
    high = "#08306b",
    na.value = "grey95",
    breaks = log10(c(1, 10, 100, 1000, 10000)),
    labels = comma(c(1, 10, 100, 1000, 10000)),
    name = "Expert mentions"
  ) +

  labs(
    title = "Geographic distribution of experts cited in Russian media",
    subtitle = "Counts of expert mentions by country (log-scaled color)"
  ) +

  theme_minimal(base_size = 12) +
  theme(
    panel.grid = element_blank(),
    axis.text = element_blank(),
    axis.title = element_blank(),
    plot.title = element_text(face = "bold"),
    legend.position = "right"
  )
```

Top foreign expert countries

```{r}

library(dplyr)
library(ggplot2)
library(scales)

master_dataset %>%
  filter(
    foreign_expert == 1,
    !is.na(expert_country),
    expert_country != "Unknown"
  ) %>%
  count(expert_country, sort = TRUE) %>%
  slice_head(n = 15) %>%
  ggplot(aes(x = reorder(expert_country, n), y = n)) +

  geom_col(fill = "#2b6cb0") +   # same tone as map (blue)

  coord_flip() +

  scale_y_continuous(labels = comma) +

  labs(
    x = NULL,
    y = "Number of mentions",
    title = "Most frequently cited foreign expert countries",
    subtitle = "Top 15 countries by number of expert mentions"
  ) +

  theme_minimal(base_size = 13) +
  theme(
    panel.grid.major.y = element_blank(),   # cleaner
    panel.grid.minor = element_blank(),
    axis.text.y = element_text(size = 11),
    axis.text.x = element_text(size = 10),
    plot.title = element_text(face = "bold", size = 15),
    plot.subtitle = element_text(size = 12),
    legend.position = "none"
  )
```

```{r}

master_dataset %>%
  count(topic_group, foreign_expert) %>%
  group_by(foreign_expert) %>%
  mutate(share = n / sum(n)) %>%
  ggplot(aes(x = topic_group, y = share, fill = factor(foreign_expert, labels = c("Domestic", "Foreign")))) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = scales::percent) +
  labs(
    x = NULL,
    y = "Share of expert mentions",
    fill = NULL,
    title = "Issue profile of foreign and domestic experts"
  ) +
  theme_minimal()
```

```{r}

heatmap_data <- master_dataset %>%
  group_by(topic_group) %>%
  summarise(
    Russia = mean(anti_russia, na.rm = TRUE),
    West = mean(anti_west, na.rm = TRUE),
    Ukraine = mean(anti_ukraine, na.rm = TRUE)
  ) %>%
  tidyr::pivot_longer(cols = c(Russia, West, Ukraine), names_to = "target", values_to = "rate")

ggplot(heatmap_data, aes(x = target, y = topic_group, fill = rate)) +
  geom_tile() +
  scale_fill_viridis_c(labels = scales::percent) +
  labs(
    x = NULL,
    y = NULL,
    fill = "Negative rate",
    title = "Heatmap of negative sentiment by topic and target"
  ) +
  theme_minimal()


heatmap_data_dom <- master_dataset %>%
  group_by(master_dataset$dominant_topic) %>%
  summarise(
    Russia = mean(anti_russia, na.rm = TRUE),
    West = mean(anti_west, na.rm = TRUE),
    Ukraine = mean(anti_ukraine, na.rm = TRUE)
  ) %>%
  tidyr::pivot_longer(cols = c(Russia, West, Ukraine), names_to = "target", values_to = "rate")

ggplot(heatmap_data_dom, aes(x = target, y = heatmap_data_dom$`master_dataset$dominant_topic`, fill = rate)) +
  geom_tile() +
  scale_fill_viridis_c(labels = scales::percent) +
  labs(
    x = NULL,
    y = NULL,
    fill = "Negative rate",
    title = "Heatmap of negative sentiment by topic and target"
  ) +
  theme_minimal()
```

```{r}

heatmap_data <- master_dataset %>%
  count(topic_group, foreign_expert) %>%
  group_by(topic_group) %>%
  mutate(share = n / sum(n))

ggplot(heatmap_data,
       aes(x = topic_group,
           y = factor(foreign_expert,
           labels = c("Domestic","Foreign")),
           fill = share)) +

  geom_tile() +

  scale_fill_viridis_c(labels = scales::percent) +

  labs(
    x = "Topic",
    y = "Expert origin",
    fill = "Share",
    title = "Foreign and domestic experts across issue areas"
  ) +

  theme_minimal()
```

# Topic modelling for Tore

```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
library(stringr)
library(scales)

topic_cols <- c(
"courts_crime",
"covid_health",
"development_education",
"energy_sanctions",
"general_news",
"housing_market",
"information_services",
"international_geopolitics",
"kremlin_governance",
"macro_economy",
"media_society",
"military_technology",
"opinion_discourse",
"regions_local",
"ukraine_war"
)

topic_distribution <- master_dataset %>%
  summarise(across(all_of(topic_cols), mean)) %>%
  pivot_longer(
    everything(),
    names_to = "topic",
    values_to = "share"
  ) %>%
  mutate(
    topic = str_replace_all(topic, "_", " "),
    topic = str_to_title(topic),
    percent = share * 100
  ) %>%
  arrange(desc(percent))

ggplot(topic_distribution,
       aes(x = reorder(topic, percent),
           y = percent)) +
  geom_col(fill = "#4C78A8", width = 0.7) +
  coord_flip() +
  geom_text(
    aes(label = sprintf("%.1f%%", percent)),
    hjust = -0.1,
    size = 3.5
  ) +
  scale_y_continuous(
    expand = expansion(mult = c(0, .08)),
    labels = label_percent(scale = 1)
  ) +
  labs(
    x = NULL,
    y = "Average topic share (%)",
    title = "Topic prevalence in the news corpus"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    panel.grid.major.y = element_blank(),
    plot.title = element_text(face = "bold"),
    axis.text.y = element_text(size = 11)
  )

```

```{r}

library(dplyr)
library(tidyr)
library(ggplot2)
library(stringr)
library(scales)

topic_cols <- c(
"courts_crime",
"covid_health",
"development_education",
"energy_sanctions",
"general_news",
"housing_market",
"information_services",
"international_geopolitics",
"kremlin_governance",
"macro_economy",
"media_society",
"military_technology",
"opinion_discourse",
"regions_local",
"ukraine_war"
)

topic_distribution <- master_dataset %>%
  summarise(across(all_of(topic_cols), mean)) %>%
  pivot_longer(
    everything(),
    names_to = "topic",
    values_to = "share"
  ) %>%
  mutate(
    
    topic = str_replace_all(topic, "_", " "),
    topic = str_to_title(topic),
    
    percent = share * 100,
    
    group = case_when(
      topic %in% c("Macro Economy","Housing Market","Energy Sanctions") ~ "Economic policy",
      
      topic %in% c("Kremlin Governance","Courts Crime","Regions Local") ~ "Domestic politics",
      
      topic %in% c("Ukraine War","Military Technology","International Geopolitics") ~ "International politics",
      
      topic %in% c("Covid Health","Media Society","Opinion Discourse",
                   "General News","Development Education","Information Services") ~ "Society and information"
    )
    
  ) %>%
  arrange(desc(percent))

ggplot(topic_distribution,
       aes(x = reorder(topic, percent),
           y = percent,
           fill = group)) +
  
  geom_col(width = 0.7) +
  
  coord_flip() +
  
  geom_text(
    aes(label = sprintf("%.1f%%", percent)),
    hjust = -0.1,
    size = 3.5
  ) +
  
  scale_fill_manual(values = c(
    "Economic policy" = "#4C78A8",
    "Domestic politics" = "#F58518",
    "International politics" = "#54A24B",
    "Society and information" = "#B279A2"
  )) +
  
  scale_y_continuous(
    expand = expansion(mult = c(0, .08)),
    labels = label_percent(scale = 1)
  ) +
  
  labs(
    x = NULL,
    y = "Average topic share (%)",
    fill = "Topic category",
    title = "Topic prevalence in the Lenta.ru news corpus"
  ) +
  
  theme_minimal(base_size = 12) +
  
  theme(
    panel.grid.major.y = element_blank(),
    plot.title = element_text(face = "bold"),
    axis.text.y = element_text(size = 11),
    legend.position = "bottom"
  )
```

```{r}

topic_map <- data.frame(
topic = topic_cols,
group = c(
"crime",
"other",
"economy",
"geopolitics",
"other",
"economy",
"other",
"geopolitics",
"politics",
"economy",
"politics",
"geopolitics",
"politics",
"other",
"geopolitics"
))

topic_group_dist <- topic_distribution %>%
  left_join(topic_map)

ggplot(topic_group_dist,
       aes(x=group,
           y=share,
           fill=topic)) +
  geom_col() +
  labs(
    x="Topic group",
    y="Average topic weight",
    title="Aggregation of topics into issue groups"
  ) +
  theme_minimal()
```

```{r}

topic_time <- master_dataset %>%
  group_by(year) %>%
  summarise(across(all_of(topic_cols), mean)) %>%
  pivot_longer(-year,
               names_to="topic",
               values_to="share")

ggplot(topic_time,
       aes(x=year,
           y=share,
           color=topic)) +
  geom_line() +
  labs(
    x=NULL,
    y="Average topic weight",
    title="Topic prevalence over time"
  ) +
  theme_minimal()
```

```{r}

library(treemapify)

topic_sizes <- topic_distribution %>%
  left_join(topic_map)

ggplot(topic_sizes,
       aes(area=share,
           fill=group,
           label=topic)) +
  geom_treemap() +
  geom_treemap_text(
    colour="white",
    place="centre",
    grow=TRUE
  ) +
  labs(
    title="Topic composition of the corpus"
  ) +
  theme_minimal()

ggplot(topic_sizes,
       aes(area=share,
           fill=group,
           label=paste0(topic,"\n",round(share*100,1),"%"))) +

  geom_treemap(color="white") +
  geom_treemap_text(
    colour="white",
    place="centre",
    reflow=TRUE
  ) +

  scale_fill_brewer(palette="Set2") +

  labs(
    title="Topic composition of the corpus",
    fill="Topic group"
  ) +

  theme_minimal()
```

```{r}

master_dataset %>%
  count(dominant_topic) %>%
  ggplot(aes(x=reorder(dominant_topic,n), y=n)) +
  geom_col(fill="darkred") +
  coord_flip() +
  labs(
    x=NULL,
    y="Expert mentions",
    title="Distribution of expert mentions across topics"
  ) +
  theme_minimal()
```

# Directed sentiment for Tore:

```{r}

library(dplyr)
library(ggplot2)

sentiment_dist <- master_dataset %>%
  summarise(
    anti_russia = sum(anti_russia),
    anti_west = sum(anti_west),
    anti_ukraine = sum(anti_ukraine)
  ) %>%
  tidyr::pivot_longer(
    everything(),
    names_to="target",
    values_to="count"
  )

ggplot(sentiment_dist,
       aes(x=target, y=count)) +
  geom_col(fill="steelblue") +
  labs(
    x=NULL,
    y="Number of mentions",
    title="Directed negative sentiment by target actor"
  ) +
  theme_minimal()

```

```{r}

sentiment_compare <- master_dataset %>%
  summarise(
    Russia = mean(anti_russia),
    West = mean(anti_west),
    Ukraine = mean(anti_ukraine)
  ) %>%
  tidyr::pivot_longer(
    everything(),
    names_to="target",
    values_to="rate"
  )

ggplot(sentiment_compare,
       aes(x=target, y=rate)) +
  geom_col(fill="darkred") +
  scale_y_continuous(labels=scales::percent) +
  labs(
    x=NULL,
    y="Share of mentions",
    title="Directed sentiment assigns negativity to specific actors"
  ) +
  theme_minimal()
```

```{r}

sentiment_categories <- master_dataset %>%
  mutate(sentiment_category = case_when(
    anti_west == 1 ~ "Anti-West",
    anti_russia == 1 ~ "Anti-Russia",
    anti_ukraine == 1 ~ "Anti-Ukraine",
    TRUE ~ "Neutral"
  )) %>%
  count(sentiment_category)

ggplot(sentiment_categories,
       aes(x=reorder(sentiment_category, n), y=n)) +
  geom_col(fill="grey50") +
  coord_flip() +
  labs(
    x=NULL,
    y="Number of sentences",
    title="Distribution of directed sentiment categories"
  ) +
  theme_minimal()
```

```{r}

targets <- master_dataset %>%
  summarise(
    Russia=sum(any_negative_russia),
    West=sum(any_negative_west),
    Ukraine=sum(any_negative_ukraine)
  ) %>%
  tidyr::pivot_longer(
    everything(),
    names_to="target",
    values_to="mentions"
  )

ggplot(targets,
       aes(x=target, y=mentions)) +
  geom_col(fill="firebrick") +
  labs(
    x=NULL,
    y="Mentions",
    title="Targets detected in directed sentiment analysis"
  ) +
  theme_minimal()

```

```{r}
master_dataset %>%
  filter(anti_west == 1) %>%
  select(mention_sentence) %>%
  slice_sample(n=5)
```

```{r}

library(DiagrammeR)

grViz("
digraph pipeline {

graph [layout = dot]

node [shape = box]

A [label='News Articles']
B [label='Topic Modelling']
C [label='Expert Extraction']
D [label='Directed Sentiment']
E [label='Final Dataset']

A -> B -> C -> D -> E

}
")

```

```{r}

library(broom)
library(ggplot2)

model <- glm(
  anti_west ~ foreign_expert + topic_group + year,
  data = master_dataset,
  family = binomial
)

coef_data <- broom::tidy(model, conf.int = TRUE)

coef_data <- coef_data %>%
  filter(term != "(Intercept)")

ggplot(coef_data,
       aes(x = estimate,
           y = reorder(term, estimate))) +

  geom_point(size = 3) +

  geom_errorbarh(
    aes(xmin = conf.low,
        xmax = conf.high),
    height = .2
  ) +

  geom_vline(xintercept = 0,
             linetype = "dashed") +

  labs(
    x = "Coefficient estimate",
    y = NULL,
    title = "Factors associated with anti-West sentiment"
  ) +

  theme_minimal()


```

```{r}

library(ggeffects)

pred <- ggpredict(model, terms = "foreign_expert")

plot(pred) +
  labs(
    x = "Foreign expert",
    y = "Predicted probability of anti-West sentiment",
    title = "Effect of foreign experts on anti-West sentiment"
  )

pred_topic <- ggpredict(model,
                        terms = c("topic_group","foreign_expert"))

plot(pred_topic) +
  labs(
    x = "Topic group",
    y = "Predicted probability",
    title = "Anti-West sentiment across topics and expert origin"
  )

pred_topic <- ggpredict(model,
                        terms = c("topic_group","foreign_expert"))

plot(pred_topic) +
  labs(
    x = "Topic group",
    y = "Predicted probability",
    title = "Anti-West sentiment across topics and expert origin"
  )
```

```{r}

model1 <- glm(
  anti_west ~ foreign_expert,
  data = master_dataset,
  family = binomial
)

library(ggeffects)

plot(ggpredict(model1, terms = "foreign_expert")) +
  labs(
    x = "Foreign expert",
    y = "Predicted probability",
    title = "Foreign experts and anti-West sentiment"
  )

```

```{r}

model2 <- glm(
  anti_west ~ foreign_expert + topic_group,
  data = master_dataset,
  family = binomial
)

library(broom)

coef2 <- tidy(model2, conf.int = TRUE)

ggplot(coef2 %>% filter(term != "(Intercept)"),
       aes(x = estimate, y = reorder(term, estimate))) +
  geom_point() +
  geom_errorbarh(aes(xmin = conf.low, xmax = conf.high), height=.2) +
  geom_vline(xintercept = 0, linetype="dashed") +
  theme_minimal() +
  labs(
    x="Coefficient",
    y=NULL,
    title="Topic effects on anti-West sentiment"
  )

```

```{r}

model3 <- glm(
  anti_west ~ foreign_expert * topic_group,
  data = master_dataset,
  family = binomial
)

plot(ggpredict(model3, terms = c("topic_group","foreign_expert"))) +
  labs(
    x="Topic group",
    y="Predicted probability",
    title="Foreign experts across issue areas"
  )
```

```{r}

model4 <- lm(
  anti_west_vs_russia ~ foreign_expert + topic_group + year,
  data = master_dataset
)

coef4 <- tidy(model4, conf.int = TRUE)

ggplot(coef4 %>% filter(term!="(Intercept)"),
       aes(x=estimate, y=reorder(term,estimate))) +
  geom_point() +
  geom_errorbarh(aes(xmin=conf.low, xmax=conf.high), height=.2) +
  geom_vline(xintercept=0, linetype="dashed") +
  theme_minimal() +
  labs(
    title="Drivers of narrative asymmetry"
  )
```

```{r}

model5 <- glm(
  anti_russia ~ foreign_expert + topic_group + year,
  data = master_dataset,
  family = binomial
)

model5
```

```{r}

model6 <- glm(
  anti_west ~ foreign_expert + topic_group + year,
  data = master_dataset,
  family = binomial
)


plot(ggpredict(model6, terms="year")) +
  labs(
    y="Predicted probability",
    title="Anti-West sentiment over time"
  )
```

```{r}

model_topic <- glm(
  anti_west ~ foreign_expert + dominant_topic + year,
  data = master_dataset,
  family = binomial
)

library(broom)
library(dplyr)

coef_topic <- tidy(model_topic, conf.int = TRUE) %>%
  filter(term != "(Intercept)")


coef_topic <- coef_topic %>%
  mutate(
    term = gsub("dominant_topic", "", term),
    term = gsub("_", " ", term)
  )

library(ggplot2)

ggplot(coef_topic,
       aes(x = estimate,
           y = reorder(term, estimate))) +

  geom_point(size = 3) +

  geom_errorbarh(
    aes(xmin = conf.low,
        xmax = conf.high),
    height = .2
  ) +

  geom_vline(xintercept = 0,
             linetype = "dashed",
             color = "grey40") +

  labs(
    x = "Coefficient estimate",
    y = NULL,
    title = "Anti-West sentiment across dominant topics"
  ) +

  theme_minimal()


coef_topic <- coef_topic %>%
  filter(grepl("topic", term))

library(ggeffects)

pred_topic <- ggpredict(
  model_topic,
  terms = "dominant_topic"
)

plot(pred_topic) +
  labs(
    x = "Dominant topic",
    y = "Predicted probability of anti-West sentiment",
    title = "Anti-West sentiment by topic"
  )
```

```{r}

library(dplyr)
library(ggplot2)

target_data <- master_dataset %>%
  mutate(
    target = case_when(
      any_positive_russia == 1 | any_negative_russia == 1 | any_neutral_russia == 1 ~ "Russia",
      any_positive_west == 1 | any_negative_west == 1 | any_neutral_west == 1 ~ "West",
      any_positive_ukraine == 1 | any_negative_ukraine == 1 | any_neutral_ukraine == 1 ~ "Ukraine",
      TRUE ~ "Other actors / non-target"
    )
  )

counts <- target_data %>%
  count(target)

detected <- counts %>%
  filter(target != "Other actors / non-target") %>%
  mutate(group = "Detected targets")

other <- counts %>%
  filter(target == "Other actors / non-target") %>%
  mutate(group = "Other actors / non-target")

plot_data <- bind_rows(detected, other)

ggplot(plot_data,
       aes(x = group,
           y = n,
           fill = target)) +
  
  geom_col(width = 0.6) +
  
 scale_fill_manual(values = c(
  "Russia" = "#4E79A7",
  "West" = "#76B7B2",
  "Ukraine" = "#F28E2B",
  "Other actors / non-target" = "#D3D3D3"
)) +
  
  labs(
    x = NULL,
    y = "Number of expert mention sentences",
    fill = "Target actor",
    title = "Detection of geopolitical targets in expert commentary"
  ) +
  
  theme_minimal(base_size = 12) +
  theme(
    legend.position = "right",
    plot.title = element_text(face = "bold")
  )
```

```{r}

library(dplyr)
library(tidyr)
library(ggplot2)

sentiment_data <- master_dataset %>%
  summarise(
    Russia_Positive = sum(any_positive_russia),
    Russia_Neutral  = sum(any_neutral_russia),
    Russia_Negative = sum(any_negative_russia),
    
    West_Positive   = sum(any_positive_west),
    West_Neutral    = sum(any_neutral_west),
    West_Negative   = sum(any_negative_west),
    
    Ukraine_Positive = sum(any_positive_ukraine),
    Ukraine_Neutral  = sum(any_neutral_ukraine),
    Ukraine_Negative = sum(any_negative_ukraine)
  ) %>%
  pivot_longer(everything()) %>%
  separate(name, into = c("target","sentiment"), sep = "_")

ggplot(sentiment_data,
       aes(x = target,
           y = value,
           fill = sentiment)) +
  
  geom_col(position = position_dodge(width = 0.7),
           width = 0.6) +
  
  scale_fill_manual(values = c(
    "Positive" = "#4C78A8",
    "Neutral"  = "#D9D9D9",
    "Negative" = "#7F7F7F"
  )) +
  
  labs(
    x = "Target actor",
    y = "Number of expert mention sentences",
    fill = "Sentiment",
    title = "Sentiment classification across detected geopolitical targets"
  ) +
  
  theme_minimal(base_size = 12) +
  theme(
    legend.title = element_blank(),
    panel.grid.minor = element_blank(),
    plot.title = element_text(face = "bold")
  )
```

# Plots for writing:

## H1: Foreign expert + topic

```{r}

library(dplyr)
library(ggplot2)
library(ggeffects)
library(scales)

# Create clean topic names (without modifying original variable)
master_dataset <- master_dataset %>%
  mutate(
    dominant_topic_clean = recode(dominant_topic,
      "ukraine_war" = "Ukraine war",
      "international_geopolitics" = "International geopolitics",
      "media_society" = "Media and society",
      "no_topic" = "Other / no clear topic",
      "military_technology" = "Military technology",
      "general_news" = "General news reporting",
      "energy_sanctions" = "Energy and sanctions",
      "opinion_discourse" = "Opinion and commentary",
      "macro_economy" = "Macroeconomy",
      "courts_crime" = "Courts and crime",
      "kremlin_governance" = "Kremlin governance",
      "covid_health" = "COVID-19 and health",
      "information_services" = "Information services",
      "housing_market" = "Housing market",
      "regions_local" = "Regional and local issues",
      "development_education" = "Development and education"
    )
  )
library(dplyr)
library(ggplot2)
library(ggeffects)
library(scales)

# Ensure dominant_topic is a factor and set reference category
master_dataset$dominant_topic_clean <- factor(master_dataset$dominant_topic_clean)

# OPTIONAL: change reference to a meaningful baseline if you have one
# Example:
# master_dataset$dominant_topic <- relevel(master_dataset$dominant_topic, ref = "Domestic politics")

# Run model
model_h1 <- glm(
  foreign_expert ~ dominant_topic_clean + year,
  data = master_dataset,
  family = binomial
)

# Get predicted probabilities
pred_topic <- ggpredict(model_h1, terms = "dominant_topic_clean")

pred_df <- as.data.frame(pred_topic)

# Plot
ggplot(pred_df, aes(x = reorder(x, predicted), y = predicted)) +

  geom_point(size = 3, color = "#2b6cb0") +

  geom_errorbar(
    aes(ymin = conf.low, ymax = conf.high),
    width = 0.2
  ) +

  coord_flip() +

  scale_y_continuous(labels = percent_format(accuracy = 1)) +

  labs(
    x = NULL,
    y = "Predicted probability of foreign expert",
    title = "Foreign expert presence across topics"
  ) +

  theme_minimal(base_size = 13) +
  theme(
    plot.title = element_text(face = "bold"),
    panel.grid.minor = element_blank()
  )

```

```{r}
library(dplyr)
library(ggplot2)
library(ggeffects)
library(scales)

# Define geopolitical topics
geopolitical_topics <- c(
  "Ukraine war",
  "International geopolitics",
  "Military technology",
  "Energy and sanctions"
)

# Clean topic names and remove no_topic
master_dataset <- master_dataset %>%
  mutate(
    dominant_topic_clean = recode(dominant_topic,
      "ukraine_war"             = "Ukraine war",
      "international_geopolitics" = "International geopolitics",
      "media_society"           = "Media and society",
      "military_technology"     = "Military technology",
      "general_news"            = "General news reporting",
      "energy_sanctions"        = "Energy and sanctions",
      "opinion_discourse"       = "Opinion and commentary",
      "macro_economy"           = "Macroeconomy",
      "courts_crime"            = "Courts and crime",
      "kremlin_governance"      = "Kremlin governance",
      "covid_health"            = "COVID-19 and health",
      "information_services"    = "Information services",
      "housing_market"          = "Housing market",
      "regions_local"           = "Regional and local issues",
      "development_education"   = "Development and education"
    )
  ) %>%
  filter(dominant_topic != "no_topic")

master_dataset$dominant_topic_clean <- factor(master_dataset$dominant_topic_clean)

# Run model
model_h1 <- glm(
  foreign_expert ~ dominant_topic_clean + year,
  data = master_dataset,
  family = binomial
)

# Get predicted probabilities
pred_topic <- ggpredict(model_h1, terms = "dominant_topic_clean")
pred_df <- as.data.frame(pred_topic)

# Add geopolitical indicator
pred_df <- pred_df %>%
  mutate(topic_type = ifelse(x %in% geopolitical_topics,
                             "Geopolitical", "Domestic / other"))

# Plot
ggplot(pred_df, aes(x = reorder(x, predicted), y = predicted,
                    color = topic_type)) +
  geom_point(size = 4) +
  geom_errorbar(
    aes(ymin = conf.low, ymax = conf.high),
    width = 0.2
  ) +
  scale_color_manual(
    values = c("Geopolitical" = "#2b6cb0", "Domestic / other" = "gray"),
    name = NULL
  ) +
  coord_flip() +
  scale_y_continuous(labels = percent_format(accuracy = 1)) +
  labs(
    x = NULL,
    y = "Predicted probability of foreign expert",
    title = "Foreign expert presence across topics"
  ) +
  theme_minimal(base_size = 13) +
  theme(
    plot.title = element_text(face = "bold"),
    panel.grid.minor = element_blank(),
    legend.position = "bottom"
  )
```

## Before vs after 2014

```{r}
library(dplyr)
library(ggplot2)
library(ggeffects)
library(scales)

# Split pre/post 2014
master_dataset <- master_dataset %>%
  mutate(
    period = if_else(year < 2014, "Before 2014", "2014 and after"),
    period = factor(period, levels = c("Before 2014", "2014 and after"))
  )

# Model
model_period <- glm(
  foreign_expert ~ dominant_topic_clean * period,
  data = master_dataset,
  family = binomial
)

# Predictions
pred_df <- ggpredict(
  model_period,
  terms = c("dominant_topic_clean", "period")
) %>%
  as.data.frame() %>%
  mutate(x = as.character(x))

# Order topics by pre-2014 probabilities
topic_order <- pred_df %>%
  filter(group == "Before 2014") %>%
  arrange(desc(predicted)) %>%
  pull(x)

pred_df <- pred_df %>%
  mutate(
    x = factor(x, levels = rev(topic_order))
  )

# Wide format for plotting change
plot_df <- pred_df %>%
  select(x, group, predicted) %>%
  tidyr::pivot_wider(
    names_from = group,
    values_from = predicted
  )

# Dumbbell plot
ggplot(plot_df, aes(y = x)) +
  
  geom_segment(
    aes(
      x = `2014 and after`,
      xend = `Before 2014`,
      yend = x
    ),
    color = "grey70",
    linewidth = 0.8
  ) +
  
  geom_point(
    aes(x = `Before 2014`),
    size = 3,
    color = "#2b6cb0"
  ) +
  
  geom_point(
    aes(x = `2014 and after`),
    size = 3,
    color = "#c53030"
  ) +
  
  scale_x_continuous(
    labels = percent_format(accuracy = 1)
  ) +
  
  labs(
    x = "Predicted probability of foreign expert",
    y = NULL,
    title = "Change in foreign expert use across topics after the 2014 takeover",
    subtitle = "Blue = Before 2014   |   Red = 2014 and after"
  ) +
  
  theme_minimal(base_size = 13) +
  theme(
    plot.title = element_text(face = "bold"),
    panel.grid.minor = element_blank(),
    panel.grid.major.y = element_blank()
  )


```

```{r}
# -----------------------------
# Define geopolitical topics
# -----------------------------
geo_topics <- c(
  "Ukraine war",
  "International geopolitics",
  "Military technology",
  "Energy and sanctions"
)

# -----------------------------
# Get predictions from model
# -----------------------------
pred_df <- ggpredict(
  model_period,
  terms = c("dominant_topic_clean", "period")
) %>%
  as.data.frame() %>%
  mutate(
    x = as.character(x),
    topic_group = if_else(
      x %in% geo_topics,
      "Geopolitical",
      "Domestic / other"
    )
  )

# -----------------------------
# Wide format + compute change
# -----------------------------
plot_df <- pred_df %>%
  select(x, group, predicted, topic_group) %>%
  pivot_wider(
    names_from = group,
    values_from = predicted
  ) %>%
  mutate(change = after_2014 - before_2014)

topic_order <- plot_df %>%
  arrange(topic_group, change) %>%
  pull(x)

plot_df <- plot_df %>%
  mutate(x = factor(x, levels = topic_order))

# -----------------------------
# Plot
# -----------------------------
ggplot(plot_df, aes(y = x)) +
  
  geom_segment(
    aes(
      x = before_2014,
      xend = after_2014,
      yend = x
    ),
    arrow = arrow(length = unit(0.06, "inches")),
    linewidth = 0.7,
    color = "grey40"
  ) +
  
  geom_point(
    aes(x = before_2014),
    shape = 21,
    fill = "white",
    color = "black",
    size = 2.8,
    stroke = 0.8
  ) +
  
  geom_point(
    aes(
      x = after_2014,
      fill = topic_group
    ),
    shape = 21,
    color = "black",
    size = 3,
    stroke = 0.5
  ) +
  
  scale_fill_manual(
    values = c(
      "Geopolitical"     = "#2166ac",
      "Domestic / other" = "#d6604d"
    ),
    name = NULL
  ) +
  
  scale_x_continuous(
    labels = percent_format(accuracy = 1),
    expand = expansion(mult = c(0.02, 0.08))
  ) +
  
  # Optional: add change labels on the right
  geom_text(
    aes(
      x = after_2014,
      label = sprintf("%+.0f pp", change * 100)
    ),
    hjust = -0.4,
    vjust = 0.8,
    size = 3,
    color = "grey30"
  ) +
  geom_hline(
  yintercept = sum(plot_df$topic_group == "Domestic / other") + 0.5,
  linetype = "dashed",
  color = "grey70",
  linewidth = 0.5
) +
  
  labs(
    x = "Predicted probability of foreign expert",
    y = NULL,
    title = "Foreign expert use before and after the 2014 takeover",
    subtitle = "Topics sorted by post-takeover change; open circle = before 2014, filled = after 2014",
    caption = "Predicted probabilities from logistic regression. Blue = geopolitical topics, red = domestic/other."
  ) +
  
  theme_minimal(base_size = 13) +
  theme(
    plot.title    = element_text(face = "bold"),
    plot.subtitle = element_text(color = "grey40", size = 11),
    plot.caption  = element_text(color = "grey50", size = 9, hjust = 0),
    panel.grid.minor   = element_blank(),
    panel.grid.major.y = element_blank(),
    legend.position    = "top",
    legend.justification = "left"
  )
```

topic before and after 2014 v.2

```{r}
library(tidyverse)
library(ggeffects)
library(scales)
library(ggplot2)

# -----------------------------
# Define geopolitical topics
# -----------------------------
geo_topics <- c(
  "Ukraine war",
  "International geopolitics",
  "Military technology",
  "Energy and sanctions"
)

# -----------------------------
# Get predictions from model
# -----------------------------
pred_df <- ggpredict(
  model_period,
  terms = c("dominant_topic_clean", "period")
) %>%
  as.data.frame() %>%
  mutate(
    x = as.character(x),
    topic_group = if_else(
      x %in% geo_topics,
      "Geopolitical",
      "Domestic / other"
    )
  )

# -----------------------------
# Wide format + compute change
# -----------------------------
plot_df <- pred_df %>%
  select(x, group, predicted, conf.low, conf.high, topic_group) %>%
  mutate(
    period = case_when(
      group == "Before 2014"    ~ "before_2014",
      group == "2014 and after" ~ "after_2014"
    )
  ) %>%
  select(-group) %>%
  pivot_wider(
    names_from = period,
    values_from = c(predicted, conf.low, conf.high),
    names_glue = "{.value}_{period}"
  ) %>%
  mutate(
    change = predicted_after_2014 - predicted_before_2014,
    topic_group = factor(topic_group, levels = c("Geopolitical", "Domestic / other"))
  )

# -----------------------------
# Order topics
# -----------------------------
topic_order <- plot_df %>%
  arrange(change) %>%
  pull(x)

plot_df <- plot_df %>%
  mutate(x = factor(x, levels = rev(topic_order)))

plot_df <- plot_df %>%
  mutate(decline = predicted_before_2014 - predicted_after_2014)

# -----------------------------
# Plot
# -----------------------------
ggplot(plot_df, aes(x = change, y = x, fill = topic_group)) +
  geom_col(width = 0.65, color = "grey25", linewidth = 0.2) +
  geom_vline(xintercept = 0, linewidth = 0.5, color = "grey35") +
  geom_text(
    aes(label = sprintf("%+.0f pp", change * 100)),
    hjust = if_else(plot_df$change < 0, 1.1, -0.1),
    size = 3.2,
    color = "grey20"
  ) +
  scale_x_continuous(
    labels = percent_format(accuracy = 1),
    expand = expansion(mult = c(0.12, 0.12))
  ) +
  scale_fill_manual(
    values = c(
      "Geopolitical"     = "#2166ac",
      "Domestic / other" = "#d6604d"
    ),
    name = NULL
  ) +
  labs(
    x = "Post-2014 change in predicted probability of foreign expert use",
    y = NULL,
    title = "Foreign expert use contracted mainly outside geopolitical topics after 2014",
    subtitle = "Bars show post-2014 predicted probability minus pre-2014 predicted probability",
    caption = "Predicted probabilities from logistic regression with topic-period interactions."
  ) +
  theme_minimal(base_size = 13) +
  theme(
    plot.title    = element_text(face = "bold"),
    plot.subtitle = element_text(color = "grey40", size = 11),
    plot.caption  = element_text(color = "grey50", size = 9, hjust = 0),
    panel.grid.minor   = element_blank(),
    panel.grid.major.y = element_blank(),
    legend.position    = "top",
    legend.justification = "left"
  )
```

```{r}
library(tidyverse)
library(ggeffects)
library(scales)
library(ggplot2)

# -----------------------------
# Define geopolitical topics
# -----------------------------
geo_topics <- c(
  "Ukraine war",
  "International geopolitics",
  "Military technology",
  "Energy and sanctions"
)

# -----------------------------
# Get predictions from model
# -----------------------------
pred_df <- ggpredict(
  model_period,
  terms = c("dominant_topic_clean", "period")
) %>%
  as.data.frame() %>%
  mutate(
    topic = as.character(x),
    period_label = case_when(
      as.character(group) == "Before 2014"    ~ "Before 2014",
      as.character(group) == "2014 and after" ~ "2014 and after",
      TRUE ~ as.character(group)
    ),
    topic_group = if_else(
      topic %in% geo_topics,
      "Geopolitical",
      "Domestic / other"
    ),
    period_label = factor(
      period_label,
      levels = c("Before 2014", "2014 and after")
    ),
    topic_group = factor(
      topic_group,
      levels = c("Geopolitical", "Domestic / other")
    )
  )

# -----------------------------
# Long format for slopegraph
# -----------------------------
slope_df <- plot_df %>%
  select(
    x,
    topic_group,
    before_2014 = predicted_before_2014,
    after_2014 = predicted_after_2014,
    change
  ) %>%
  pivot_longer(
    cols = c(before_2014, after_2014),
    names_to = "period",
    values_to = "predicted"
  ) %>%
  mutate(
    period = case_when(
      period == "before_2014" ~ "1999--2013",
      period == "after_2014"  ~ "2015--2024"
    ),
    period = factor(period, levels = c("1999--2013", "2015--2024")),
    topic_group = factor(topic_group, levels = c("Geopolitical", "Domestic / other"))
  )

# Order topics by change within the full sample
topic_order <- plot_df %>%
  arrange(change) %>%
  pull(x)

slope_df <- slope_df %>%
  mutate(x = factor(x, levels = topic_order))

# -----------------------------
# Plot: slopegraph
# -----------------------------
ggplot(slope_df, aes(x = period, y = predicted, group = x, color = topic_group)) +
  geom_line(linewidth = 0.7, alpha = 0.75) +
  geom_point(size = 2.5) +
  geom_text(
    data = slope_df %>% filter(period == "1999--2013"),
    aes(label = x),
    hjust = 1.05,
    size = 3,
    color = "grey25"
  ) +
  geom_text(
    data = slope_df %>% filter(period == "2015--2024"),
    aes(label = sprintf("%.0f%%", predicted * 100)),
    hjust = -0.25,
    size = 3,
    color = "grey25"
  ) +
  facet_wrap(~ topic_group, scales = "free_y") +
  scale_y_continuous(
    labels = percent_format(accuracy = 1),
    expand = expansion(mult = c(0.08, 0.12))
  ) +
  scale_color_manual(
    values = c(
      "Geopolitical"     = "#2166ac",
      "Domestic / other" = "#d6604d"
    ),
    guide = "none"
  ) +
  labs(
    x = NULL,
    y = "Predicted probability of foreign expert use",
    title = "Foreign expert use narrowed after the 2014 editorial takeover",
    subtitle = "Lines connect each topic's predicted probability before and after 2014",
    caption = "Predicted probabilities from logistic regression with topic-period interactions."
  ) +
  coord_cartesian(clip = "off") +
  theme_minimal(base_size = 13) +
  theme(
    plot.title    = element_text(face = "bold"),
    plot.subtitle = element_text(color = "grey40", size = 11),
    plot.caption  = element_text(color = "grey50", size = 9, hjust = 0),
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_blank(),
    strip.text = element_text(face = "bold"),
    plot.margin = margin(5.5, 45, 5.5, 90)
  )
```

```{r}


master_dataset %>%
  group_by(dominant_topic) %>%
  summarise(
    share_foreign = mean(foreign_expert)
  ) %>%
  ggplot(aes(x = reorder(dominant_topic, share_foreign),
             y = share_foreign)) +
  geom_col(fill = "#2b6cb0") +
  coord_flip()

```

## H2: sentiment

```{r}
library(dplyr)
library(ggplot2)
library(ggeffects)
library(scales)

# Run main model
model_sentiment <- glm(
  anti_west ~ foreign_expert + dominant_topic_clean + year,
  data = master_dataset,
  family = binomial
)

# Get predicted probabilities for foreign vs domestic
pred_expert <- ggpredict(model_sentiment, terms = "foreign_expert")

pred_df <- as.data.frame(pred_expert)

# Clean labels
pred_df <- pred_df %>%
  mutate(
    Expert = factor(x,
                    levels = c(0, 1),
                    labels = c("Domestic expert", "Foreign expert"))
  )

# Plot
ggplot(pred_df,
       aes(x = Expert, y = predicted, color = Expert)) +

  geom_point(size = 3) +

  geom_errorbar(
    aes(ymin = conf.low, ymax = conf.high),
    width = 0.15
  ) +

  scale_color_manual(
    values = c(
      "Domestic expert" = "#b04a4a",
      "Foreign expert"  = "#2b6cb0"
    )
  ) +

  scale_y_continuous(
    labels = percent_format(accuracy = 1)
  ) +

  labs(
    x = NULL,
    y = "Predicted probability of negative sentiment toward the West",
    title = "Effect of foreign experts on anti-West sentiment"
  ) +

  theme_minimal(base_size = 13) +
  theme(
    plot.title = element_text(face = "bold"),
    legend.position = "none",
    panel.grid.minor = element_blank()
  )
```

```{r}


library(dplyr)
library(ggplot2)
library(broom)

# Faster models (no topic)
model_west <- glm(anti_west ~ foreign_expert + year,
                  data = master_dataset, family = binomial)

model_russia <- glm(anti_russia ~ foreign_expert + year,
                    data = master_dataset, family = binomial)

model_ukraine <- glm(any_anti_ukraine ~ foreign_expert + year,
                     data = master_dataset, family = binomial)

# Extract coefficients (fast CI)
coef_df <- bind_rows(
  tidy(model_russia) %>% mutate(Target = "Russia"),
  tidy(model_ukraine) %>% mutate(Target = "Ukraine"),
  tidy(model_west) %>% mutate(Target = "West")
) %>%
  filter(term == "foreign_expert") %>%
  mutate(
    conf.low = estimate - 1.96 * std.error,
    conf.high = estimate + 1.96 * std.error,
    Target = factor(Target, levels = c("Russia", "Ukraine", "West"))
  )

# Plot
ggplot(coef_df,
       aes(x = estimate, y = Target)) +

  geom_point(size = 3, color = "#2b6cb0") +

  geom_errorbarh(
    aes(xmin = conf.low, xmax = conf.high),
    height = 0.2,
    color = "#2b6cb0"
  ) +

  geom_vline(xintercept = 0, linetype = "dashed") +

  labs(
    x = "Effect of foreign expert (log-odds)",
    y = NULL,
    title = "Effect of foreign experts on directed sentiment"
  ) +

  theme_minimal(base_size = 13)
```

```{r}
library(dplyr)
library(ggplot2)
library(broom)

# Add period variable
master_dataset <- master_dataset %>%
  mutate(period = if_else(year < 2014, "Before 2014", "After 2014"))

# Function to run models for one period
run_models <- function(data, period_label) {
  model_west    <- glm(anti_west ~ foreign_expert + year,
                       data = data, family = binomial)
  model_russia  <- glm(anti_russia ~ foreign_expert + year,
                       data = data, family = binomial)
  model_ukraine <- glm(any_anti_ukraine ~ foreign_expert + year,
                       data = data, family = binomial)
  
  bind_rows(
    tidy(model_russia)  %>% mutate(Target = "Russia"),
    tidy(model_ukraine) %>% mutate(Target = "Ukraine"),
    tidy(model_west)    %>% mutate(Target = "West")
  ) %>%
    filter(term == "foreign_expert") %>%
    mutate(period = period_label)
}

# Run for each period
coef_df <- bind_rows(
  run_models(filter(master_dataset, year <  2014), "Before 2014"),
  run_models(filter(master_dataset, year >= 2014), "After 2014")
) %>%
  mutate(
    conf.low  = estimate - 1.96 * std.error,
    conf.high = estimate + 1.96 * std.error,
    Target    = factor(Target, levels = c("Russia", "Ukraine", "West")),
    period    = factor(period, levels = c("Before 2014", "After 2014"))
  )

# Plot
ggplot(coef_df, aes(x = estimate, y = Target, color = period, shape = period)) +
  geom_point(size = 3, position = position_dodge(width = 0.4)) +
  geom_errorbarh(
    aes(xmin = conf.low, xmax = conf.high),
    height = 0.2,
    position = position_dodge(width = 0.4)
  ) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey50") +
  scale_color_manual(
    values = c("Before 2014" = "grey60", "After 2014" = "#2b6cb0"),
    name = NULL
  ) +
  scale_shape_manual(
    values = c("Before 2014" = 21, "After 2014" = 16),
    name = NULL
  ) +
  labs(
    x     = "Effect of foreign expert (log-odds)",
    y     = NULL,
    title = "Effect of foreign experts on directed sentiment, before and after 2014"
  ) +
  theme_minimal(base_size = 13) +
  theme(legend.position = "top")
```

```{r}


set.seed(133)

validation_sample <- final_data_verify[
  sample(.N,1000) ,
  .(
    orig_row_id,
    text_en,
    person,
    mention_country,
    country_final,
    mention_country_confidence,
    mention_Country_source
  )
] 

write.csv(
  validation_sample,
  "validation_sample.csv",
  row.names = FALSE,
  fileEncoding = "UTF-8"
)

getwd()
```

```{r}


library(data.table)
set.seed(3.14)

# Split upfront
person_rows <- final_data_verify[!is.na(person)]
na_rows     <- final_data_verify[is.na(person)]

# Helper: sample up to n rows and tag stratum
take <- function(dt, n, label) {
  dt <- copy(dt)
  dt[, stratum := label]
  dt[sample(.N, min(.N, n))]
}

# Build strata
strata <- list(
  
  # Most important: low-confidence by key country
  take(person_rows[mention_country_confidence == 0 & 
                   country_final == "Russia"],          150, "conf0_Russia"),
  
  take(person_rows[mention_country_confidence == 0 & 
                   country_final == "Ukraine"],         150, "conf0_Ukraine"),
  
  take(person_rows[mention_country_confidence == 0 & 
                   !country_final %in% c("Russia", "Ukraine", 
                                         "Unknown", "")], 100, "conf0_other_foreign"),
  
  # Medium tier (norp-near / gpe-near)
  take(person_rows[mention_country_confidence >= 0.55 & 
                   mention_country_confidence <  0.70], 100, "conf_medium"),
  
  # High tier (syntax / org-embedded)
  take(person_rows[mention_country_confidence >= 0.70 & 
                   mention_country_confidence <  0.85], 150, "conf_high"),
  
  # Very high tier (org exact match)
  take(person_rows[mention_country_confidence >= 0.85], 100, "conf_very_high"),
  
  # NA rows for recall estimation
  take(na_rows, 250, "na_recall")
)

# Combine
validation_sample_strat <- rbindlist(strata)[, .(
  orig_row_id,
  text_en,
  person,
  mention_country,
  country_final,
  mention_country_confidence,
  mention_country_sources,   # lowercase c — check your column name
  stratum                   # keep this for per-stratum accuracy reporting
)]

# Verify stratum sizes (some may be smaller if data is limited)
validation_sample_strat[, .N, by = stratum]


write.csv(
  validation_sample_strat,
  "validation_sample_strat.csv",
  row.names = FALSE,
  fileEncoding = "UTF-8"
)
```

```{r}
library(ggplot2)
library(dplyr)


stages <- list(
  "Raw pipeline\n(pre-filter)" = data.frame(
    True = c("Non-expert", "Non-expert", "Expert", "Expert"),
    Predicted = c("Extracted", "Missed", "Extracted", "Missed"),
    n = c(218, 228, 532, 22),
    label = c("FP\n218", "TN\n~228", "TP\n532", "FN\n~22"),
    correct = c(FALSE, TRUE, TRUE, FALSE)
  ),
  "After manual\nfiltering" = data.frame(
    True = c("Non-expert", "Non-expert", "Expert", "Expert"),
    Predicted = c("Extracted", "Missed", "Extracted", "Missed"),
    n = c(83, 365, 530, 22),
    label = c("FP\n~83", "TN\n~365", "TP\n530", "FN\n~22"),
    correct = c(FALSE, TRUE, TRUE, FALSE)
  )
)

precision_vals <- c(
  "Raw pipeline\n(pre-filter)" = "Precision = 71%  |  Recall ≈ 91%  |  F1 ≈ 81%",
  "After manual\nfiltering"   = "Precision = 87%  |  Recall ≈ 91%"
)

plot_data <- bind_rows(
  lapply(names(stages), function(s) {
    stages[[s]] %>% mutate(stage = s)
  })
) %>%
  mutate(
    stage = factor(stage, levels = names(stages)),
    True = factor(True, levels = c("Non-expert", "Expert")),
    Predicted = factor(Predicted, levels = c("Extracted", "Missed")),
    prec_label = precision_vals[as.character(stage)]
  )

label_data <- plot_data %>%
  distinct(stage, prec_label) %>%
  mutate(
    True = factor("Expert", levels = c("Non-expert", "Expert")),
    Predicted = factor("Extracted", levels = c("Extracted", "Missed"))
  )

fig1 <- ggplot(plot_data, aes(x = Predicted, y = True, fill = correct)) +
  geom_tile(colour = "white", linewidth = 1.5) +
  geom_text(
    aes(label = label),
    size = 4.2,
    fontface = "bold",
    colour = "white",
    lineheight = 1.3
  ) +
  geom_text(
    data = label_data,
    aes(label = prec_label),
    x = 1.5,
    y = 0.35,
    size = 3.0,
    colour = "grey30",
    inherit.aes = FALSE
  ) +
  facet_wrap(~stage, nrow = 1) +
  scale_fill_manual(
    values = c("TRUE" = "grey30", "FALSE" = "grey70"),
    guide = "none"
  ) +
  scale_x_discrete(position = "top") +
  labs(
    x = "Pipeline output",
    y = "True classification",
    title = "Expert extraction performance"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    strip.text = element_text(face = "bold", size = 11),
    axis.text = element_text(size = 10),
    axis.title = element_text(size = 10, colour = "grey30"),
    panel.grid = element_blank(),
    plot.title = element_text(
      face = "bold", size = 12, hjust = 0.5, margin = margin(b = 10)
    ),
    panel.spacing = unit(2, "lines")
  )

fig1
ggsave("fig_cm_precision.pdf", fig1, width = 8, height = 4.5, device = cairo_pdf)
```

```{r}
library(ggplot2)
library(dplyr)

fd_data <- data.frame(
  True = factor(
    c("Domestic\n(Russian)", "Domestic\n(Russian)",
      "Foreign\n(Non-Russian)", "Foreign\n(Non-Russian)"),
    levels = c("Domestic\n(Russian)", "Foreign\n(Non-Russian)")
  ),
  Predicted = factor(
    c("Domestic\n(Russian)", "Foreign\n(Non-Russian)",
      "Domestic\n(Russian)", "Foreign\n(Non-Russian)"),
    levels = c("Domestic\n(Russian)", "Foreign\n(Non-Russian)")
  ),
  n = c(210, 111, 25, 186),
  correct = c(TRUE, FALSE, FALSE, TRUE),
  label = c(
    "TN\n210\n(65% recall)",
    "FN\n111\nTopic contamination:\nRussian experts in\nforeign-topic articles",
    "FP\n25",
    "TP\n186\n(88% recall)"
  )
)

# Summary metrics for annotation
metrics <- data.frame(
  x = 1.5,
  y = c(0.35, 0.20, 0.05),
  label = c(
    "Overall accuracy: 74%",
    "Foreign precision: 63%",
    "n = 532 valid experts"
  )
)

fig2 <- ggplot(fd_data, aes(x = Predicted, y = True, fill = correct)) +
  geom_tile(colour = "white", linewidth = 1.5) +
  geom_text(
    aes(label = label),
    size = 3.5, fontface = "bold", colour = "white", lineheight = 1.2
  ) +
  annotate(
    "text",
    x = metrics$x, y = metrics$y,
    label = metrics$label,
    size = 3.2, colour = "grey30"
  ) +
  scale_fill_manual(
    values = c("TRUE" = "#2166ac", "FALSE" = "#d73027"),
    guide = "none"
  ) +
  scale_x_discrete(position = "top") +
  labs(
    x = "Pipeline classification",
    y = "True classification",
    title = "Foreign/domestic classification accuracy"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    axis.text = element_text(size = 10),
    panel.grid = element_blank(),
    plot.title = element_text(face = "bold", size = 12, hjust = 0.5)
  )

fig2
ggsave("fig_cm_fd.pdf", fig2, width = 7, height = 5.5, device = cairo_pdf)
```

```{r}

library(ggplot2)
library(dplyr)

cal_data <- data.frame(
  tier = c(
    "Corpus-only\n(Russia, conf=0)",
    "High\n(conf ≥ 0.85)",
    "Medium\n(conf 0.70–0.84)",
    "Corpus-only\n(Ukraine, conf=0)",
    "Low\n(conf 0.55–0.69)",
    "Corpus-only\n(Other foreign, conf=0)"
  ),
  accuracy = c(0.95, 0.81, 0.69, 0.63, 0.69, 0.54),
  n = c(150, 100, 150, 150, 100, 100),
  tier_type = c(
    "Corpus-only", "Explicit signal", "Explicit signal",
    "Corpus-only", "Explicit signal", "Corpus-only"
  )
) %>%
  mutate(
    se = sqrt(accuracy * (1 - accuracy) / n),
    ci_lo = accuracy - 1.96 * se,
    ci_hi = accuracy + 1.96 * se,
    tier = factor(tier, levels = tier[order(accuracy)])
  )

fig3 <- ggplot(cal_data, aes(x = accuracy, y = tier, colour = tier_type)) +
  geom_vline(xintercept = 0.74, linetype = "dashed",
             colour = "grey50", linewidth = 0.7) +
  geom_vline(xintercept = 0.81, linetype = "dashed",
             colour = "#2166ac", linewidth = 0.7) +
  geom_errorbarh(
    aes(xmin = ci_lo, xmax = ci_hi),
    height = 0.25, linewidth = 0.8
  ) +
  geom_point(size = 4) +
  annotate(
    "text", x = 0.745, y = 0.5,
    label = "Overall\n74%",
    hjust = 0, size = 3, colour = "grey40"
  ) +
  annotate(
    "text", x = 0.815, y = 0.5,
    label = "Robustness\nthreshold\n81%",
    hjust = 0, size = 3, colour = "#2166ac"
  ) +
  annotate(
    "text",
    x = 0.96,
    y = "Corpus-only\n(Russia, conf=0)",
    label = "Corpus accumulation\nmore reliable than\nsingle-mention extraction",
    hjust = 1, size = 2.8, colour = "grey30", fontface = "italic"
  ) +
  scale_colour_manual(
    values = c("Corpus-only" = "#d73027", "Explicit signal" = "#2166ac"),
    name = "Signal type"
  ) +
  scale_x_continuous(
    limits = c(0.45, 1.0),
    labels = scales::percent_format(accuracy = 1),
    breaks = seq(0.5, 1.0, 0.1)
  ) +
  labs(
    x = "FD classification accuracy",
    y = NULL,
    title = "Classification accuracy by confidence tier",
    subtitle = "Error bars show 95% binomial confidence intervals"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    legend.position = "bottom",
    panel.grid.minor = element_blank(),
    panel.grid.major.y = element_blank(),
    axis.text.y = element_text(size = 9),
    plot.title = element_text(face = "bold", size = 12),
    plot.subtitle = element_text(size = 10, colour = "grey40")
  )

fig3

ggsave("fig_calibration.pdf", fig3, width = 8, height = 5.5, device = cairo_pdf)

```

```{r}

library(ggplot2)
library(tidyverse)

# Confusion matrix values
cm_data <- tibble(
  Predicted = factor(c("Expert", "Expert", "No expert", "No expert"),
                     levels = c("Expert", "No expert")),
  Actual    = factor(c("Expert", "No expert", "Expert", "No expert"),
                     levels = c("Expert", "No expert")),
  n         = c(695, 55, 16, 234),
  label     = c("TP = 695", "FP = 55", "FN = 16", "TN = 234")
)

# Precision, recall, F1 for subtitle
precision <- 695 / (695 + 55)
recall    <- 695 / (695 + 16)
f1        <- 2 * precision * recall / (precision + recall)

subtitle_text <- sprintf(
  "Precision = %.1f%%   Recall = %.1f%%   F1 = %.3f",
  precision * 100, recall * 100, f1
)

ggplot(cm_data, aes(x = Predicted, y = Actual, fill = n)) +
  geom_tile(colour = "white", linewidth = 1.2) +
  geom_text(aes(label = label), size = 5, fontface = "bold") +
  scale_fill_gradient(low = "white", high = "grey30",
                      name = "Count") +
  scale_x_discrete(position = "top") +
  labs(
    title    = "Expert extraction: confusion matrix",
    subtitle = subtitle_text,
    x        = "Predicted",
    y        = "Actual"
  ) +
  theme_minimal(base_size = 13) +
  theme(
    plot.title    = element_text(face = "bold", hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5, colour = "grey40"),
    axis.text     = element_text(size = 12),
     legend.position = "none",
    panel.grid    = element_blank()
  )

ggsave("plot1_person_confusion_matrix.png", width = 6, height = 4.5)

```

```{r}
library(ggplot2)
library(tidyverse)

plot_data <- tribble(
  ~stratum,             ~tier_label,               ~person_acc, ~country_acc, ~fd_acc, ~n_confirmed,
  "conf0_Russia",       "conf = 0\n(Russia)",       94.0,        50.0,         50.0,    6,
  "conf0_Ukraine",      "conf = 0\n(Ukraine)",      94.0,         3.6,          4.5,    56,
  "conf0_other",        "conf = 0\n(other)",        87.0,         0.0,          0.0,    19,
  "conf_medium",        "conf 0.55-0.70\n(medium)", 92.0,        88.0,         90.0,    92,
  "conf_high",          "conf 0.70-0.85\n(high)",   93.3,        86.4,         89.6,   140,
  "conf_very_high",     "conf >= 0.85\n(very high)",94.0,        86.2,         90.0,    94,
)

plot_long <- plot_data %>%
  pivot_longer(cols = c(person_acc, country_acc, fd_acc),
               names_to  = "metric",
               values_to = "accuracy") %>%
  mutate(
    metric = recode(metric,
                    "person_acc"  = "Person extraction",
                    "country_acc" = "Country attribution",
                    "fd_acc"      = "Foreign / domestic"),
    metric = factor(metric, levels = c("Person extraction",
                                       "Country attribution",
                                       "Foreign / domestic")),
    low_n      = n_confirmed < 30,
    tier_label = factor(tier_label, levels = plot_data$tier_label)
  )

solid_data  <- plot_long %>% filter(!low_n)
dotted_data <- plot_long %>% filter(low_n)

ggplot(plot_long, aes(x = tier_label, y = accuracy,
                      colour = metric, group = metric)) +
  geom_line(data = solid_data,  linewidth = 0.8, linetype = "solid") +
  geom_line(data = dotted_data, linewidth = 0.8, linetype = "dotted") +
  geom_point(aes(shape = low_n), size = 3.5, fill = "white", stroke = 1.2) +
  geom_hline(yintercept = 85, linetype = "dashed",
             colour = "grey50", linewidth = 0.5) +
  annotate("text", x = 5.8, y = 87,
           label = "85%", size = 3.2, colour = "grey50") +
  scale_shape_manual(values = c(`FALSE` = 16, `TRUE` = 21),
                     guide = "none") +
  scale_colour_manual(values = c("Person extraction"  = "#1a5276",
                                 "Country attribution" = "#c0392b",
                                 "Foreign / domestic"  = "#1e8449"),
                      name = NULL) +
  scale_y_continuous(limits = c(0, 100),
                     breaks = seq(0, 100, 20),
                     labels = function(x) paste0(x, "%")) +
  labs(
    title    = "Validation accuracy by confidence tier",
    subtitle = "Open points indicate fewer than 30 confirmed cases (high uncertainty)",
    x        = NULL,
    y        = "Accuracy (confirmed cases only)"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    plot.title         = element_text(face = "bold", hjust = 0.5),
    plot.subtitle      = element_text(hjust = 0.5, colour = "grey40", size = 9),
    legend.position    = "bottom",
    panel.grid.minor   = element_blank(),
    panel.grid.major.x = element_blank(),
    axis.text.x        = element_text(size = 9)
  )

ggsave("plot2_accuracy_by_confidence.pdf", width = 8, height = 5)
```

```{r}

library(ggplot2)
library(tidyverse)

# ── shared data ────────────────────────────────────────────────────────────────

all_data <- tribble(
  ~tier_label,                ~low_n, ~metric,              ~accuracy,
  "conf = 0\n(Russia)",       TRUE,   "Person extraction",   94.0,
  "conf = 0\n(Russia)",       TRUE,   "Country attribution", 50.0,
  "conf = 0\n(Russia)",       TRUE,   "Foreign / domestic",  50.0,
  "conf = 0\n(Ukraine)",      FALSE,  "Person extraction",   94.0,
  "conf = 0\n(Ukraine)",      FALSE,  "Country attribution",  3.6,
  "conf = 0\n(Ukraine)",      FALSE,  "Foreign / domestic",   4.5,
  "conf = 0\n(other)",        FALSE,  "Person extraction",   87.0,
  "conf = 0\n(other)",        FALSE,  "Country attribution",  0.0,
  "conf = 0\n(other)",        FALSE,  "Foreign / domestic",   0.0,
  "conf 0.55-0.70\n(medium)", FALSE,  "Person extraction",   92.0,
  "conf 0.55-0.70\n(medium)", FALSE,  "Country attribution", 88.0,
  "conf 0.55-0.70\n(medium)", FALSE,  "Foreign / domestic",  90.0,
  "conf 0.70-0.85\n(high)",   FALSE,  "Person extraction",   93.3,
  "conf 0.70-0.85\n(high)",   FALSE,  "Country attribution", 86.4,
  "conf 0.70-0.85\n(high)",   FALSE,  "Foreign / domestic",  89.6,
  "conf >= 0.85\n(very high)",FALSE,  "Person extraction",   94.0,
  "conf >= 0.85\n(very high)",FALSE,  "Country attribution", 86.2,
  "conf >= 0.85\n(very high)",FALSE,  "Foreign / domestic",  90.0,
) %>%
  mutate(
    metric     = factor(metric, levels = c("Person extraction",
                                           "Country attribution",
                                           "Foreign / domestic")),
    tier_label = factor(tier_label, levels = unique(tier_label))
  )

high_data <- all_data %>%
  filter(!str_detect(tier_label, "conf = 0")) %>%
  mutate(tier_label = factor(tier_label,
                             levels = c("conf 0.55-0.70\n(medium)",
                                        "conf 0.70-0.85\n(high)",
                                        "conf >= 0.85\n(very high)")))

colours <- c("Person extraction"  = "#1a5276",
             "Country attribution"= "#c0392b",
             "Foreign / domestic" = "#1e8449")

# ── Option B: dot plot, all tiers ─────────────────────────────────────────────

plotB <- ggplot(all_data,
                aes(x = accuracy, y = tier_label, colour = metric, shape = low_n)) +
  geom_vline(xintercept = 85, linetype = "dashed",
             colour = "grey60", linewidth = 0.5) +
  annotate("text", x = 86, y = 0.55, label = "85%",
           size = 3, colour = "grey50", hjust = 0) +
  geom_point(size = 4, stroke = 1.1,
             position = position_dodge(width = 0.4)) +
  scale_shape_manual(values = c(`TRUE` = 1, `FALSE` = 16),
                     labels = c(`TRUE`  = "Fewer than 30 confirmed cases",
                                `FALSE` = "30+ confirmed cases"),
                     name = NULL) +
  scale_colour_manual(values = colours, name = NULL) +
  scale_x_continuous(limits = c(0, 100),
                     breaks = seq(0, 100, 20),
                     labels = function(x) paste0(x, "%")) +
  scale_y_discrete(limits = rev) +
  labs(
    title    = "Validation accuracy by confidence tier",
    subtitle = "Hollow points indicate fewer than 30 confirmed cases",
    x        = "Accuracy (confirmed cases only)",
    y        = NULL
  ) +
  theme_minimal(base_size = 12) +
  theme(
    plot.title       = element_text(face = "bold", hjust = 0.5),
    plot.subtitle    = element_text(hjust = 0.5, colour = "grey40", size = 9),
    legend.position  = "bottom",
    legend.box       = "vertical",
    panel.grid.major.y = element_line(colour = "grey92"),
    panel.grid.major.x = element_line(colour = "grey92"),
    panel.grid.minor   = element_blank()
  )

plotB

ggsave("plotB_dot.pdf", plotB, width = 7, height = 5.5)


# ── Option C: dot plot, high-confidence tiers only ────────────────────────────

plotC <- ggplot(high_data,
                aes(x = accuracy, y = tier_label, colour = metric)) +
  geom_vline(xintercept = 85, linetype = "dashed",
             colour = "grey60", linewidth = 0.5) +
  annotate("text", x = 86, y = 0.55, label = "85%",
           size = 3, colour = "grey50", hjust = 0) +
  geom_point(size = 4.5,
             position = position_dodge(width = 0.4)) +
  geom_text(aes(label = paste0(round(accuracy, 1), "%")),
            position = position_dodge(width = 0.4),
            hjust = -0.35, size = 3.2, show.legend = FALSE) +
  scale_colour_manual(values = colours, name = NULL) +
  scale_x_continuous(limits = c(75, 100),
                     breaks = seq(75, 100, 5),
                     labels = function(x) paste0(x, "%")) +
  scale_y_discrete(limits = rev) +
  labs(
    title    = "Validation accuracy at conf \u2265 0.55",
    subtitle = "Confirmed cases only. Low-confidence (conf = 0) strata excluded.",
    x        = "Accuracy",
    y        = NULL
  ) +
  theme_minimal(base_size = 12) +
  theme(
    plot.title         = element_text(face = "bold", hjust = 0.5),
    plot.subtitle      = element_text(hjust = 0.5, colour = "grey40", size = 9),
    legend.position    = "bottom",
    panel.grid.major.y = element_line(colour = "grey92"),
    panel.grid.major.x = element_line(colour = "grey92"),
    panel.grid.minor   = element_blank()
  )

plotC
ggsave("plotC_dot_highconf.pdf", plotC, width = 6.5, height = 4)
```

```{r}
final_data_verify %>%
  mutate(
    # How was country_final determined?
    final_tier = case_when(
      is.na(person)                                      ~ "No extraction",
      country_final == "Unknown" | country_final == "" | 
        is.na(country_final)                             ~ "Unknown after overwrite",
      # Was it overwritten? i.e. mention_country_confidence == 0 
      # but country_final is not Unknown
      mention_country_confidence == 0 & 
        !is.na(country_final) & 
        country_final != "Unknown"                       ~ "conf = 0 (rescued by majority vote)",
      mention_country_confidence >= 0.55 & 
        mention_country_confidence < 0.70                ~ "conf 0.55-0.70",
      mention_country_confidence >= 0.70 & 
        mention_country_confidence < 0.85                ~ "conf 0.70-0.85",
      mention_country_confidence >= 0.85                 ~ "conf >= 0.85",
      TRUE                                               ~ "other"
    )
  ) %>%
  count(final_tier) %>%
  mutate(pct = n / sum(n) * 100) %>%
  arrange(desc(n)) %>%
  print()

final_data_verify %>%
  filter(mention_country_confidence == 0 & 
         !is.na(country_final) & 
         country_final != "Unknown") %>%
  count(country_final) %>%
  mutate(pct = n / sum(n) * 100) %>%
  arrange(desc(n)) %>%
  print(n = 20)
```

```{r}
library(ggplot2)
library(tidyverse)

# Confusion matrix values
# Restricted to conf_medium, conf_high, conf_very_high confirmed rows
# (conf0 strata excluded as they are not in the final analysis dataset)
cm_data <- tibble(
  Predicted = factor(c("Foreign", "Foreign", "Domestic", "Domestic"),
                     levels = c("Foreign", "Domestic")),
  Actual    = factor(c("Foreign", "Domestic", "Foreign", "Domestic"),
                     levels = c("Foreign", "Domestic")),
  n         = c(129, 25, 7, 154),
  label     = c("TP = 129", "FP = 25", "FN = 7", "TN = 154")
)

precision <- 129 / (129 + 25)
recall    <- 129 / (129 + 7)
f1        <- 2 * precision * recall / (precision + recall)
accuracy  <- (129 + 154) / (129 + 25 + 7 + 154)

subtitle_text <- sprintf(
  "Precision = %.1f%%   Recall = %.1f%%   Accuracy = %.1f%%   F1 = %.3f",
  precision * 100, recall * 100, accuracy * 100, f1
)

ggplot(cm_data, aes(x = Predicted, y = Actual, fill = n)) +
  geom_tile(colour = "white", linewidth = 1.2) +
  geom_text(aes(label = label), size = 5, fontface = "bold") +
  scale_fill_gradient(low = "white", high = "grey30") +
  scale_x_discrete(position = "top") +
  labs(
    title    = "Foreign/domestic classification: confusion matrix",
    subtitle = subtitle_text,
    x        = "Predicted",
    y        = "Actual"
  ) +
  theme_minimal(base_size = 13) +
  theme(
    plot.title    = element_text(face = "bold", hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5, colour = "grey40", size = 9),
    plot.caption  = element_text(colour = "grey50", size = 8, hjust = 0.5),
    axis.text     = element_text(size = 12),
    legend.position = "none",
    panel.grid    = element_blank()
  )

ggsave("plot3_fd_confusion_matrix.png", width = 6.5, height = 5)
```

```{r}
library(ggplot2)
library(tidyverse)
library(data.table)

# ── Top 10 foreign experts ────────────────────────────────────────────────────
top_foreign <- expert_topic_sentiment_master %>%
  filter(is_foreign_final == TRUE) %>%
  count(person, country_final, sort = TRUE) %>%
  slice_head(n = 20) %>%
  mutate(person = fct_reorder(person, n))

# ── Top 10 domestic experts ───────────────────────────────────────────────────
top_domestic <- expert_topic_sentiment_master %>%
  filter(is_foreign_final == FALSE) %>%
  count(person, country_final, sort = TRUE) %>%
  slice_head(n = 10) %>%
  mutate(person = fct_reorder(person, n))

# ── Plot foreign ──────────────────────────────────────────────────────────────
p_foreign <- ggplot(top_foreign,
                    aes(x = n, y = person, fill = country_final)) +
  geom_col(width = 0.7) +
  geom_text(aes(label = scales::comma(n)),
            hjust = -0.15, size = 3.2) +
  scale_x_continuous(expand = expansion(mult = c(0, 0.18)),
                     labels = scales::comma) +
  scale_fill_brewer(palette = "Set2", name = "Country") +
  labs(
    title    = "Top 10 most cited foreign experts",
    subtitle = "By total number of mentions in the analysis dataset",
    x        = "Number of mentions",
    y        = NULL
  ) +
  theme_minimal(base_size = 12) +
  theme(
    plot.title      = element_text(face = "bold", hjust = 0),
    plot.subtitle   = element_text(colour = "grey40", size = 9, hjust = 0),
    legend.position = "right",
    panel.grid.major.y = element_blank(),
    panel.grid.minor   = element_blank()
  )

p_foreign
ggsave("plot_top10_foreign.pdf", p_foreign, width = 7, height = 5)

# ── Plot domestic ─────────────────────────────────────────────────────────────
p_domestic <- ggplot(top_domestic,
                     aes(x = n, y = person)) +
  geom_col(width = 0.7, fill = "#2c7bb6") +
  geom_text(aes(label = scales::comma(n)),
            hjust = -0.15, size = 3.2) +
  scale_x_continuous(expand = expansion(mult = c(0, 0.18)),
                     labels = scales::comma) +
  labs(
    title    = "Top 10 most cited domestic experts",
    subtitle = "By total number of mentions in the analysis dataset",
    x        = "Number of mentions",
    y        = NULL
  ) +
  theme_minimal(base_size = 12) +
  theme(
    plot.title         = element_text(face = "bold", hjust = 0),
    plot.subtitle      = element_text(colour = "grey40", size = 9, hjust = 0),
    legend.position    = "none",
    panel.grid.major.y = element_blank(),
    panel.grid.minor   = element_blank()
  )

p_domestic
ggsave("plot_top10_domestic.pdf", p_domestic, width = 7, height = 5)
```

```{r}


```

```{r}
library(dplyr)
library(ggplot2)

# Define geopolitical topics
geo_topics <- c(
  "Ukraine war",
  "International geopolitics",
  "Military technology",
  "Energy and sanctions"
)

# Prepare data
topic_counts <- master_dataset %>%
  filter(dominant_topic_clean != "Other / no clear topic") %>%
  group_by(dominant_topic_clean) %>%
  summarise(
    foreign_expert_count = sum(foreign_expert, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(
    topic_group = if_else(
      dominant_topic_clean %in% geo_topics,
      "Geopolitical",
      "Other"
    )
  ) %>%
  arrange(desc(foreign_expert_count)) %>%
  mutate(
    dominant_topic_clean = factor(
      dominant_topic_clean,
      levels = rev(dominant_topic_clean)
    )
  )

# Plot
ggplot(topic_counts, aes(x = foreign_expert_count, y = dominant_topic_clean)) +
  
  geom_col(aes(fill = topic_group), width = 0.7) +
  
  scale_fill_manual(
    values = c(
      "Geopolitical" = "grey20",
      "Other" = "grey70"
    ),
    name = NULL
  ) +
  
  labs(
    x = "Number of articles with foreign expert",
    y = NULL,
    title = "Raw count of foreign expert use across topics"
  ) +
  
  theme_minimal(base_size = 13) +
  theme(
    plot.title = element_text(face = "bold"),
    panel.grid.minor = element_blank(),
    panel.grid.major.y = element_blank()
  )
```

## Manual validation subtest

```{r}

set.seed(3.14)  # optional, for reproducibility
sample_50 <- validation_results[sample(nrow(validation_results), 50), ]


write.csv(sample_50, "sample50.csv")
```

### Expert frequency robustness: h1

```{r}
library(dplyr)
library(modelsummary)
library(kableExtra)

# ── Data preparation ───────────────────────────────────────────────────────

h1_data <- master_dataset %>%
  filter(dominant_topic_clean != "Other / no clear topic") %>%
  mutate(
    dominant_topic_clean = relevel(
      factor(dominant_topic_clean),
      ref = "Courts and crime"
    ),
    post_2014 = as.integer(year >= 2014),
    post_2022 = as.integer(year >= 2022)
  )

h1_data_restricted <- h1_data %>%
  filter(expert_country_maxconf >= 0.85)

# ── Models ─────────────────────────────────────────────────────────────────

h1_m1 <- glm(foreign_expert ~ dominant_topic_clean,
             data   = h1_data,
             family = binomial)

h1_m2 <- glm(foreign_expert ~ dominant_topic_clean + year,
             data   = h1_data,
             family = binomial)

h1_m4 <- glm(foreign_expert ~ dominant_topic_clean + year,
             data   = h1_data_restricted,
             family = binomial)

h1_m5 <- glm(foreign_expert ~ dominant_topic_clean + post_2014 + post_2022,
             data   = h1_data,
             family = binomial)

# ── Coefficient map in block order ─────────────────────────────────────────

coef_map <- c(
  # Geopolitical block
  "dominant_topic_cleanInternational geopolitics" = "International geopolitics",
  "dominant_topic_cleanUkraine war"               = "Ukraine war",
  "dominant_topic_cleanMilitary technology"       = "Military technology",
  "dominant_topic_cleanEnergy and sanctions"      = "Energy and sanctions",
  # Domestic block
  "dominant_topic_cleanMacroeconomy"              = "Macroeconomy",
  "dominant_topic_cleanOpinion and commentary"    = "Opinion and commentary",
  "dominant_topic_cleanInformation services"      = "Information services",
  "dominant_topic_cleanMedia and society"         = "Media and society",
  "dominant_topic_cleanKremlin governance"        = "Kremlin governance",
  "dominant_topic_cleanHousing market"            = "Housing market",
  "dominant_topic_cleanDevelopment and education" = "Development and education",
  "dominant_topic_cleanCOVID-19 and health"       = "COVID-19 and health",
  "dominant_topic_cleanGeneral news"              = "General news",
  "dominant_topic_cleanRegional and local issues" = "Regional and local issues",
  # Controls
  "year"      = "Year (linear)",
  "post_2014" = "Post-2014",
  "post_2022" = "Post-2022"
)

# ── Table ──────────────────────────────────────────────────────────────────

modelsummary(
  list(
    "No controls"              = h1_m1,
    "+ Year (linear)"          = h1_m2,
    "Restricted (conf. 0.85+)" = h1_m4,
    "+ Era indicators"         = h1_m5
  ),
  estimate   = "{estimate} ({std.error}){stars}",
  statistic  = NULL,
  coef_map   = coef_map,
  gof_map    = c("nobs", "logLik"),
  stars      = c("*" = 0.05, "**" = 0.01, "***" = 0.001),
  title      = "H1: Foreign expert presence across topics",
  notes      = c(
    "Log-odds coefficients with standard errors in parentheses.",
    "Baseline: Courts and crime topic, domestic expert.",
    "Restricted column uses observations where expert_country_maxconf >= 0.85.",
    "Era indicators: Post-2014 and Post-2022 are binary variables marking",
    "the editorial transformation and the full-scale invasion respectively.",
    "* p < 0.05, ** p < 0.01, *** p < 0.001"
  ),
  output     = "kableExtra"
) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width        = FALSE,
    font_size         = 12
  ) %>%
  pack_rows(
    "Geopolitical topics",
    start_row  = 1,
    end_row    = 4,
    bold       = TRUE,
    background = "#e8f0f7"
  ) %>%
  pack_rows(
    "Domestic / other topics",
    start_row  = 5,
    end_row    = 14,
    bold       = TRUE,
    background = "#f7f0e8"
  ) %>%
  pack_rows(
    "Controls",
    start_row  = 15,
    end_row    = 17,
    bold       = FALSE,
    background = "#f5f5f5"
  ) %>%
  add_header_above(
    c(" "           = 1,
      "Main models" = 2,
      "Robustness"  = 2)
  ) %>%
  column_spec(4, background = "#fafafa", italic = TRUE) %>%
  column_spec(5, background = "#fafafa", italic = TRUE)


library(broom)

# Extract tidy results from all three models
m1_tidy <- tidy(h1_m1) %>% mutate(model = "No controls")
m2_tidy <- tidy(h1_m2) %>% mutate(model = "+ Year")
m4_tidy <- tidy(h1_m4) %>% mutate(model = "Robustness")

all_results <- bind_rows(m1_tidy, m2_tidy, m4_tidy) %>%
  select(model, term, estimate, std.error, p.value)

print(all_results, n = 100)

summary(h1_m2)
summary(h1_m4)

# ── Mention frequency robustness ───────────────────────────────────────────

# Count unique articles per expert (not raw mentions)
expert_article_counts <- master_dataset %>%
  distinct(expert_id, row_id) %>%
  count(expert_id, name = "n_articles")

# Join back to h1_data
h1_data <- h1_data %>%
  left_join(expert_article_counts, by = "expert_id") %>%
  mutate(
    inv_freq_weight = 1 / n_articles,
    freq_bin = case_when(
      n_articles == 1        ~ "Single mention",
      n_articles <= 5        ~ "2-5 articles",
      n_articles <= 20       ~ "6-20 articles",
      TRUE                   ~ "20+ articles"
    )
  )

# Model 1: Restricted to experts appearing in 5 or fewer articles
h1_data_rare <- h1_data %>% filter(n_articles <= 5)

h1_m_rare <- glm(foreign_expert ~ dominant_topic_clean + year,
                 data   = h1_data_rare,
                 family = binomial)

# Model 2: Inverse frequency weighted
h1_m_weighted <- glm(foreign_expert ~ dominant_topic_clean + year,
                     data    = h1_data,
                     family  = binomial,
                     weights = inv_freq_weight)

# ── Table ──────────────────────────────────────────────────────────────────

modelsummary(
  list(
    "Main"                     = h1_m2,
    "Rare experts (≤5 articles)" = h1_m_rare,
    "Inverse frequency weighted" = h1_m_weighted
  ),
  estimate  = "{estimate} ({std.error}){stars}",
  statistic = NULL,
  coef_map  = coef_map,
  gof_map   = c("nobs", "logLik"),
  stars     = c("*" = 0.05, "**" = 0.01, "***" = 0.001),
  title     = "H1 Robustness: Mention frequency",
  notes     = c(
    "Log-odds coefficients with standard errors in parentheses.",
    "Baseline: Courts and crime topic.",
    "Mention frequency counted as distinct articles per expert_id.",
    "Rare experts column restricts to experts appearing in 5 or fewer articles.",
    "Weighted column uses inverse article frequency as observation weight.",
    "* p < 0.05, ** p < 0.01, *** p < 0.001"
  ),
  output    = "kableExtra"
) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width        = FALSE,
    font_size         = 12
  ) %>%
  pack_rows("Geopolitical topics",    1,  4, bold = TRUE, background = "#e8f0f7") %>%
  pack_rows("Domestic / other topics", 5, 14, bold = TRUE, background = "#f7f0e8") %>%
  pack_rows("Controls",              15, 15, bold = FALSE, background = "#f5f5f5")

```

### Expert Frequency robustness: H2

```{r}
library(dplyr)
library(modelsummary)
library(kableExtra)

# ── Data preparation ───────────────────────────────────────────────────────

h2_data <- master_dataset %>%
  filter(dominant_topic_clean != "Other / no clear topic") %>%
  mutate(
    topic_block = factor(
      if_else(topic_group == "geopolitics", "Geopolitical", "Domestic / other"),
      levels = c("Domestic / other", "Geopolitical")
    )
  )

h2_data_restricted <- h2_data %>%
  filter(expert_country_maxconf >= 0.85)

# ── Models ─────────────────────────────────────────────────────────────────

# Main models
h2_aw  <- glm(anti_west            ~ foreign_expert + topic_block + year,
              data = h2_data, family = binomial)
h2_au  <- glm(anti_ukraine         ~ foreign_expert + topic_block + year,
              data = h2_data, family = binomial)
h2_puk <- glm(any_positive_ukraine ~ foreign_expert + topic_block + year,
              data = h2_data, family = binomial)
h2_ar  <- glm(anti_russia          ~ foreign_expert + topic_block + year,
              data = h2_data, family = binomial)
h2_pw  <- glm(any_positive_west    ~ foreign_expert + topic_block + year,
              data = h2_data, family = binomial)
h2_pr  <- glm(any_positive_russia  ~ foreign_expert + topic_block + year,
              data = h2_data, family = binomial)

# Robustness models
h2_aw_r  <- glm(anti_west            ~ foreign_expert + topic_block + year,
                data = h2_data_restricted, family = binomial)
h2_au_r  <- glm(anti_ukraine         ~ foreign_expert + topic_block + year,
                data = h2_data_restricted, family = binomial)
h2_puk_r <- glm(any_positive_ukraine ~ foreign_expert + topic_block + year,
                data = h2_data_restricted, family = binomial)
h2_ar_r  <- glm(anti_russia          ~ foreign_expert + topic_block + year,
                data = h2_data_restricted, family = binomial)
h2_pw_r  <- glm(any_positive_west    ~ foreign_expert + topic_block + year,
                data = h2_data_restricted, family = binomial)
h2_pr_r  <- glm(any_positive_russia  ~ foreign_expert + topic_block + year,
                data = h2_data_restricted, family = binomial)

# ── Raw outcome counts for footer ─────────────────────────────────────────

outcome_counts <- h2_data %>%
  summarise(
    aw  = sum(anti_west,            na.rm = TRUE),
    au  = sum(anti_ukraine,         na.rm = TRUE),
    puk = sum(any_positive_ukraine, na.rm = TRUE),
    ar  = sum(anti_russia,          na.rm = TRUE),
    pw  = sum(any_positive_west,    na.rm = TRUE),
    pr  = sum(any_positive_russia,  na.rm = TRUE)
  )

counts_note <- paste0(
  "Outcome event counts (full sample): ",
  "Anti-West = ",    outcome_counts$aw,  ", ",
  "Anti-Ukraine = ", outcome_counts$au,  ", ",
  "Pro-Ukraine = ",  outcome_counts$puk, ", ",
  "Anti-Russia = ",  outcome_counts$ar,  ", ",
  "Pro-West = ",     outcome_counts$pw,  ", ",
  "Pro-Russia = ",   outcome_counts$pr,  "."
)

# ── Coefficient map ────────────────────────────────────────────────────────

coef_map <- c(
  "foreign_expert"          = "Foreign expert",
  "topic_blockGeopolitical" = "Topic: Geopolitical",
  "year"                    = "Year"
)

# ── Table ──────────────────────────────────────────────────────────────────

modelsummary(
  list(
    "Anti-West"    = h2_aw,
    "Anti-Ukraine" = h2_au,
    "Pro-Ukraine"  = h2_puk,
    "Anti-Russia"  = h2_ar,
    "Pro-West"     = h2_pw,
    "Pro-Russia"   = h2_pr,
    "Anti-West"    = h2_aw_r,
    "Anti-Ukraine" = h2_au_r,
    "Pro-Ukraine"  = h2_puk_r,
    "Anti-Russia"  = h2_ar_r,
    "Pro-West"     = h2_pw_r,
    "Pro-Russia"   = h2_pr_r
  ),
  estimate   = "{estimate} ({std.error}){stars}",
  statistic  = NULL,
  coef_map   = coef_map,
  gof_map    = c("nobs", "logLik"),
  stars      = c("*" = 0.05, "**" = 0.01, "***" = 0.001),
  title      = "H2: Foreign expert evaluative profile across sentiment targets",
  notes      = c(
    "Log-odds coefficients with standard errors in parentheses.",
    "Baseline: domestic expert, domestic/other topic.",
    "Robustness columns restricted to expert_country_maxconf >= 0.85.",
    counts_note,
    "* p < 0.05, ** p < 0.01, *** p < 0.001"
  ),
  output     = "kableExtra"
) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width        = FALSE,
    font_size         = 12
  ) %>%
  add_header_above(
    c(" "                          = 1,
      "Main models"                = 6,
      "Robustness (conf. 0.85+)"   = 6)
  ) %>%
  row_spec(1, bold = TRUE, background = "#e8f0f7") %>%
  column_spec(8:13, background = "#fafafa", italic = TRUE)

library(broom)

models_main <- list(
  anti_west    = h2_aw,
  anti_ukraine = h2_au,
  pro_ukraine  = h2_puk,
  anti_russia  = h2_ar,
  pro_west     = h2_pw,
  pro_russia   = h2_pr
)

models_rob <- list(
  anti_west_r    = h2_aw_r,
  anti_ukraine_r = h2_au_r,
  pro_ukraine_r  = h2_puk_r,
  anti_russia_r  = h2_ar_r,
  pro_west_r     = h2_pw_r,
  pro_russia_r   = h2_pr_r
)

all_h2 <- bind_rows(
  lapply(names(models_main), function(n)
    tidy(models_main[[n]]) %>% mutate(model = n)),
  lapply(names(models_rob), function(n)
    tidy(models_rob[[n]]) %>% mutate(model = n))
) %>%
  filter(term %in% c("foreign_expert",
                     "topic_blockGeopolitical",
                     "year")) %>%
  select(model, term, estimate, std.error, p.value)

print(all_h2, n = 100)

print(outcome_counts)

# ── Mention frequency robustness for H2 ───────────────────────────────────

# Reuse expert_article_counts from H1 section
# (if running independently, recompute here)
expert_article_counts <- master_dataset %>%
  distinct(expert_id, row_id) %>%
  count(expert_id, name = "n_articles")

h2_data <- h2_data %>%
  left_join(expert_article_counts, by = "expert_id") %>%
  mutate(inv_freq_weight = 1 / n_articles)

# Rare experts dataset
h2_data_rare <- h2_data %>% filter(n_articles <= 5)

# ── Rare experts models ────────────────────────────────────────────────────

h2_aw_rare  <- glm(anti_west            ~ foreign_expert + topic_block + year,
                   data = h2_data_rare, family = binomial)
h2_au_rare  <- glm(anti_ukraine         ~ foreign_expert + topic_block + year,
                   data = h2_data_rare, family = binomial)
h2_puk_rare <- glm(any_positive_ukraine ~ foreign_expert + topic_block + year,
                   data = h2_data_rare, family = binomial)
h2_ar_rare  <- glm(anti_russia          ~ foreign_expert + topic_block + year,
                   data = h2_data_rare, family = binomial)
h2_pw_rare  <- glm(any_positive_west    ~ foreign_expert + topic_block + year,
                   data = h2_data_rare, family = binomial)
h2_pr_rare  <- glm(any_positive_russia  ~ foreign_expert + topic_block + year,
                   data = h2_data_rare, family = binomial)

# ── Inverse frequency weighted models ─────────────────────────────────────

h2_aw_wt  <- glm(anti_west            ~ foreign_expert + topic_block + year,
                 data = h2_data, family = binomial, weights = inv_freq_weight)
h2_au_wt  <- glm(anti_ukraine         ~ foreign_expert + topic_block + year,
                 data = h2_data, family = binomial, weights = inv_freq_weight)
h2_puk_wt <- glm(any_positive_ukraine ~ foreign_expert + topic_block + year,
                 data = h2_data, family = binomial, weights = inv_freq_weight)
h2_ar_wt  <- glm(anti_russia          ~ foreign_expert + topic_block + year,
                 data = h2_data, family = binomial, weights = inv_freq_weight)
h2_pw_wt  <- glm(any_positive_west    ~ foreign_expert + topic_block + year,
                 data = h2_data, family = binomial, weights = inv_freq_weight)
h2_pr_wt  <- glm(any_positive_russia  ~ foreign_expert + topic_block + year,
                 data = h2_data, family = binomial, weights = inv_freq_weight)

# ── Outcome counts for rare sample ────────────────────────────────────────

counts_rare <- h2_data_rare %>%
  summarise(
    aw  = sum(anti_west,            na.rm = TRUE),
    au  = sum(anti_ukraine,         na.rm = TRUE),
    puk = sum(any_positive_ukraine, na.rm = TRUE),
    ar  = sum(anti_russia,          na.rm = TRUE),
    pw  = sum(any_positive_west,    na.rm = TRUE),
    pr  = sum(any_positive_russia,  na.rm = TRUE)
  )

counts_rare_note <- paste0(
  "Outcome event counts (rare experts sample, n_articles <= 5): ",
  "Anti-West = ",    counts_rare$aw,  ", ",
  "Anti-Ukraine = ", counts_rare$au,  ", ",
  "Pro-Ukraine = ",  counts_rare$puk, ", ",
  "Anti-Russia = ",  counts_rare$ar,  ", ",
  "Pro-West = ",     counts_rare$pw,  ", ",
  "Pro-Russia = ",   counts_rare$pr,  "."
)

# ── Table ──────────────────────────────────────────────────────────────────

modelsummary(
  list(
    "Anti-West"    = h2_aw,
    "Anti-Ukraine" = h2_au,
    "Pro-Ukraine"  = h2_puk,
    "Anti-Russia"  = h2_ar,
    "Pro-West"     = h2_pw,
    "Pro-Russia"   = h2_pr,
    "Anti-West"    = h2_aw_rare,
    "Anti-Ukraine" = h2_au_rare,
    "Pro-Ukraine"  = h2_puk_rare,
    "Anti-Russia"  = h2_ar_rare,
    "Pro-West"     = h2_pw_rare,
    "Pro-Russia"   = h2_pr_rare,
    "Anti-West"    = h2_aw_wt,
    "Anti-Ukraine" = h2_au_wt,
    "Pro-Ukraine"  = h2_puk_wt,
    "Anti-Russia"  = h2_ar_wt,
    "Pro-West"     = h2_pw_wt,
    "Pro-Russia"   = h2_pr_wt
  ),
  estimate  = "{estimate} ({std.error}){stars}",
  statistic = NULL,
  coef_map  = coef_map,
  gof_map   = c("nobs", "logLik"),
  stars     = c("*" = 0.05, "**" = 0.01, "***" = 0.001),
  title     = "H2 Robustness: Mention frequency",
  notes     = c(
    "Log-odds coefficients with standard errors in parentheses.",
    "Baseline: domestic expert, domestic/other topic.",
    "Rare experts column restricts to experts appearing in 5 or fewer articles.",
    "Weighted column uses inverse article frequency as observation weight.",
    counts_note,
    counts_rare_note,
    "* p < 0.05, ** p < 0.01, *** p < 0.001"
  ),
  output    = "kableExtra"
) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width        = FALSE,
    font_size         = 10
  ) %>%
  add_header_above(
    c(" "                            = 1,
      "Main models"                  = 6,
      "Rare experts (≤5 articles)"   = 6,
      "Inverse frequency weighted"   = 6)
  ) %>%
  row_spec(1, bold = TRUE, background = "#e8f0f7") %>%
  column_spec(8:13,  background = "#fafafa", italic = TRUE) %>%
  column_spec(14:19, background = "#f0f0f0", italic = TRUE)
```

### Expert Frequency robustness: H3

```{r}

library(modelsummary)
library(kableExtra)
# ── Data preparation ───────────────────────────────────────────────────────
h3_data <- master_dataset %>%
  filter(dominant_topic_clean != "Other / no clear topic") %>%
  mutate(
    topic_block = factor(
      if_else(topic_group == "geopolitics", "Geopolitical", "Domestic / other"),
      levels = c("Domestic / other", "Geopolitical")
    )
  )
h3_data_restricted <- h3_data %>%
  filter(expert_country_maxconf >= 0.85)
# ── Models ─────────────────────────────────────────────────────────────────
h3_m1 <- glm(anti_west ~ foreign_expert + topic_block,
             data   = h3_data,
             family = binomial)
h3_m2 <- glm(anti_west ~ foreign_expert + topic_block + year,
             data   = h3_data,
             family = binomial)
h3_m3 <- glm(anti_west ~ foreign_expert * topic_block + year,
             data   = h3_data,
             family = binomial)
h3_m4 <- glm(anti_west ~ foreign_expert * topic_block + year,
             data   = h3_data_restricted,
             family = binomial)
# ── Coefficient map ────────────────────────────────────────────────────────
coef_map <- c(
  "foreign_expert"                        = "Foreign expert",
  "topic_blockGeopolitical"               = "Topic: Geopolitical",
  "foreign_expert:topic_blockGeopolitical" = "Foreign expert x Geopolitical",
  "year"                                  = "Year"
)
# ── Table ──────────────────────────────────────────────────────────────────
modelsummary(
  list(
    "No controls"          = h3_m1,
    "+ Year"               = h3_m2,
    "+ Interaction"        = h3_m3,
    "Restricted (conf. 0.85+)" = h3_m4
  ),
  estimate   = "{estimate} ({std.error}){stars}",
  statistic  = NULL,
  coef_map   = coef_map,
  gof_map    = c("nobs", "logLik"),
  stars      = c("*" = 0.05, "**" = 0.01, "***" = 0.001),
  title      = "H3: Foreign expert anti-West framing across topic contexts",
  notes      = c(
    "Log-odds coefficients with standard errors in parentheses.",
    "Baseline: domestic expert, domestic/other topic.",
    "Foreign expert coefficient captures the effect in the domestic/other baseline.",
    "Interaction term shows how this effect differs in geopolitical topics.",
    "Column 4 restricted to observations where expert_country_maxconf >= 0.85.",
    "* p < 0.05, ** p < 0.01, *** p < 0.001"
  ),
  output     = "kableExtra"
) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width        = FALSE,
    font_size         = 12
  ) %>%
  add_header_above(
    c(" "           = 1,
      "Main models" = 3,
      "Robustness"  = 1)
  ) %>%
  row_spec(1, bold = TRUE, background = "
#e8f0f7") %>%
  row_spec(3, bold = TRUE, background = "
#e8f0f7") %>%
  column_spec(5, background = "
#fafafa", italic = TRUE)
all_h3 <- bind_rows(
  lapply(list(h3_m1, h3_m2, h3_m3, h3_m4),
         function(m) tidy(m)) %>%
    bind_rows(.id = "model")
) %>%
  select(model, term, estimate, std.error, p.value)
print(all_h3, n = 100)

# ── Mention frequency robustness for H3 ───────────────────────────────────

# Reuse expert_article_counts from H1/H2 section
h3_data <- h3_data %>%
  left_join(expert_article_counts, by = "expert_id") %>%
  mutate(inv_freq_weight = 1 / n_articles)

# Rare experts dataset
h3_data_rare <- h3_data %>% filter(n_articles <= 5)

# ── Models ─────────────────────────────────────────────────────────────────

# Rare experts
h3_m_rare <- glm(anti_west ~ foreign_expert * topic_block + year,
                 data   = h3_data_rare,
                 family = binomial)

# Inverse frequency weighted
h3_m_weighted <- glm(anti_west ~ foreign_expert * topic_block + year,
                     data    = h3_data,
                     family  = binomial,
                     weights = inv_freq_weight)

# ── Table ──────────────────────────────────────────────────────────────────

modelsummary(
  list(
    "No controls"                = h3_m1,
    "+ Year"                     = h3_m2,
    "+ Interaction"              = h3_m3,
    "Restricted (conf. 0.85+)"   = h3_m4,
    "Rare experts (≤5 articles)" = h3_m_rare,
    "Inverse frequency weighted" = h3_m_weighted
  ),
  estimate  = "{estimate} ({std.error}){stars}",
  statistic = NULL,
  coef_map  = coef_map,
  gof_map   = c("nobs", "logLik"),
  stars     = c("*" = 0.05, "**" = 0.01, "***" = 0.001),
  title     = "H3 Robustness: Mention frequency",
  notes     = c(
    "Log-odds coefficients with standard errors in parentheses.",
    "Baseline: domestic expert, domestic/other topic.",
    "Foreign expert coefficient captures the association in the domestic/other baseline.",
    "Interaction term shows how this differs in geopolitical topics.",
    "Rare experts column restricts to experts appearing in 5 or fewer articles.",
    "Weighted column uses inverse article frequency as observation weight.",
    "* p < 0.05, ** p < 0.01, *** p < 0.001"
  ),
  output    = "kableExtra"
) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width        = FALSE,
    font_size         = 12
  ) %>%
  add_header_above(
    c(" "           = 1,
      "Main models" = 3,
      "Robustness"  = 3)
  ) %>%
  row_spec(1, bold = TRUE, background = "#e8f0f7") %>%
  row_spec(3, bold = TRUE, background = "#e8f0f7") %>%
  column_spec(5:7, background = "#fafafa", italic = TRUE)
```

### Robustness Ukraine excluded H1 to H3

```{r}
# ── Exclude Ukrainian-attributed experts ───────────────────────────────────

# For H1
h1_data_no_ukr <- h1_data %>%
  filter(expert_country_master != "Ukraine")

h1_m2_no_ukr <- glm(foreign_expert ~ dominant_topic_clean + year,
                    data   = h1_data_no_ukr,
                    family = binomial)

# For H2
h2_data_no_ukr <- h2_data %>%
  filter(expert_country_master != "Ukraine")

h2_aw_no_ukr  <- glm(anti_west            ~ foreign_expert + topic_block + year,
                     data = h2_data_no_ukr, family = binomial)
h2_au_no_ukr  <- glm(anti_ukraine         ~ foreign_expert + topic_block + year,
                     data = h2_data_no_ukr, family = binomial)
h2_puk_no_ukr <- glm(any_positive_ukraine ~ foreign_expert + topic_block + year,
                     data = h2_data_no_ukr, family = binomial)
h2_ar_no_ukr  <- glm(anti_russia          ~ foreign_expert + topic_block + year,
                     data = h2_data_no_ukr, family = binomial)
h2_pw_no_ukr  <- glm(any_positive_west    ~ foreign_expert + topic_block + year,
                     data = h2_data_no_ukr, family = binomial)
h2_pr_no_ukr  <- glm(any_positive_russia  ~ foreign_expert + topic_block + year,
                     data = h2_data_no_ukr, family = binomial)

# For H3
h3_data_no_ukr <- h3_data %>%
  filter(expert_country_master != "Ukraine")

h3_m3_no_ukr <- glm(anti_west ~ foreign_expert * topic_block + year,
                    data   = h3_data_no_ukr,
                    family = binomial)

# ── H1 table ───────────────────────────────────────────────────────────────

coef_map_h1 <- c(
  "dominant_topic_cleanInternational geopolitics" = "International geopolitics",
  "dominant_topic_cleanUkraine war"               = "Ukraine war",
  "dominant_topic_cleanMilitary technology"       = "Military technology",
  "dominant_topic_cleanEnergy and sanctions"      = "Energy and sanctions",
  "dominant_topic_cleanMacroeconomy"              = "Macroeconomy",
  "dominant_topic_cleanOpinion and commentary"    = "Opinion and commentary",
  "dominant_topic_cleanInformation services"      = "Information services",
  "dominant_topic_cleanMedia and society"         = "Media and society",
  "dominant_topic_cleanKremlin governance"        = "Kremlin governance",
  "dominant_topic_cleanHousing market"            = "Housing market",
  "dominant_topic_cleanDevelopment and education" = "Development and education",
  "dominant_topic_cleanCOVID-19 and health"       = "COVID-19 and health",
  "dominant_topic_cleanGeneral news"              = "General news",
  "dominant_topic_cleanRegional and local issues" = "Regional and local issues",
  "year"                                          = "Year (linear)"
)

modelsummary(
  list(
    "Main (+ Year)"        = h1_m2,
    "Excluding Ukrainians" = h1_m2_no_ukr
  ),
  estimate  = "{estimate} ({std.error}){stars}",
  statistic = NULL,
  coef_map  = coef_map_h1,
  gof_map   = c("nobs", "logLik"),
  stars     = c("*" = 0.05, "**" = 0.01, "***" = 0.001),
  title     = "H1 Robustness: Excluding Ukrainian-attributed experts",
  notes     = c(
    "Log-odds coefficients with standard errors in parentheses.",
    "Baseline: Courts and crime topic.",
    "Excluding Ukrainian-attributed experts addresses the systematic",
    "misattribution of Russian domestic experts to Ukraine documented",
    "in the validation analysis (Appendix C).",
    "* p < 0.05, ** p < 0.01, *** p < 0.001"
  ),
  output    = "kableExtra"
) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width        = FALSE,
    font_size         = 12
  ) %>%
  pack_rows("Geopolitical topics",     1,  4, bold = TRUE, background = "#e8f0f7") %>%
  pack_rows("Domestic / other topics", 5, 14, bold = TRUE, background = "#f7f0e8") %>%
  pack_rows("Controls",               15, 15, bold = FALSE, background = "#f5f5f5") %>%
  column_spec(3, background = "#fafafa", italic = TRUE)

# ── H2 table ───────────────────────────────────────────────────────────────

counts_no_ukr <- h2_data_no_ukr %>%
  summarise(
    aw  = sum(anti_west,            na.rm = TRUE),
    au  = sum(anti_ukraine,         na.rm = TRUE),
    puk = sum(any_positive_ukraine, na.rm = TRUE),
    ar  = sum(anti_russia,          na.rm = TRUE),
    pw  = sum(any_positive_west,    na.rm = TRUE),
    pr  = sum(any_positive_russia,  na.rm = TRUE)
  )

counts_no_ukr_note <- paste0(
  "Outcome event counts (excluding Ukrainians): ",
  "Anti-West = ",    counts_no_ukr$aw,  ", ",
  "Anti-Ukraine = ", counts_no_ukr$au,  ", ",
  "Pro-Ukraine = ",  counts_no_ukr$puk, ", ",
  "Anti-Russia = ",  counts_no_ukr$ar,  ", ",
  "Pro-West = ",     counts_no_ukr$pw,  ", ",
  "Pro-Russia = ",   counts_no_ukr$pr,  "."
)

coef_map_h2 <- c(
  "foreign_expert"          = "Foreign expert",
  "topic_blockGeopolitical" = "Topic: Geopolitical",
  "year"                    = "Year"
)

modelsummary(
  list(
    "Anti-West"    = h2_aw,
    "Anti-Ukraine" = h2_au,
    "Pro-Ukraine"  = h2_puk,
    "Anti-Russia"  = h2_ar,
    "Pro-West"     = h2_pw,
    "Pro-Russia"   = h2_pr,
    "Anti-West"    = h2_aw_no_ukr,
    "Anti-Ukraine" = h2_au_no_ukr,
    "Pro-Ukraine"  = h2_puk_no_ukr,
    "Anti-Russia"  = h2_ar_no_ukr,
    "Pro-West"     = h2_pw_no_ukr,
    "Pro-Russia"   = h2_pr_no_ukr
  ),
  estimate  = "{estimate} ({std.error}){stars}",
  statistic = NULL,
  coef_map  = coef_map_h2,
  gof_map   = c("nobs", "logLik"),
  stars     = c("*" = 0.05, "**" = 0.01, "***" = 0.001),
  title     = "H2 Robustness: Excluding Ukrainian-attributed experts",
  notes     = c(
    "Log-odds coefficients with standard errors in parentheses.",
    "Baseline: domestic expert, domestic/other topic.",
    "Excluding Ukrainian-attributed experts addresses the systematic",
    "misattribution of Russian domestic experts to Ukraine documented",
    "in the validation analysis (Appendix C).",
    counts_note,
    counts_no_ukr_note,
    "* p < 0.05, ** p < 0.01, *** p < 0.001"
  ),
  output    = "kableExtra"
) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width        = FALSE,
    font_size         = 10
  ) %>%
  add_header_above(
    c(" "                            = 1,
      "Main models"                  = 6,
      "Excluding Ukrainians"         = 6)
  ) %>%
  row_spec(1, bold = TRUE, background = "#e8f0f7") %>%
  column_spec(8:13, background = "#fafafa", italic = TRUE)

# ── H3 table ───────────────────────────────────────────────────────────────

coef_map_h3 <- c(
  "foreign_expert"                         = "Foreign expert",
  "topic_blockGeopolitical"                = "Topic: Geopolitical",
  "foreign_expert:topic_blockGeopolitical" = "Foreign expert x Geopolitical",
  "year"                                   = "Year"
)

modelsummary(
  list(
    "Main (+ Interaction)"  = h3_m3,
    "Excluding Ukrainians"  = h3_m3_no_ukr
  ),
  estimate  = "{estimate} ({std.error}){stars}",
  statistic = NULL,
  coef_map  = coef_map_h3,
  gof_map   = c("nobs", "logLik"),
  stars     = c("*" = 0.05, "**" = 0.01, "***" = 0.001),
  title     = "H3 Robustness: Excluding Ukrainian-attributed experts",
  notes     = c(
    "Log-odds coefficients with standard errors in parentheses.",
    "Baseline: domestic expert, domestic/other topic.",
    "Foreign expert coefficient captures the association in the",
    "domestic/other baseline. Interaction term shows how this",
    "differs in geopolitical topics.",
    "Excluding Ukrainian-attributed experts addresses the systematic",
    "misattribution of Russian domestic experts to Ukraine documented",
    "in the validation analysis (Appendix C).",
    "* p < 0.05, ** p < 0.01, *** p < 0.001"
  ),
  output    = "kableExtra"
) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width        = FALSE,
    font_size         = 12
  ) %>%
  row_spec(1, bold = TRUE, background = "#e8f0f7") %>%
  row_spec(3, bold = TRUE, background = "#e8f0f7") %>%
  column_spec(3, background = "#fafafa", italic = TRUE)
```

### Robustness academics only H1 to H3

```{r}
# ── Academic experts only robustness ──────────────────────────────────────

# For H1
h1_data_academic <- h1_data %>%
  filter(role_class == "academic_expert")

h1_m2_academic <- glm(foreign_expert ~ dominant_topic_clean + year,
                      data   = h1_data_academic,
                      family = binomial)

# For H2
h2_data_academic <- h2_data %>%
  filter(role_class == "academic_expert")

h2_aw_academic  <- glm(anti_west     ~ foreign_expert + topic_block + year,
                       data = h2_data_academic, family = binomial)
h2_au_academic  <- glm(anti_ukraine  ~ foreign_expert + topic_block + year,
                       data = h2_data_academic, family = binomial)
h2_puk_academic <- glm(any_positive_ukraine ~ foreign_expert + topic_block + year,
                       data = h2_data_academic, family = binomial)
h2_ar_academic  <- glm(anti_russia   ~ foreign_expert + topic_block + year,
                       data = h2_data_academic, family = binomial)
h2_pw_academic  <- glm(any_positive_west ~ foreign_expert + topic_block + year,
                       data = h2_data_academic, family = binomial)
h2_pr_academic  <- glm(any_positive_russia ~ foreign_expert + topic_block + year,
                       data = h2_data_academic, family = binomial)

# For H3
h3_data_academic <- h3_data %>%
  filter(role_class == "academic_expert")

h3_m3_academic <- glm(anti_west ~ foreign_expert * topic_block + year,
                      data   = h3_data_academic,
                      family = binomial)

# ── H1 table ───────────────────────────────────────────────────────────────

modelsummary(
  list(
    "Main (+ Year)"       = h1_m2,
    "Academic experts only" = h1_m2_academic
  ),
  estimate  = "{estimate} ({std.error}){stars}",
  statistic = NULL,
  coef_map  = coef_map_h1,
  gof_map   = c("nobs", "logLik"),
  stars     = c("*" = 0.05, "**" = 0.01, "***" = 0.001),
  title     = "H1 Robustness: Academic experts only",
  notes     = c(
    "Log-odds coefficients with standard errors in parentheses.",
    "Baseline: Courts and crime topic.",
    "Academic experts only column restricts to role_class == academic_expert.",
    "* p < 0.05, ** p < 0.01, *** p < 0.001"
  ),
  output    = "kableExtra"
) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width        = FALSE,
    font_size         = 12
  ) %>%
  pack_rows("Geopolitical topics",     1,  4, bold = TRUE, background = "#e8f0f7") %>%
  pack_rows("Domestic / other topics", 5, 14, bold = TRUE, background = "#f7f0e8") %>%
  pack_rows("Controls",               15, 15, bold = FALSE, background = "#f5f5f5") %>%
  column_spec(3, background = "#fafafa", italic = TRUE)

# ── H2 table ───────────────────────────────────────────────────────────────

counts_academic <- h2_data_academic %>%
  summarise(
    aw  = sum(anti_west,         na.rm = TRUE),
    au  = sum(anti_ukraine,      na.rm = TRUE),
    puk = sum(any_positive_ukraine,  na.rm = TRUE),
    ar  = sum(anti_russia,       na.rm = TRUE),
    pw  = sum(any_positive_west,     na.rm = TRUE),
    pr  = sum(any_positive_russia,   na.rm = TRUE)
  )

counts_academic_note <- paste0(
  "Outcome event counts (academic experts only): ",
  "Anti-West = ",    counts_academic$aw,  ", ",
  "Anti-Ukraine = ", counts_academic$au,  ", ",
  "Pro-Ukraine = ",  counts_academic$puk, ", ",
  "Anti-Russia = ",  counts_academic$ar,  ", ",
  "Pro-West = ",     counts_academic$pw,  ", ",
  "Pro-Russia = ",   counts_academic$pr,  "."
)

modelsummary(
  list(
    "Anti-West"    = h2_aw,
    "Anti-Ukraine" = h2_au,
    "Pro-Ukraine"  = h2_puk,
    "Anti-Russia"  = h2_ar,
    "Pro-West"     = h2_pw,
    "Pro-Russia"   = h2_pr,
    "Anti-West"    = h2_aw_academic,
    "Anti-Ukraine" = h2_au_academic,
    "Pro-Ukraine"  = h2_puk_academic,
    "Anti-Russia"  = h2_ar_academic,
    "Pro-West"     = h2_pw_academic,
    "Pro-Russia"   = h2_pr_academic
  ),
  estimate  = "{estimate} ({std.error}){stars}",
  statistic = NULL,
  coef_map  = coef_map_h2,
  gof_map   = c("nobs", "logLik"),
  stars     = c("*" = 0.05, "**" = 0.01, "***" = 0.001),
  title     = "H2 Robustness: Academic experts only",
  notes     = c(
    "Log-odds coefficients with standard errors in parentheses.",
    "Baseline: domestic expert, domestic/other topic.",
    "Academic experts only columns restrict to role_class == academic_expert.",
    counts_note,
    counts_academic_note,
    "* p < 0.05, ** p < 0.01, *** p < 0.001"
  ),
  output    = "kableExtra"
) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width        = FALSE,
    font_size         = 10
  ) %>%
  add_header_above(
    c(" "                      = 1,
      "Main models"            = 6,
      "Academic experts only"  = 6)
  ) %>%
  row_spec(1, bold = TRUE, background = "#e8f0f7") %>%
  column_spec(8:13, background = "#fafafa", italic = TRUE)

# ── H3 table ───────────────────────────────────────────────────────────────

modelsummary(
  list(
    "Main (+ Interaction)"  = h3_m3,
    "Academic experts only" = h3_m3_academic
  ),
  estimate  = "{estimate} ({std.error}){stars}",
  statistic = NULL,
  coef_map  = coef_map_h3,
  gof_map   = c("nobs", "logLik"),
  stars     = c("*" = 0.05, "**" = 0.01, "***" = 0.001),
  title     = "H3 Robustness: Academic experts only",
  notes     = c(
    "Log-odds coefficients with standard errors in parentheses.",
    "Baseline: domestic expert, domestic/other topic.",
    "Foreign expert coefficient captures the association in the",
    "domestic/other baseline. Interaction term shows how this",
    "differs in geopolitical topics.",
    "Academic experts only column restricts to role_class == academic_expert.",
    "* p < 0.05, ** p < 0.01, *** p < 0.001"
  ),
  output    = "kableExtra"
) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width        = FALSE,
    font_size         = 12
  ) %>%
  row_spec(1, bold = TRUE, background = "#e8f0f7") %>%
  row_spec(3, bold = TRUE, background = "#e8f0f7") %>%
  column_spec(3, background = "#fafafa", italic = TRUE)


h1_data_rare <- h1_data %>% filter(n_articles <= 5)

h1_m2_rare <- glm(foreign_expert ~ dominant_topic_clean + year,
                  data   = h1_data_rare,
                  family = binomial)

h1_m2_rare


```

### Robustness dropped experts treated as Russian H1

```{r}
# ── Prepare dropped experts for H1 ────────────────────────────────────────

# Topic label mapping matching dominant_topic_clean in master_dataset
topic_col_to_label <- c(
  "macro_economy"           = "Macroeconomy",
  "media_society"           = "Media and society",
  "general_news"            = "General news",
  "housing_market"          = "Housing market",
  "opinion_discourse"       = "Opinion and commentary",
  "covid_health"            = "COVID-19 and health",
  "development_education"   = "Development and education",
  "energy_sanctions"        = "Energy and sanctions",
  "military_technology"     = "Military technology",
  "information_services"    = "Information services",
  "kremlin_governance"      = "Kremlin governance",
  "courts_crime"            = "Courts and crime",
  "regions_local"           = "Regional and local issues",
  "ukraine_war"             = "Ukraine war",
  "international_geopolitics" = "International geopolitics"
)

topic_cols <- names(topic_col_to_label)

dropped_h1 <- dropped_topics_k15 %>%
  mutate(
    year = as.integer(format(DateParsed, "%Y")),
    foreign_expert = 0L,
    # Find dominant topic column
    dominant_topic_raw = topic_cols[max.col(across(all_of(topic_cols)))],
    dominant_topic_clean = recode(dominant_topic_raw, !!!topic_col_to_label)
  ) %>%
  select(row_id, year, foreign_expert, dominant_topic_clean)

# ── Combine with h1_data ───────────────────────────────────────────────────

# Keep only the columns needed from h1_data to avoid conflicts
h1_data_slim <- h1_data %>%
  select(row_id, year, foreign_expert, dominant_topic_clean)

h1_data_with_dropped <- bind_rows(
  h1_data_slim,
  dropped_h1
) %>%
  filter(dominant_topic_clean != "No clear topic") %>%
  mutate(
    dominant_topic_clean = relevel(
      factor(dominant_topic_clean),
      ref = "Courts and crime"
    )
  )

# ── Model ──────────────────────────────────────────────────────────────────

h1_m2_dropped <- glm(foreign_expert ~ dominant_topic_clean + year,
                     data   = h1_data_with_dropped,
                     family = binomial)

# ── Table ──────────────────────────────────────────────────────────────────

modelsummary(
  list(
    "Main (+ Year)"              = h1_m2,
    "Dropped experts as Russian" = h1_m2_dropped
  ),
  estimate  = "{estimate} ({std.error}){stars}",
  statistic = NULL,
  coef_map  = coef_map_h1,
  gof_map   = c("nobs", "logLik"),
  stars     = c("*" = 0.05, "**" = 0.01, "***" = 0.001),
  title     = "H1 Robustness: Dropped experts treated as Russian",
  notes     = c(
    "Log-odds coefficients with standard errors in parentheses.",
    "Baseline: Courts and crime topic.",
    "Dropped experts column adds approximately 37,000 experts excluded",
    "from the main analysis due to missing country attribution,",
    "treating them as Russian domestic experts (foreign_expert = 0).",
    "This represents the most conservative possible assumption about",
    "the unattributed expert pool.",
    "* p < 0.05, ** p < 0.01, *** p < 0.001"
  ),
  output    = "kableExtra"
) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width        = FALSE,
    font_size         = 12
  ) %>%
  pack_rows("Geopolitical topics",     1,  4, bold = TRUE, background = "#e8f0f7") %>%
  pack_rows("Domestic / other topics", 5, 14, bold = TRUE, background = "#f7f0e8") %>%
  pack_rows("Controls",               15, 15, bold = FALSE, background = "#f5f5f5") %>%
  column_spec(3, background = "#fafafa", italic = TRUE)


```

### Robustness dropped experts treated as Russian H2 and H3

```{r}

library(dplyr)
library(modelsummary)
library(kableExtra)

# ── Load dropped sentiment ─────────────────────────────────────────────────

dropped_sentiment <- read.csv(
  "C:/Users/olemga/OneDrive - PRIO/Documents/MA Thesis/Methods/Data/lenta_dropped_sentiment_full.csv"
)

library(dplyr)
library(modelsummary)
library(kableExtra)

# ── Topic label mapping ────────────────────────────────────────────────────

topic_col_to_label <- c(
  "macro_economy"             = "Macroeconomy",
  "media_society"             = "Media and society",
  "general_news"              = "General news",
  "housing_market"            = "Housing market",
  "opinion_discourse"         = "Opinion and commentary",
  "covid_health"              = "COVID-19 and health",
  "development_education"     = "Development and education",
  "energy_sanctions"          = "Energy and sanctions",
  "military_technology"       = "Military technology",
  "information_services"      = "Information services",
  "kremlin_governance"        = "Kremlin governance",
  "courts_crime"              = "Courts and crime",
  "regions_local"             = "Regional and local issues",
  "ukraine_war"               = "Ukraine war",
  "international_geopolitics" = "International geopolitics"
)

geopolitical_topics <- c(
  "Ukraine war",
  "International geopolitics",
  "Military technology",
  "Energy and sanctions"
)

topic_cols <- names(topic_col_to_label)

# ── Build topic assignment from dropped_topics_k15 ─────────────────────────

dropped_topics_slim <- dropped_topics_k15 %>%
  mutate(
    row_id               = as.numeric(row_id),
    dominant_topic_raw   = topic_cols[max.col(across(all_of(topic_cols)))],
    dominant_topic_clean = recode(dominant_topic_raw, !!!topic_col_to_label),
    topic_group          = if_else(
      dominant_topic_clean %in% geopolitical_topics,
      "geopolitics",
      "domestic"
    ),
    topic_block = factor(
      if_else(topic_group == "geopolitics", "Geopolitical", "Domestic / other"),
      levels = c("Domestic / other", "Geopolitical")
    )
  ) %>%
  select(row_id, dominant_topic_clean, topic_group, topic_block)

# ── Join topics onto dropped sentiment ────────────────────────────────────

dropped_for_h2 <- dropped_sentiment %>%
  mutate(row_id = as.numeric(row_id)) %>%
  left_join(dropped_topics_slim, by = "row_id") %>%
  mutate(
    foreign_expert = 0L,
    year           = as.integer(format(as.Date(DateParsed), "%Y"))
  ) %>%
  filter(
    !is.na(year),
    !is.na(topic_block)
  ) %>%
  select(
    row_id, year, foreign_expert, topic_block,
    any_anti_west, any_anti_ukraine, any_positive_ukraine,
    any_anti_russia, any_positive_west, any_positive_russia
  )

# ── Slim h2_data to matching columns ──────────────────────────────────────

h2_data_slim <- h2_data %>%
  rename(
    any_anti_west    = anti_west,
    any_anti_russia  = anti_russia
  ) %>%
  select(
    row_id, year, foreign_expert, topic_block,
    any_anti_west, anti_ukraine, any_positive_ukraine,
    any_anti_russia, any_positive_west, any_positive_russia
  )

# ── Diagnostics ────────────────────────────────────────────────────────────

cat("Row ID overlap check (should be 0):\n")
print(sum(dropped_for_h2$row_id %in% h2_data_slim$row_id))

cat("\ndropped_for_h2 rows:\n")
print(nrow(dropped_for_h2))

cat("\nTopic block distribution in dropped:\n")
print(table(dropped_for_h2$topic_block))

# ── Combine ────────────────────────────────────────────────────────────────

h2_data_with_dropped <- bind_rows(h2_data_slim, dropped_for_h2)

cat("\nCombined dataset rows:\n")
print(nrow(h2_data_with_dropped))

cat("\nForeign expert distribution:\n")
print(table(h2_data_with_dropped$foreign_expert))

# ── H2 models ──────────────────────────────────────────────────────────────

h2_aw_dropped  <- glm(any_anti_west        ~ foreign_expert + topic_block + year,
                      data = h2_data_with_dropped, family = binomial)
h2_au_dropped  <- glm(anti_ukraine     ~ foreign_expert + topic_block + year,
                      data = h2_data_with_dropped, family = binomial)
h2_puk_dropped <- glm(any_positive_ukraine ~ foreign_expert + topic_block + year,
                      data = h2_data_with_dropped, family = binomial)
h2_ar_dropped  <- glm(any_anti_russia      ~ foreign_expert + topic_block + year,
                      data = h2_data_with_dropped, family = binomial)
h2_pw_dropped  <- glm(any_positive_west    ~ foreign_expert + topic_block + year,
                      data = h2_data_with_dropped, family = binomial)
h2_pr_dropped  <- glm(any_positive_russia  ~ foreign_expert + topic_block + year,
                      data = h2_data_with_dropped, family = binomial)

# ── H3 model ───────────────────────────────────────────────────────────────

h3_m3_dropped <- glm(any_anti_west ~ foreign_expert * topic_block + year,
                     data   = h2_data_with_dropped,
                     family = binomial)

# ── Outcome counts ─────────────────────────────────────────────────────────

counts_dropped_h2 <- h2_data_with_dropped %>%
  summarise(
    aw  = sum(any_anti_west,          na.rm = TRUE),
    au  = sum(any_anti_ukraine,       na.rm = TRUE),
    puk = sum(any_positive_ukraine,   na.rm = TRUE),
    ar  = sum(any_anti_russia,        na.rm = TRUE),
    pw  = sum(any_positive_west,      na.rm = TRUE),
    pr  = sum(any_positive_russia,    na.rm = TRUE)
  )

counts_dropped_note <- paste0(
  "Outcome event counts (with dropped experts as Russian): ",
  "Anti-West = ",    counts_dropped_h2$aw,  ", ",
  "Anti-Ukraine = ", counts_dropped_h2$au,  ", ",
  "Pro-Ukraine = ",  counts_dropped_h2$puk, ", ",
  "Anti-Russia = ",  counts_dropped_h2$ar,  ", ",
  "Pro-West = ",     counts_dropped_h2$pw,  ", ",
  "Pro-Russia = ",   counts_dropped_h2$pr,  "."
)

# ── Coefficient maps ───────────────────────────────────────────────────────

coef_map_h2 <- c(
  "foreign_expert"          = "Foreign expert",
  "topic_blockGeopolitical" = "Topic: Geopolitical",
  "year"                    = "Year"
)

coef_map_h3 <- c(
  "foreign_expert"                         = "Foreign expert",
  "topic_blockGeopolitical"                = "Topic: Geopolitical",
  "foreign_expert:topic_blockGeopolitical" = "Foreign expert x Geopolitical",
  "year"                                   = "Year"
)

# ── H2 table ───────────────────────────────────────────────────────────────

modelsummary(
  list(
    "Anti-West"    = h2_aw,
    "Anti-Ukraine" = h2_au,
    "Pro-Ukraine"  = h2_puk,
    "Anti-Russia"  = h2_ar,
    "Pro-West"     = h2_pw,
    "Pro-Russia"   = h2_pr,
    "Anti-West"    = h2_aw_dropped,
    "Anti-Ukraine" = h2_au_dropped,
    "Pro-Ukraine"  = h2_puk_dropped,
    "Anti-Russia"  = h2_ar_dropped,
    "Pro-West"     = h2_pw_dropped,
    "Pro-Russia"   = h2_pr_dropped
  ),
  estimate  = "{estimate} ({std.error}){stars}",
  statistic = NULL,
  coef_map  = coef_map_h2,
  gof_map   = c("nobs", "logLik"),
  stars     = c("*" = 0.05, "**" = 0.01, "***" = 0.001),
  title     = "H2 Robustness: Dropped experts treated as Russian",
  notes     = c(
    "Log-odds coefficients with standard errors in parentheses.",
    "Baseline: domestic expert, domestic/other topic.",
    "Dropped experts column adds experts excluded from the main",
    "analysis due to missing country attribution, treating them",
    "as Russian domestic experts. This is the most conservative",
    "possible assumption about the unattributed expert pool.",
    counts_note,
    counts_dropped_note,
    "* p < 0.05, ** p < 0.01, *** p < 0.001"
  ),
  output    = "kableExtra"
) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width        = FALSE,
    font_size         = 10
  ) %>%
  add_header_above(
    c(" "                          = 1,
      "Main models"                = 6,
      "Dropped experts as Russian" = 6)
  ) %>%
  row_spec(1, bold = TRUE, background = "#e8f0f7") %>%
  column_spec(8:13, background = "#fafafa", italic = TRUE)

# ── H3 table ───────────────────────────────────────────────────────────────

modelsummary(
  list(
    "Main (+ Interaction)"       = h3_m3,
    "Dropped experts as Russian" = h3_m3_dropped
  ),
  estimate  = "{estimate} ({std.error}){stars}",
  statistic = NULL,
  coef_map  = coef_map_h3,
  gof_map   = c("nobs", "logLik"),
  stars     = c("*" = 0.05, "**" = 0.01, "***" = 0.001),
  title     = "H3 Robustness: Dropped experts treated as Russian",
  notes     = c(
    "Log-odds coefficients with standard errors in parentheses.",
    "Baseline: domestic expert, domestic/other topic.",
    "Foreign expert coefficient captures the association in the",
    "domestic/other baseline. Interaction term shows how this",
    "differs in geopolitical topics.",
    "Dropped experts treated as Russian domestic experts.",
    "* p < 0.05, ** p < 0.01, *** p < 0.001"
  ),
  output    = "kableExtra"
) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width        = FALSE,
    font_size         = 12
  ) %>%
  row_spec(1, bold = TRUE, background = "#e8f0f7") %>%
  row_spec(3, bold = TRUE, background = "#e8f0f7") %>%
  column_spec(3, background = "#fafafa", italic = TRUE)
```

### Robustness: alternative explanations H1 H3

```{r}
# ── H1: Alternative specifications ────────────────────────────────────────

# Probit
h1_probit <- glm(foreign_expert ~ dominant_topic_clean + year,
                 data   = h1_data,
                 family = binomial(link = "probit"))

# Linear probability model
h1_lpm <- lm(foreign_expert ~ dominant_topic_clean + year,
             data = h1_data)

# ── H1 table ───────────────────────────────────────────────────────────────

modelsummary(
  list(
    "Logit (main)"  = h1_m2,
    "Probit"        = h1_probit,
    "LPM"           = h1_lpm
  ),
  estimate  = "{estimate} ({std.error}){stars}",
  statistic = NULL,
  coef_map  = coef_map_h1,
  gof_map   = c("nobs", "logLik", "r.squared"),
  stars     = c("*" = 0.05, "**" = 0.01, "***" = 0.001),
  title     = "H1 Robustness: Alternative model specifications",
  notes     = c(
    "Logit and probit coefficients are log-odds and probit coefficients",
    "respectively. LPM coefficients are percentage point differences.",
    "Standard errors in parentheses.",
    "Baseline: Courts and crime topic.",
    "* p < 0.05, ** p < 0.01, *** p < 0.001"
  ),
  output    = "kableExtra"
) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width        = FALSE,
    font_size         = 12
  ) %>%
  pack_rows("Geopolitical topics",     1,  4, bold = TRUE, background = "#e8f0f7") %>%
  pack_rows("Domestic / other topics", 5, 14, bold = TRUE, background = "#f7f0e8") %>%
  pack_rows("Controls",               15, 15, bold = FALSE, background = "#f5f5f5") %>%
  add_header_above(
    c(" "                             = 1,
      "Main"                          = 1,
      "Alternative specifications"    = 2)
  ) %>%
  column_spec(3:4, background = "#fafafa", italic = TRUE)

# ── H2: Alternative specifications ────────────────────────────────────────

# Probit models
h2_aw_probit  <- glm(anti_west          ~ foreign_expert + topic_block + year,
                     data = h2_data, family = binomial(link = "probit"))
h2_au_probit  <- glm(anti_ukraine       ~ foreign_expert + topic_block + year,
                     data = h2_data, family = binomial(link = "probit"))
h2_puk_probit <- glm(any_positive_ukraine   ~ foreign_expert + topic_block + year,
                     data = h2_data, family = binomial(link = "probit"))
h2_ar_probit  <- glm(anti_russia        ~ foreign_expert + topic_block + year,
                     data = h2_data, family = binomial(link = "probit"))
h2_pw_probit  <- glm(any_positive_west      ~ foreign_expert + topic_block + year,
                     data = h2_data, family = binomial(link = "probit"))
h2_pr_probit  <- glm(any_positive_russia    ~ foreign_expert + topic_block + year,
                     data = h2_data, family = binomial(link = "probit"))

# LPM models
h2_aw_lpm  <- lm(anti_west          ~ foreign_expert + topic_block + year,
                 data = h2_data)
h2_au_lpm  <- lm(anti_ukraine       ~ foreign_expert + topic_block + year,
                 data = h2_data)
h2_puk_lpm <- lm(any_positive_ukraine   ~ foreign_expert + topic_block + year,
                 data = h2_data)
h2_ar_lpm  <- lm(anti_russia        ~ foreign_expert + topic_block + year,
                 data = h2_data)
h2_pw_lpm  <- lm(any_positive_west      ~ foreign_expert + topic_block + year,
                 data = h2_data)
h2_pr_lpm  <- lm(any_positive_russia    ~ foreign_expert + topic_block + year,
                 data = h2_data)

# ── H2 table ───────────────────────────────────────────────────────────────

modelsummary(
  list(
    "Anti-West"    = h2_aw,
    "Anti-Ukraine" = h2_au,
    "Pro-Ukraine"  = h2_puk,
    "Anti-Russia"  = h2_ar,
    "Pro-West"     = h2_pw,
    "Pro-Russia"   = h2_pr,
    "Anti-West"    = h2_aw_probit,
    "Anti-Ukraine" = h2_au_probit,
    "Pro-Ukraine"  = h2_puk_probit,
    "Anti-Russia"  = h2_ar_probit,
    "Pro-West"     = h2_pw_probit,
    "Pro-Russia"   = h2_pr_probit,
    "Anti-West"    = h2_aw_lpm,
    "Anti-Ukraine" = h2_au_lpm,
    "Pro-Ukraine"  = h2_puk_lpm,
    "Anti-Russia"  = h2_ar_lpm,
    "Pro-West"     = h2_pw_lpm,
    "Pro-Russia"   = h2_pr_lpm
  ),
  estimate  = "{estimate} ({std.error}){stars}",
  statistic = NULL,
  coef_map  = coef_map_h2,
  gof_map   = c("nobs", "logLik"),
  stars     = c("*" = 0.05, "**" = 0.01, "***" = 0.001),
  title     = "H2 Robustness: Alternative model specifications",
  notes     = c(
    "Logit and probit report log-odds and probit coefficients respectively.",
    "LPM reports percentage point differences.",
    "Standard errors in parentheses.",
    "Baseline: domestic expert, domestic/other topic.",
    counts_note,
    "* p < 0.05, ** p < 0.01, *** p < 0.001"
  ),
  output    = "kableExtra"
) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width        = FALSE,
    font_size         = 9
  ) %>%
  add_header_above(
    c(" "                          = 1,
      "Logit (main)"               = 6,
      "Probit"                     = 6,
      "LPM"                        = 6)
  ) %>%
  row_spec(1, bold = TRUE, background = "#e8f0f7") %>%
  column_spec(8:13,  background = "#fafafa", italic = TRUE) %>%
  column_spec(14:19, background = "#f0f0f0", italic = TRUE)

# ── H3: Alternative specifications ────────────────────────────────────────

# Probit
h3_probit <- glm(anti_west ~ foreign_expert * topic_block + year,
                 data   = h3_data,
                 family = binomial(link = "probit"))

# LPM
h3_lpm <- lm(anti_west ~ foreign_expert * topic_block + year,
             data = h3_data)

# ── H3 table ───────────────────────────────────────────────────────────────

modelsummary(
  list(
    "Logit (main)" = h3_m3,
    "Probit"       = h3_probit,
    "LPM"          = h3_lpm
  ),
  estimate  = "{estimate} ({std.error}){stars}",
  statistic = NULL,
  coef_map  = coef_map_h3,
  gof_map   = c("nobs", "logLik", "r.squared"),
  stars     = c("*" = 0.05, "**" = 0.01, "***" = 0.001),
  title     = "H3 Robustness: Alternative model specifications",
  notes     = c(
    "Logit and probit report log-odds and probit coefficients respectively.",
    "LPM reports percentage point differences.",
    "Standard errors in parentheses.",
    "Baseline: domestic expert, domestic/other topic.",
    "Foreign expert coefficient captures the association in the",
    "domestic/other baseline. Interaction term shows how this",
    "differs in geopolitical topics.",
    "* p < 0.05, ** p < 0.01, *** p < 0.001"
  ),
  output    = "kableExtra"
) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width        = FALSE,
    font_size         = 12
  ) %>%
  add_header_above(
    c(" "                          = 1,
      "Main"                       = 1,
      "Alternative specifications" = 2)
  ) %>%
  row_spec(1, bold = TRUE, background = "#e8f0f7") %>%
  row_spec(3, bold = TRUE, background = "#e8f0f7") %>%
  column_spec(3:4, background = "#fafafa", italic = TRUE)
```

### Robustness: exclude government official h1 h3

```{r}
# ── Exclude government officials ───────────────────────────────────────────

h1_data_no_gov <- h1_data %>%
  filter(role_class != "government_official")

h2_data_no_gov <- h2_data %>%
  filter(role_class != "government_official")

h3_data_no_gov <- h3_data %>%
  filter(role_class != "government_official")

# ── H1 model ───────────────────────────────────────────────────────────────

h1_m2_no_gov <- glm(foreign_expert ~ dominant_topic_clean + year,
                    data   = h1_data_no_gov,
                    family = binomial)

# ── H2 models ──────────────────────────────────────────────────────────────

h2_aw_no_gov  <- glm(anti_west          ~ foreign_expert + topic_block + year,
                     data = h2_data_no_gov, family = binomial)
h2_au_no_gov  <- glm(anti_ukraine       ~ foreign_expert + topic_block + year,
                     data = h2_data_no_gov, family = binomial)
h2_puk_no_gov <- glm(any_positive_ukraine   ~ foreign_expert + topic_block + year,
                     data = h2_data_no_gov, family = binomial)
h2_ar_no_gov  <- glm(anti_russia        ~ foreign_expert + topic_block + year,
                     data = h2_data_no_gov, family = binomial)
h2_pw_no_gov  <- glm(any_positive_west      ~ foreign_expert + topic_block + year,
                     data = h2_data_no_gov, family = binomial)
h2_pr_no_gov  <- glm(any_positive_russia    ~ foreign_expert + topic_block + year,
                     data = h2_data_no_gov, family = binomial)

# ── H3 model ───────────────────────────────────────────────────────────────

h3_m3_no_gov <- glm(anti_west ~ foreign_expert * topic_block + year,
                    data   = h3_data_no_gov,
                    family = binomial)

# ── Sample size check ──────────────────────────────────────────────────────

cat("H1 sample sizes:\n")
cat("Main:", nrow(h1_data), "\n")
cat("No government officials:", nrow(h1_data_no_gov), "\n")
cat("Removed:", nrow(h1_data) - nrow(h1_data_no_gov), "\n")

cat("\nH2 sample sizes:\n")
cat("Main:", nrow(h2_data), "\n")
cat("No government officials:", nrow(h2_data_no_gov), "\n")

# ── Outcome counts ─────────────────────────────────────────────────────────

counts_no_gov <- h2_data_no_gov %>%
  summarise(
    aw  = sum(anti_west,          na.rm = TRUE),
    au  = sum(anti_ukraine,       na.rm = TRUE),
    puk = sum(any_positive_ukraine,   na.rm = TRUE),
    ar  = sum(anti_russia,        na.rm = TRUE),
    pw  = sum(any_positive_west,      na.rm = TRUE),
    pr  = sum(any_positive_russia,    na.rm = TRUE)
  )

counts_no_gov_note <- paste0(
  "Outcome event counts (excluding government officials): ",
  "Anti-West = ",    counts_no_gov$aw,  ", ",
  "Anti-Ukraine = ", counts_no_gov$au,  ", ",
  "Pro-Ukraine = ",  counts_no_gov$puk, ", ",
  "Anti-Russia = ",  counts_no_gov$ar,  ", ",
  "Pro-West = ",     counts_no_gov$pw,  ", ",
  "Pro-Russia = ",   counts_no_gov$pr,  "."
)

# ── H1 table ───────────────────────────────────────────────────────────────

modelsummary(
  list(
    "Main (+ Year)"                  = h1_m2,
    "Excluding government officials" = h1_m2_no_gov
  ),
  estimate  = "{estimate} ({std.error}){stars}",
  statistic = NULL,
  coef_map  = coef_map_h1,
  gof_map   = c("nobs", "logLik"),
  stars     = c("*" = 0.05, "**" = 0.01, "***" = 0.001),
  title     = "H1 Robustness: Excluding government officials",
  notes     = c(
    "Log-odds coefficients with standard errors in parentheses.",
    "Baseline: Courts and crime topic.",
    "Excluding government officials removes role_class == government_official.",
    "Government officials are not expert voices in the journalistic sense",
    "and their inclusion may conflate editorial selection of expert credibility",
    "with routine citation of official sources.",
    "* p < 0.05, ** p < 0.01, *** p < 0.001"
  ),
  output    = "kableExtra"
) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width        = FALSE,
    font_size         = 12
  ) %>%
  pack_rows("Geopolitical topics",     1,  4, bold = TRUE, background = "#e8f0f7") %>%
  pack_rows("Domestic / other topics", 5, 14, bold = TRUE, background = "#f7f0e8") %>%
  pack_rows("Controls",               15, 15, bold = FALSE, background = "#f5f5f5") %>%
  column_spec(3, background = "#fafafa", italic = TRUE)

# ── H2 table ───────────────────────────────────────────────────────────────

modelsummary(
  list(
    "Anti-West"    = h2_aw,
    "Anti-Ukraine" = h2_au,
    "Pro-Ukraine"  = h2_puk,
    "Anti-Russia"  = h2_ar,
    "Pro-West"     = h2_pw,
    "Pro-Russia"   = h2_pr,
    "Anti-West"    = h2_aw_no_gov,
    "Anti-Ukraine" = h2_au_no_gov,
    "Pro-Ukraine"  = h2_puk_no_gov,
    "Anti-Russia"  = h2_ar_no_gov,
    "Pro-West"     = h2_pw_no_gov,
    "Pro-Russia"   = h2_pr_no_gov
  ),
  estimate  = "{estimate} ({std.error}){stars}",
  statistic = NULL,
  coef_map  = coef_map_h2,
  gof_map   = c("nobs", "logLik"),
  stars     = c("*" = 0.05, "**" = 0.01, "***" = 0.001),
  title     = "H2 Robustness: Excluding government officials",
  notes     = c(
    "Log-odds coefficients with standard errors in parentheses.",
    "Baseline: domestic expert, domestic/other topic.",
    "Excluding government officials removes role_class == government_official.",
    counts_note,
    counts_no_gov_note,
    "* p < 0.05, ** p < 0.01, *** p < 0.001"
  ),
  output    = "kableExtra"
) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width        = FALSE,
    font_size         = 10
  ) %>%
  add_header_above(
    c(" "                              = 1,
      "Main models"                    = 6,
      "Excluding government officials" = 6)
  ) %>%
  row_spec(1, bold = TRUE, background = "#e8f0f7") %>%
  column_spec(8:13, background = "#fafafa", italic = TRUE)

# ── H3 table ───────────────────────────────────────────────────────────────

modelsummary(
  list(
    "Main (+ Interaction)"           = h3_m3,
    "Excluding government officials" = h3_m3_no_gov
  ),
  estimate  = "{estimate} ({std.error}){stars}",
  statistic = NULL,
  coef_map  = coef_map_h3,
  gof_map   = c("nobs", "logLik"),
  stars     = c("*" = 0.05, "**" = 0.01, "***" = 0.001),
  title     = "H3 Robustness: Excluding government officials",
  notes     = c(
    "Log-odds coefficients with standard errors in parentheses.",
    "Baseline: domestic expert, domestic/other topic.",
    "Foreign expert coefficient captures the association in the",
    "domestic/other baseline. Interaction term shows how this",
    "differs in geopolitical topics.",
    "Excluding government officials removes role_class == government_official.",
    "* p < 0.05, ** p < 0.01, *** p < 0.001"
  ),
  output    = "kableExtra"
) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width        = FALSE,
    font_size         = 12
  ) %>%
  row_spec(1, bold = TRUE, background = "#e8f0f7") %>%
  row_spec(3, bold = TRUE, background = "#e8f0f7") %>%
  column_spec(3, background = "#fafafa", italic = TRUE)
```

### Robustness h4

```{r}

# Restrict to post-2014 for main H4 models
h4_data <- h2_data %>% filter(year >= 2014)

# Alternative cutoff: 2013
h4_data_2013 <- h2_data %>% filter(year >= 2013)

# Alternative cutoff: 2015  
h4_data_2015 <- h2_data %>% filter(year >= 2015)

# Exclude post-2022
h4_data_no2022 <- h2_data %>% filter(year >= 2014 & year < 2022)

# Pre-2014 placebo
h4_data_pre2014 <- h2_data %>% filter(year < 2014)

# Models: anti-West outcome only since that is the H4 focus
h4_main    <- glm(anti_west ~ foreign_expert + topic_block + year,
                  data = h4_data, family = binomial)
h4_2013    <- glm(anti_west ~ foreign_expert + topic_block + year,
                  data = h4_data_2013, family = binomial)
h4_2015    <- glm(anti_west ~ foreign_expert + topic_block + year,
                  data = h4_data_2015, family = binomial)
h4_no2022  <- glm(anti_west ~ foreign_expert + topic_block + year,
                  data = h4_data_no2022, family = binomial)
h4_placebo <- glm(anti_west ~ foreign_expert + topic_block + year,
                  data = h4_data_pre2014, family = binomial)


summary(h4_main)
summary(h4_2013)
summary(h4_2015)
summary(h4_no2022)
summary(h4_placebo)

# Check variable name consistency
h4_data_pre2014 <- h2_data %>% filter(year < 2014)

# Interaction model on full dataset
h4_interaction <- glm(anti_west ~ foreign_expert * post_2014 + 
                        topic_block + year,
                      data = h2_data %>% 
                        mutate(post_2014 = as.integer(year >= 2014)),
                      family = binomial)

summary(h4_interaction)

# ── Split by topic block and period ───────────────────────────────────────

# Geopolitical topics only
h4_geo_pre2014  <- h2_data %>% 
  filter(year < 2014, topic_block == "Geopolitical")

h4_geo_post2014 <- h2_data %>% 
  filter(year >= 2014, topic_block == "Geopolitical")

# Domestic topics only
h4_dom_pre2014  <- h2_data %>% 
  filter(year < 2014, topic_block == "Domestic / other")

h4_dom_post2014 <- h2_data %>% 
  filter(year >= 2014, topic_block == "Domestic / other")

# Models
h4_geo_pre  <- glm(anti_west ~ foreign_expert + year,
                   data = h4_geo_pre2014,  family = binomial)
h4_geo_post <- glm(anti_west ~ foreign_expert + year,
                   data = h4_geo_post2014, family = binomial)
h4_dom_pre  <- glm(anti_west ~ foreign_expert + year,
                   data = h4_dom_pre2014,  family = binomial)
h4_dom_post <- glm(anti_west ~ foreign_expert + year,
                   data = h4_dom_post2014, family = binomial)

summary(h4_geo_pre)
summary(h4_geo_post)
summary(h4_dom_pre)
summary(h4_dom_post)

coef_map_h4 <- c(
  "foreign_expert"          = "Foreign expert",
  "topic_blockGeopolitical" = "Topic: Geopolitical",
  "year"                    = "Year"
)

modelsummary(
  list(
    "Geopolitical pre-2014"  = h4_geo_pre,
    "Geopolitical post-2014" = h4_geo_post,
    "Domestic pre-2014"      = h4_dom_pre,
    "Domestic post-2014"     = h4_dom_post
  ),
  estimate  = "{estimate} ({std.error}){stars}",
  statistic = NULL,
  coef_map  = coef_map_h4,
  gof_map   = c("nobs", "logLik"),
  stars     = c("*" = 0.05, "**" = 0.01, "***" = 0.001),
  title     = "H4 Robustness: Foreign expert anti-West coefficient by topic block and period",
  notes     = c(
    "Log-odds coefficients with standard errors in parentheses.",
    "Outcome: anti-West sentiment. Baseline: domestic expert.",
    "Topic block fixed within each model — geopolitical models",
    "include only geopolitical articles, domestic models include",
    "only domestic and other articles.",
    "Pre-2014 period uses editorially independent Lenta.ru as baseline.",
    "* p < 0.05, ** p < 0.01, *** p < 0.001"
  ),
  output    = "kableExtra"
) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width        = FALSE,
    font_size         = 12
  ) %>%
  add_header_above(
    c(" "              = 1,
      "Geopolitical"   = 2,
      "Domestic"       = 2)
  ) %>%
  column_spec(2:3, background = "#e8f0f7") %>%
  column_spec(4:5, background = "#f7f0e8")

# ── Periodization checks on full dataset ──────────────────────────────────

h4_main    <- glm(anti_west ~ foreign_expert + topic_block + year,
                  data   = h2_data %>% filter(year >= 2014),
                  family = binomial)

h4_2013    <- glm(anti_west ~ foreign_expert + topic_block + year,
                  data   = h2_data %>% filter(year >= 2013),
                  family = binomial)

h4_2015    <- glm(anti_west ~ foreign_expert + topic_block + year,
                  data   = h2_data %>% filter(year >= 2015),
                  family = binomial)

h4_no2022  <- glm(anti_west ~ foreign_expert + topic_block + year,
                  data   = h2_data %>% filter(year >= 2014 & year < 2022),
                  family = binomial)

h4_placebo <- glm(anti_west ~ foreign_expert + topic_block + year,
                  data   = h2_data %>% filter(year < 2014),
                  family = binomial)

modelsummary(
  list(
    "Main (2014--2024)"  = h4_main,
    "Alt. cutoff 2013"   = h4_2013,
    "Alt. cutoff 2015"   = h4_2015,
    "Excl. 2022--2024"   = h4_no2022,
    "Pre-2014 placebo"   = h4_placebo
  ),
  estimate  = "{estimate} ({std.error}){stars}",
  statistic = NULL,
  coef_map  = coef_map_h4,
  gof_map   = c("nobs", "logLik"),
  stars     = c("*" = 0.05, "**" = 0.01, "***" = 0.001),
  title     = "H4 Robustness: Periodization checks",
  notes     = c(
    "Log-odds coefficients with standard errors in parentheses.",
    "Outcome: anti-West sentiment. Baseline: domestic expert,",
    "domestic/other topic.",
    "Main model restricted to 2014 onward. Alternative cutoff",
    "models use 2013 and 2015 as alternative start dates.",
    "Excl. 2022-2024 removes the acute war period.",
    "Pre-2014 placebo uses the editorially independent period.",
    "* p < 0.05, ** p < 0.01, *** p < 0.001"
  ),
  output    = "kableExtra"
) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width        = FALSE,
    font_size         = 12
  ) %>%
  add_header_above(
    c(" "                    = 1,
      "Periodization checks" = 3,
      "Exclusion"            = 1,
      "Placebo"              = 1)
  ) %>%
  column_spec(5, background = "#fafafa", italic = TRUE) %>%
  column_spec(6, background = "#f0f0f0", italic = TRUE)
```

```{r}
library(dplyr)
library(ggplot2)
library(lubridate)
library(scales)
library(tidyr)

# ── Step 1: Total articles per month from full corpus ──────────────────────

articles_per_month <- lenta_news_1999_2024 %>%
  mutate(
    date  = as.Date(date),
    month = floor_date(date, "month")
  ) %>%
  filter(!is.na(month)) %>%
  count(month, name = "n_articles_total")

# ── Step 2: Articles with foreign and domestic experts per month ──────────
# Count distinct articles (row_id) per month for each expert type

articles_with_experts <- master_dataset %>%
  mutate(
    date  = as.Date(date),
    month = floor_date(date, "month")
  ) %>%
  filter(!is.na(month)) %>%
  group_by(month) %>%
  summarise(
    n_articles_foreign  = n_distinct(row_id[foreign_expert == 1]),
    n_articles_domestic = n_distinct(row_id[foreign_expert == 0]),
    .groups = "drop"
  )

# ── Step 3: Combine and compute shares ────────────────────────────────────

monthly_shares <- articles_per_month %>%
  left_join(articles_with_experts, by = "month") %>%
  mutate(
    n_articles_foreign  = ifelse(is.na(n_articles_foreign),  0, n_articles_foreign),
    n_articles_domestic = ifelse(is.na(n_articles_domestic), 0, n_articles_domestic),
    share_foreign       = n_articles_foreign  / n_articles_total,
    share_domestic      = n_articles_domestic / n_articles_total
  ) %>%
  filter(month >= as.Date("1999-09-01") & month <= as.Date("2024-06-30"))

# ── Step 4: Pivot for plotting ────────────────────────────────────────────

plot_data <- monthly_shares %>%
  select(month, share_foreign, share_domestic) %>%
  pivot_longer(
    cols      = c(share_foreign, share_domestic),
    names_to  = "expert_type",
    values_to = "share"
  ) %>%
  mutate(
    Expert = factor(expert_type,
                    levels = c("share_domestic", "share_foreign"),
                    labels = c("Domestic", "Foreign"))
  )

# ── Step 5: Plot in Figure 6.4 style ──────────────────────────────────────

ggplot(plot_data, aes(x = month, y = share, color = Expert)) +
  
  # Raw monthly line (light)
  geom_line(linewidth = 0.4, alpha = 0.4) +
  
  # Smoothed trend
  geom_smooth(
    method    = "loess",
    span      = 0.15,
    se        = FALSE,
    linewidth = 1.2
  ) +
  
  # 2014 editorial change
  geom_vline(
    xintercept = as.Date("2014-03-01"),
    linetype   = "dashed",
    color      = "grey50",
    linewidth  = 0.5
  ) +
  annotate(
    "text",
    x        = as.Date("2014-03-01"),
    y        = Inf,
    label    = "Editorial change",
    angle    = 90,
    vjust    = -0.4,
    hjust    = 1.1,
    size     = 3,
    color    = "grey40",
    fontface = "italic"
  ) +
  
  # 2020 COVID-19
  geom_vline(
    xintercept = as.Date("2020-03-01"),
    linetype   = "dashed",
    color      = "grey50",
    linewidth  = 0.5
  ) +
  annotate(
    "text",
    x        = as.Date("2020-03-01"),
    y        = Inf,
    label    = "COVID-19",
    angle    = 90,
    vjust    = -0.4,
    hjust    = 1.1,
    size     = 3,
    color    = "grey40",
    fontface = "italic"
  ) +
  
  # 2022 invasion
  geom_vline(
    xintercept = as.Date("2022-02-24"),
    linetype   = "dashed",
    color      = "grey50",
    linewidth  = 0.5
  ) +
  annotate(
    "text",
    x        = as.Date("2022-02-24"),
    y        = Inf,
    label    = "Ukraine invasion",
    angle    = 90,
    vjust    = -0.4,
    hjust    = 1.1,
    size     = 3,
    color    = "grey40",
    fontface = "italic"
  ) +
  
  scale_color_manual(
    values = c("Domestic" = "#b04a4a", "Foreign" = "#2b6cb0"),
    name   = NULL
  ) +
  
  scale_x_date(
    date_breaks = "3 years",
    date_labels = "%Y"
  ) +
  
  scale_y_continuous(labels = percent_format(accuracy = 1)) +
  
  labs(
    x        = NULL,
    y        = "Share of articles with expert mention",
    title    = "Expert use as share of total articles published",
    subtitle = "Monthly shares with smoothed trends. Dashed lines mark key editorial and geopolitical events."
  ) +
  
  theme_minimal(base_size = 13) +
  theme(
    plot.title       = element_text(face = "bold"),
    plot.subtitle    = element_text(size = 10, color = "grey30"),
    panel.grid.minor = element_blank(),
    legend.position  = "bottom"
  )
```

### new H3

```{r}
library(broom)  # for tidy() in the diagnostic dump at the end

# ── Additional data prep ──────────────────────────────────────────────────

# Stratified subsets
h3_domestic              <- h3_data            %>% filter(topic_block == "Domestic / other")
h3_geopolitical          <- h3_data            %>% filter(topic_block == "Geopolitical")
h3_domestic_restricted   <- h3_data_restricted %>% filter(topic_block == "Domestic / other")
h3_geopolitical_restricted <- h3_data_restricted %>% filter(topic_block == "Geopolitical")

# Reparameterized data: geopolitical as reference category
h3_data_georef            <- h3_data %>%
  mutate(topic_block = factor(topic_block,
                              levels = c("Geopolitical", "Domestic / other")))
h3_data_georef_restricted <- h3_data_restricted %>%
  mutate(topic_block = factor(topic_block,
                              levels = c("Geopolitical", "Domestic / other")))


# ── Stratified models (headline H3 table) ─────────────────────────────────

h3_dom_m1 <- glm(anti_west ~ foreign_expert,        data = h3_domestic,            family = binomial)
h3_dom_m2 <- glm(anti_west ~ foreign_expert + year, data = h3_domestic,            family = binomial)
h3_dom_m3 <- glm(anti_west ~ foreign_expert + year, data = h3_domestic_restricted, family = binomial)

h3_geo_m1 <- glm(anti_west ~ foreign_expert,        data = h3_geopolitical,            family = binomial)
h3_geo_m2 <- glm(anti_west ~ foreign_expert + year, data = h3_geopolitical,            family = binomial)
h3_geo_m3 <- glm(anti_west ~ foreign_expert + year, data = h3_geopolitical_restricted, family = binomial)

coef_map_strat <- c(
  "foreign_expert" = "Foreign expert",
  "year"           = "Year"
)

modelsummary(
  list(
    "(1)" = h3_dom_m1, "(2)" = h3_dom_m2, "(3)" = h3_dom_m3,
    "(4)" = h3_geo_m1, "(5)" = h3_geo_m2, "(6)" = h3_geo_m3
  ),
  estimate  = "{estimate} ({std.error}){stars}",
  statistic = NULL,
  coef_map  = coef_map_strat,
  gof_map   = c("nobs", "logLik"),
  stars     = c("*" = 0.05, "**" = 0.01, "***" = 0.001),
  title     = "H3: Foreign expert anti-West framing, stratified by topic block",
  notes = c(
    "Log-odds coefficients with standard errors in parentheses.",
    "Each column is a separate logistic regression on the indicated subset.",
    "Columns (1)-(3): articles in domestic / other topics (economic, health, legal, regional, etc.).",
    "Columns (4)-(6): articles in geopolitical topics (international geopolitics, Ukraine war, security).",
    "Columns (3) and (6) restricted to expert_country_maxconf >= 0.85.",
    "* p < 0.05, ** p < 0.01, *** p < 0.001"
  ),
  output = "kableExtra"
) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width = FALSE,
    font_size = 12
  ) %>%
  add_header_above(
    c(" " = 1, "Domestic / other topics" = 3, "Geopolitical topics" = 3)
  ) %>%
  row_spec(1, bold = TRUE, background = "#e8f0f7")  # foreign_expert row


# ── Reparameterized interaction model (geopolitical as baseline) ──────────

h3_re_m3 <- glm(anti_west ~ foreign_expert * topic_block + year,
                data = h3_data_georef,            family = binomial)
h3_re_m4 <- glm(anti_west ~ foreign_expert * topic_block + year,
                data = h3_data_georef_restricted, family = binomial)

coef_map_re <- c(
  "foreign_expert"                              = "Foreign expert",
  "topic_blockDomestic / other"                 = "Topic: Domestic / other",
  "foreign_expert:topic_blockDomestic / other"  = "Foreign expert x Domestic",
  "year"                                        = "Year"
)

modelsummary(
  list(
    "+ Interaction"           = h3_re_m3,
    "Restricted (conf >=0.85)" = h3_re_m4
  ),
  estimate  = "{estimate} ({std.error}){stars}",
  statistic = NULL,
  coef_map  = coef_map_re,
  gof_map   = c("nobs", "logLik"),
  stars     = c("*" = 0.05, "**" = 0.01, "***" = 0.001),
  title     = "H3 (reparameterized): geopolitical topic as reference category",
  notes = c(
    "Log-odds coefficients with standard errors in parentheses.",
    "Baseline: domestic expert, geopolitical topic.",
    "Foreign expert coefficient captures the foreign-expert effect in geopolitical topics.",
    "Interaction term shows the additional foreign-expert premium when moving into domestic / other topics.",
    "* p < 0.05, ** p < 0.01, *** p < 0.001"
  ),
  output = "kableExtra"
) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width = FALSE,
    font_size = 12
  ) %>%
  row_spec(3, bold = TRUE, background = "#e8f0f7")  # interaction row


# ── Diagnostic dump ───────────────────────────────────────────────────────

all_h3_strat <- bind_rows(
  lapply(
    list(
      h3_dom_m1 = h3_dom_m1, h3_dom_m2 = h3_dom_m2, h3_dom_m3 = h3_dom_m3,
      h3_geo_m1 = h3_geo_m1, h3_geo_m2 = h3_geo_m2, h3_geo_m3 = h3_geo_m3,
      h3_re_m3  = h3_re_m3,  h3_re_m4  = h3_re_m4
    ),
    tidy
  ),
  .id = "model"
) %>%
  select(model, term, estimate, std.error, p.value)

print(all_h3_strat, n = 100)
```

```{r}
library(marginaleffects)
library(ggplot2)
library(scales)

# ── Model used for predictions ────────────────────────────────────────────
# Original parameterization (domestic-block as baseline) — matches the
# interaction model in the thesis. Predictions are identical regardless of
# which factor level is reference; using this version for continuity.

h3_pred_model <- glm(
  anti_west ~ foreign_expert * topic_block + year,
  data = h3_data,
  family = binomial
)


# ── Predicted probabilities, averaged across observed year distribution ──

preds <- avg_predictions(
  h3_pred_model,
  by = c("foreign_expert", "topic_block")
) %>%
  as_tibble() %>%
  mutate(
    expert_label = factor(
      if_else(foreign_expert == 1, "Foreign expert", "Domestic expert"),
      levels = c("Domestic expert", "Foreign expert")
    ),
    topic_block = factor(
      topic_block,
      levels = c("Domestic / other", "Geopolitical")
    )
  )

print(preds)


# ── Within-topic contrasts (foreign minus domestic, in pp) ───────────────

contrasts_h3 <- avg_comparisons(
  h3_pred_model,
  variables = "foreign_expert",
  by = "topic_block"
) %>%
  as_tibble()

print(contrasts_h3)


# ── Figure ────────────────────────────────────────────────────────────────

p_h3 <- ggplot(
  preds,
  aes(x = topic_block, y = estimate,
      fill = expert_label, group = expert_label)
) +
  geom_col(
    position = position_dodge(width = 0.7),
    width = 0.6
  ) +
  geom_errorbar(
    aes(ymin = conf.low, ymax = conf.high),
    position = position_dodge(width = 0.7),
    width = 0.15,
    linewidth = 0.5,
    colour = "grey25"
  ) +
  geom_text(
    aes(label = sprintf("%.1f%%", estimate * 100)),
    position = position_dodge(width = 0.7),
    vjust = -1.6,
    size = 3.4,
    colour = "grey20"
  ) +
  scale_fill_manual(
    values = c("Domestic expert" = "#8896a3",
               "Foreign expert"  = "#b04a3f"),
    name = NULL
  ) +
  scale_y_continuous(
    labels = percent_format(accuracy = 1),
    expand = expansion(mult = c(0, 0.20))
  ) +
  labs(
    x = NULL,
    y = "Predicted probability of anti-West sentiment"
  ) +
  theme_minimal(base_size = 11) +
  theme(
    panel.grid.major.x = element_blank(),
    panel.grid.minor   = element_blank(),
    legend.position    = "top",
    legend.key.size    = unit(0.4, "cm"),
    axis.text.x        = element_text(size = 11),
    plot.margin        = margin(10, 14, 10, 10)
  )

print(p_h3)


# ── Save (adjust path / dimensions to match your other figures) ──────────

ggsave("fig_h3_predicted_probabilities.png",
      p_h3, width = 5.5, height = 3.6, device = cairo_pdf)
```
