---
title: "Topic modelling 20.04.2026"
author: "Ole Magnus Gaalaas-Hansen"
format: html
editor: visual
---

# Packages

```{r}

library(data.table)
library(stringi)
library(quanteda)
library(topicmodels)
library(stopwords)
library(ggplot2)
library(scales)
```

# LOAD BASE DATASETS

```{r}

# Load datasets from CSV
mentions <- fread(
  "C:/Users/olemga/OneDrive - PRIO/Documents/MA Thesis/Methods/Data/Output/lenta_experts_trf_1999_2024_mentions.csv"
)
articles <- fread(
  "C:/Users/olemga/OneDrive - PRIO/Documents/MA Thesis/Methods/Data/Translated files/lenta_news_1999_2024_translated_all.csv"
)

# Ensure date formats
mentions[, DateParsed := as.Date(DateParsed)]
articles[, date := as.Date(date)]

# Sanity check: ID alignment

all(unique(mentions$row_id) %in% unique(articles$orig_row_id))


```

# a better filter

```{r}

library(data.table)
library(data.table)
setDT(mentions)

# Ensure numeric
mentions[, mention_country_confidence := as.numeric(mention_country_confidence)]

# Keep only usable country evidence
country_evidence <- mentions[
  !is.na(expert_id) &
  mention_country != "Unknown" &
  !is.na(mention_country_confidence)
]

# Expert master country = country with highest confidence
# (If ties, pick the one appearing most often among tied max)
expert_master_country <- country_evidence[
  ,
  {
    maxc <- max(mention_country_confidence, na.rm = TRUE)
    top <- .SD[mention_country_confidence == maxc]
    # tie-break: most frequent among the max-confidence mentions
    best_country <- top[, .N, by = mention_country][order(-N)][1, mention_country]
    .(expert_country_master = best_country, expert_country_maxconf = maxc)
  },
  by = expert_id
]

CONF_THRESH <- 0.70

mentions <- merge(
  mentions,
  expert_master_country,
  by = "expert_id",
  all.x = TRUE
)

mentions[, mention_country_confidence := as.numeric(mention_country_confidence)]

mentions[, country_final := fifelse(
  mention_country != "Unknown" & !is.na(mention_country_confidence) & mention_country_confidence >= CONF_THRESH,
  mention_country,
  expert_country_master
)]

# If still NA, set to Unknown for clarity
mentions[is.na(country_final), country_final := "Unknown"]

# ── NEW: track where country_final came from ───────────────────────────────────
mentions[, country_final_source := fcase(
  
  # Article-level evidence was strong enough on its own
  mention_country != "Unknown" &
    !is.na(mention_country_confidence) &
    mention_country_confidence >= CONF_THRESH,
  "article_level",
  
  # Majority vote kicked in but master country has high confidence
  # (expert appears many times with strong evidence elsewhere in corpus)
  !is.na(expert_country_master) &
    expert_country_maxconf >= CONF_THRESH,
  "majority_vote_high_conf",
  
  # Majority vote kicked in but master country confidence is low
  # (expert rarely appears with strong evidence)
  !is.na(expert_country_master) &
    expert_country_maxconf > 0 &
    expert_country_maxconf < CONF_THRESH,
  "majority_vote_low_conf",
  
  # Majority vote kicked in but confidence is zero
  # (never had any direct evidence anywhere in corpus, pure frequency)
  !is.na(expert_country_master) &
    expert_country_maxconf == 0,
  "majority_vote_zero_conf",
  
  default = "unknown"
)]
# ──────────────────────────────────────────────────────────────────────────────

mentions[, is_foreign_final := country_final != "Russia" & country_final != "Unknown"]

mentions <- mentions[
  person != "Unknown" &
  country_final != "Unknown"
]

# Check distribution
mentions[, .N, by = country_final_source][
  order(-N)
][, pct := N / sum(N) * 100][] %>%
  print()
fwrite(mentions, "mentions_dataset_for_sentiment.csv")

# After the overwrite, effective confidence for each row is:
# - mention_country_confidence if article_level
# - expert_country_maxconf if majority_vote

mentions[, effective_confidence := fcase(
  country_final_source == "article_level",           mention_country_confidence,
  country_final_source == "majority_vote_high_conf", expert_country_maxconf,
  country_final_source == "majority_vote_low_conf",  expert_country_maxconf,
  default = NA_real_
)]

mentions[, conf_tier := fcase(
  effective_confidence == 0,                                        "Low",
  effective_confidence > 0  & effective_confidence < 0.70,         "Medium",
  effective_confidence >= 0.70 & effective_confidence < 0.85,      "High",
  effective_confidence >= 0.85,                                     "Very high",
  default = NA_character_
)]

mentions[, .N, by = .(conf_tier, effective_confidence)][order(effective_confidence)] %>% print()

# Check total rows in mentions after filtering
nrow(mentions)

# And distribution
mentions[, .N, by = conf_tier][order(conf_tier)]
```

### Testing low confidence removal

```{r}
library(dplyr)

cat("Raw mentions (before any filtering):\n")
print(nrow(lenta_experts_trf_1999_2024_mentions))

cat("\nPerson == Unknown:\n")
print(sum(lenta_experts_trf_1999_2024_mentions$person == "Unknown", na.rm = TRUE))

cat("\nPerson is NA:\n")
print(sum(is.na(lenta_experts_trf_1999_2024_mentions$person)))

cat("\nPerson != Unknown and not NA:\n")
n_with_person <- sum(
  lenta_experts_trf_1999_2024_mentions$person != "Unknown" & 
  !is.na(lenta_experts_trf_1999_2024_mentions$person)
)
print(n_with_person)

cat("\nDropped at country stage (had person, not in final dataset):\n")
print(n_with_person - nrow(mentions))

cat("\nFinal dataset:\n")
print(nrow(mentions))

```

```{r}

# Get the dropped rows - had person but not in final dataset
dropped <- lenta_experts_trf_1999_2024_mentions %>%
  filter(person != "Unknown") %>%
  anti_join(mentions, by = "row_id")

cat("Dropped rows - mention_country distribution:\n")
dropped %>%
  count(mention_country) %>%
  mutate(pct = n / sum(n) * 100) %>%
  arrange(desc(n)) %>%
  print(n = 20)

cat("\nDropped rows - mention_country_confidence distribution:\n")
dropped %>%
  count(mention_country_confidence) %>%
  mutate(pct = n / sum(n) * 100) %>%
  arrange(desc(n)) %>%
  print()

cat("\nDropped rows - mention_country_sources distribution:\n")
dropped %>%
  count(mention_country_sources) %>%
  mutate(pct = n / sum(n) * 100) %>%
  arrange(desc(n)) %>%
  print(n = 20)

cat("Difference between named-person rows and dropped + final:\n")
print(119456 - 37101 - 76938)

cat("Top 30 most frequent persons in dropped rows:\n")
dropped %>%
  count(person) %>%
  arrange(desc(n)) %>%
  print(n = 30)

cat("\nRandom sample of 30 names from dropped rows:\n")
dropped %>%
  distinct(person) %>%
  sample_n(30) %>%
  print()
```

# FILTER VALID EXPERT MENTIONS

# DIRECT MERGE VIA ROW_ID (NO STRING MATCHING)

```{r}

final_data <- merge(
  mentions,
  articles[, .(orig_row_id, text_en, title_en, date)],
  by.x = "row_id",
  by.y = "orig_row_id",
  all.x = TRUE
)



```

# BUILD ARTICLE-LEVEL DATASET

```{r}

article_level <- final_data[
  ,
  .(
    DateParsed = first(DateParsed),
    text_en    = first(text_en),
    title_en   = first(title_en),
    n_mentions = .N,
    mention_sentences = paste(unique(sentence), collapse = " ||| ")
  ),
  by = row_id
]

article_level[, doc_text := paste(title_en, text_en, sep = ". ")]

fwrite(article_level, "article_level_clean.csv")
```

# HARD-NEWS TOPIC MODELLING (TEST 4 CLEAN VERSION)

## Hard-News Filtering

```{r}
#| eval: false

article_level[, title_lc := tolower(title_en)]

exclude_pat <- paste0(
  "(",
  paste(c(
    "match","team","league","football","hockey","film","movie","actor",
    "concert","weather","forecast","recipe","diet","fashion","tips"
  ), collapse="|"),
  ")"
)

article_level <- article_level[!stri_detect_regex(title_lc, exclude_pat)]
article_level[, title_lc := NULL]
```

## Tokenization

```{r}
#| eval: false

corp <- corpus(article_level$doc_text)

toks <- tokens(
  corp,
  remove_punct = TRUE,
  remove_symbols = TRUE,
  remove_numbers = TRUE
)

toks <- tokens_tolower(toks)

news_stopwords <- c(
  "said","according","earlier","new","one","two",
  "also","can","may","year","years","reported"
)

toks <- tokens_remove(toks, c(stopwords("en"), news_stopwords))

keep_docs <- lengths(toks) > 40
toks <- toks[keep_docs]
article_level <- article_level[keep_docs]
```

## DFM + Trim

```{r}
#| eval: false

dfm_all <- dfm_trim(
  dfm_all,
  min_docfreq = 30,
  max_docfreq = 0.6 * ndoc(dfm_all),
  docfreq_type = "count"
)

non_empty <- ntoken(dfm_all) > 0

dfm_all <- dfm_all[non_empty, ]

article_level <- article_level[non_empty]
```

New filtering with better stopwords:

```{r}

# ----------------------------------------------------------
# 1) HARD-NEWS FILTER (Title-based exclusion)
# ----------------------------------------------------------

article_level[, title_lc := tolower(title_en)]

exclude_pat <- paste0(
  "(",
  paste(c(
    # sports
    "match","matches","team","club","coach","league","championship","tournament","football","soccer",
    "hockey","nba","nhl","fifa","olympic","olympics","race","grand prix",
    # culture/entertainment
    "film","movie","cinema","actor","actress","director","singer","concert","album","tv","series",
    "show","theater","theatre","book","novel","literature","festival","premiere","museum",
    # weather
    "weather","forecast","temperature","storm","snow","rain","wind","heat","cold",
    # lifestyle / advice
    "recipe","cook","diet","fitness","beauty","fashion","psychologist","relationship",
    "children","parent","pregnan","doctor recommends","tips","how to"
  ), collapse = "|"),
  ")"
)

article_level <- article_level[!stri_detect_regex(title_lc, exclude_pat)]
article_level[, title_lc := NULL]

gc()

# ----------------------------------------------------------
# 2) Tokenization
# ----------------------------------------------------------

corp <- corpus(article_level$doc_text)

toks <- tokens(
  corp,
  remove_punct = TRUE,
  remove_symbols = TRUE,
  remove_numbers = TRUE
)

toks <- tokens_tolower(toks)

# ----------------------------------------------------------
# 3) Stopwords (stronger cleaning)
# ----------------------------------------------------------

news_stopwords <- c(
  "said","according","earlier","new","one","two","first",
  "also","can","may","time","year","years","reported",
  "found","known","made","way","need","even","many","get","help",
  "people","url","now","however","even","still","today"
)

expert_role_stopwords <- c(
  "expert","experts","specialist","specialists","professor","professors",
  "doctor","doctors","scientist","scientists","researcher","researchers",
  "analyst","analysts","economist","economists","lawyer","lawyers",
  "institute","university","academy","center","centre","department",
  "ministry","director","head"
)

reporting_verbs <- c(
  "said","told","explained","noted","added","stated","called",
  "announced","commented","emphasized","pointed","claimed"
)

toks <- tokens_remove(
  toks,
  c(stopwords("en"),
    news_stopwords,
    expert_role_stopwords,
    reporting_verbs)
)

# Remove ultra-short tokens
toks <- tokens_keep(toks, pattern = "^[a-z]{3,}$", valuetype = "regex")

# ----------------------------------------------------------
# 4) Remove short documents AFTER cleaning
# ----------------------------------------------------------

keep_docs <- lengths(toks) > 50

toks <- toks[keep_docs]
article_level <- article_level[keep_docs]

gc()

# ----------------------------------------------------------
# 5) DFM + Trim
# ----------------------------------------------------------

dfm_all <- dfm(toks)

dfm_all <- dfm_trim(
  dfm_all,
  min_docfreq = 30,
  max_docfreq = 0.6 * ndoc(dfm_all),
  docfreq_type = "count"
)

non_empty <- ntoken(dfm_all) > 0
dfm_all <- dfm_all[non_empty, ]
article_level <- article_level[non_empty]

gc()

```

## LDA

```{r}
dtm <- convert(dfm_all, to = "topicmodels")

K <- 15
set.seed(123)

lda_fit <- LDA(
  dtm,
  k = K,
  method = "Gibbs",
  control = list(iter=1200, burnin=200, thin=100, seed=123)
)

# Save model and vocabulary for robustness check
saveRDS(lda_fit,          "lda_fit_k15.rds")
saveRDS(featnames(dfm_all), "lda_vocab_k15.rds")

theta <- posterior(lda_fit)$topics
theta_dt <- as.data.table(theta)
setnames(theta_dt, paste0("topic_", 1:K))

hardnews_topics_k15_fast <- cbind(
  article_level[, .(row_id, DateParsed, n_mentions)],
  theta_dt
)
top_terms <- terms(lda_fit, 15)
print(top_terms)

setnames(hardnews_topics_k15_fast,
         old = paste0("topic_", 1:15),
         new = c(
           "macro_economy",
           "media_society",
           "general_news",
           "housing_market",
           "opinion_discourse",
           "covid_health",
           "development_education",
           "energy_sanctions",
           "military_technology",
           "information_services",
           "kremlin_governance",
           "courts_crime",
           "regions_local",
           "ukraine_war",
           "international_geopolitics"
         ))

fwrite(hardnews_topics_k15_fast, "hardnews_topics_k15_fast.csv")
```

# ROBUSTNESS CHECK: DROPPED EXPERTS

Test whether articles containing experts with no country cues have a similar topic distribution to articles with confirmed domestic (Russian) experts. If they do, the assumption that dropped experts are mostly Russian holds.

## Build article-level dataset for dropped mentions

```{r}

topic_cols <- c(
  "macro_economy", "media_society", "general_news",
  "housing_market", "opinion_discourse", "covid_health",
  "development_education", "energy_sanctions", "military_technology",
  "information_services", "kremlin_governance", "courts_crime",
  "regions_local", "ukraine_war", "international_geopolitics"
)

dropped_dt <- as.data.table(dropped)

# Join dropped mentions with full article text
dropped_articles <- merge(
  dropped_dt[, .(row_id)],
  articles[, .(orig_row_id, text_en, title_en, date)],
  by.x = "row_id",
  by.y = "orig_row_id",
  all.x = TRUE
)

# Deduplicate to article level
dropped_al <- dropped_articles[
  !is.na(text_en),
  .(
    DateParsed = first(date),
    text_en    = first(text_en),
    title_en   = first(title_en)
  ),
  by = row_id
]

dropped_al[, doc_text := paste(title_en, text_en, sep = ". ")]

cat("Dropped articles with full text:", nrow(dropped_al), "\n")
```

## Apply same preprocessing pipeline

```{r}

# Hard-news filter (same exclude_pat as above)
dropped_al[, title_lc := tolower(title_en)]
dropped_al <- dropped_al[!stri_detect_regex(title_lc, exclude_pat)]
dropped_al[, title_lc := NULL]

corp_d <- corpus(dropped_al$doc_text)

toks_d <- tokens(
  corp_d,
  remove_punct   = TRUE,
  remove_symbols = TRUE,
  remove_numbers = TRUE
)

toks_d <- tokens_tolower(toks_d)

toks_d <- tokens_remove(
  toks_d,
  c(stopwords("en"), news_stopwords, expert_role_stopwords, reporting_verbs)
)

toks_d <- tokens_keep(toks_d, pattern = "^[a-z]{3,}$", valuetype = "regex")

keep_d <- lengths(toks_d) > 50
toks_d <- toks_d[keep_d]
dropped_al <- dropped_al[keep_d]

cat("Dropped articles after preprocessing:", nrow(dropped_al), "\n")
```

## Align DFM to original vocabulary and infer topics

```{r}

dfm_d <- dfm(toks_d)

# Align to the vocabulary the LDA was trained on
dfm_d <- dfm_match(dfm_d, featnames(dfm_all))

non_empty_d <- ntoken(dfm_d) > 0
dfm_d    <- dfm_d[non_empty_d, ]
dropped_al <- dropped_al[non_empty_d]

cat("Dropped articles with non-empty DFM:", nrow(dropped_al), "\n")

dtm_d <- convert(dfm_d, to = "topicmodels")

# Infer topic probabilities using the saved model
theta_d <- posterior(lda_fit, newdata = dtm_d)$topics

theta_d_dt <- as.data.table(theta_d)
setnames(theta_d_dt, paste0("topic_", 1:K))
setnames(theta_d_dt,
         old = paste0("topic_", 1:K),
         new = topic_cols)

dropped_topics <- cbind(dropped_al[, .(row_id, DateParsed)], theta_d_dt)

fwrite(dropped_topics, "dropped_topics_k15.csv")
```

## Compare: domestic vs. dropped topic distributions

```{r}

# Domestic = Russian experts (is_foreign_final == FALSE)
domestic_row_ids <- mentions[is_foreign_final == FALSE, unique(row_id)]
domestic_topics  <- hardnews_topics_k15_fast[row_id %in% domestic_row_ids]

mean_domestic <- colMeans(domestic_topics[, ..topic_cols])
mean_dropped  <- colMeans(dropped_topics[, ..topic_cols])

comparison <- data.table(
  topic    = topic_cols,
  domestic = mean_domestic,
  dropped  = mean_dropped,
  diff     = mean_dropped - mean_domestic,
  abs_diff = abs(mean_dropped - mean_domestic)
)

cat("Topic distribution comparison (domestic vs dropped):\n")
print(comparison[order(-abs_diff)])

cat("\nCorrelation between mean topic shares:", cor(mean_domestic, mean_dropped), "\n")
cat("Max absolute difference:", max(comparison$abs_diff), "\n")
```

## Visualisation

```{r}

library(tidyr)

comp_long <- melt(
  comparison,
  id.vars      = "topic",
  measure.vars = c("domestic", "dropped"),
  variable.name = "group",
  value.name    = "mean_share"
)

comp_long[, group := factor(group,
  levels = c("domestic", "dropped"),
  labels = c("Domestic experts (Russia)", "Dropped (unknown country)")
)]

ggplot(comp_long, aes(x = reorder(topic, mean_share), y = mean_share, fill = group)) +
  geom_col(position = "dodge") +
  coord_flip() +
  scale_fill_manual(values = c("Domestic experts (Russia)" = "#2166AC",
                               "Dropped (unknown country)"  = "#D1495B")) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 0.1)) +
  labs(
    title    = "Topic distribution: Domestic vs. Dropped experts",
    subtitle = "Mean topic share per article group (LDA k = 15)",
    x        = NULL,
    y        = "Mean topic share",
    fill     = NULL
  ) +
  theme_minimal(base_size = 12) +
  theme(legend.position = "bottom")

ggsave("topic_comparison_domestic_vs_dropped.png", width = 9, height = 6, dpi = 150)
```
