---
title: "Topic Modelling and Dataset Merging"
author: "Ole Magnus"
format: html
editor: visual
---

# Packages

```{r}
library(data.table)
library(stringi)
library(quanteda)
library(topicmodels)
library(stopwords)
library(dplyr)
library(ggplot2)
```

# Load Base Datasets

```{r}
mentions  <- as.data.table(lenta_experts_trf_1999_2024_mentions)
articles  <- as.data.table(lenta_news_1999_2024_translated_all)

mentions[, DateParsed := as.Date(DateParsed)]
articles[, date := as.Date(date)]

# Sanity check: ID alignment
all(unique(mentions$row_id) %in% unique(articles$orig_row_id))
```

# Filter Valid Expert Mentions

Assign each expert a master country based on the highest-confidence mention across the full corpus, then apply a confidence threshold at the mention level.

```{r}
setDT(mentions)

mentions[, mention_country_confidence := as.numeric(mention_country_confidence)]

# Expert master country = country with highest confidence across all mentions
country_evidence <- mentions[
  !is.na(expert_id) &
  mention_country != "Unknown" &
  !is.na(mention_country_confidence)
]

expert_master_country <- country_evidence[
  ,
  {
    maxc <- max(mention_country_confidence, na.rm = TRUE)
    top  <- .SD[mention_country_confidence == maxc]
    best_country <- top[, .N, by = mention_country][order(-N)][1, mention_country]
    .(expert_country_master = best_country, expert_country_maxconf = maxc)
  },
  by = expert_id
]

CONF_THRESH <- 0.70

mentions <- merge(mentions, expert_master_country, by = "expert_id", all.x = TRUE)

mentions[, mention_country_confidence := as.numeric(mention_country_confidence)]

# Resolve final country per mention
mentions[, country_final := fifelse(
  mention_country != "Unknown" & !is.na(mention_country_confidence) & mention_country_confidence >= CONF_THRESH,
  mention_country,
  expert_country_master
)]

mentions[is.na(country_final), country_final := "Unknown"]

# Track the source of country_final
mentions[, country_final_source := fcase(
  mention_country != "Unknown" &
    !is.na(mention_country_confidence) &
    mention_country_confidence >= CONF_THRESH,
  "article_level",
  !is.na(expert_country_master) & expert_country_maxconf >= CONF_THRESH,
  "majority_vote_high_conf",
  !is.na(expert_country_master) & expert_country_maxconf > 0 & expert_country_maxconf < CONF_THRESH,
  "majority_vote_low_conf",
  !is.na(expert_country_master) & expert_country_maxconf == 0,
  "majority_vote_zero_conf",
  default = "unknown"
)]

mentions[, is_foreign_final := country_final != "Russia" & country_final != "Unknown"]

# Drop rows without a usable person or country
mentions <- mentions[
  person != "Unknown" &
  country_final != "Unknown"
]

# Distribution of source types
mentions[, .N, by = country_final_source][order(-N)][, pct := N / sum(N) * 100][] %>% print()

fwrite(mentions, "mentions_dataset_for_sentiment.csv")

# Effective confidence and tier labels
mentions[, effective_confidence := fcase(
  country_final_source == "article_level",           mention_country_confidence,
  country_final_source == "majority_vote_high_conf", expert_country_maxconf,
  country_final_source == "majority_vote_low_conf",  expert_country_maxconf,
  default = NA_real_
)]

mentions[, conf_tier := fcase(
  effective_confidence == 0,                                    "Low",
  effective_confidence > 0  & effective_confidence < 0.70,     "Medium",
  effective_confidence >= 0.70 & effective_confidence < 0.85,  "High",
  effective_confidence >= 0.85,                                 "Very high",
  default = NA_character_
)]

mentions[, .N, by = .(conf_tier, effective_confidence)][order(effective_confidence)] %>% print()

cat("Final dataset rows:", nrow(mentions), "\n")
mentions[, .N, by = conf_tier][order(conf_tier)]
```

# Merge Articles and Mentions

Direct merge via `row_id` — no string matching.

```{r}
final_data <- merge(
  mentions,
  articles[, .(orig_row_id, text_en, title_en, date)],
  by.x = "row_id",
  by.y = "orig_row_id",
  all.x = TRUE
)

# Full outer merge for validation
final_data_verify <- merge(
  articles[, .(orig_row_id, text_en, title_en, date)],
  mentions,
  by.x = "orig_row_id",
  by.y = "row_id",
  all.x = TRUE
)

final_data <- final_data[!is.na(text_en)]
```

# Build Article-Level Dataset

Collapse mention-level rows to one row per article.

```{r}
article_level <- final_data[
  ,
  .(
    DateParsed        = first(DateParsed),
    text_en           = first(text_en),
    title_en          = first(title_en),
    n_mentions        = .N,
    mention_sentences = paste(unique(sentence), collapse = " ||| ")
  ),
  by = row_id
]

article_level[, doc_text := paste(title_en, text_en, sep = ". ")]

fwrite(article_level, "article_level_clean.csv")
```

# Hard-News Topic Modelling

## Hard-News Filtering

Remove soft-news articles (sports, culture, weather, lifestyle) by title keyword.

```{r}
article_level[, title_lc := tolower(title_en)]

exclude_pat <- paste0(
  "(",
  paste(c(
    # sports
    "match","matches","team","club","coach","league","championship","tournament","football","soccer",
    "hockey","nba","nhl","fifa","olympic","olympics","race","grand prix",
    # culture/entertainment
    "film","movie","cinema","actor","actress","director","singer","concert","album","tv","series",
    "show","theater","theatre","book","novel","literature","festival","premiere","museum",
    # weather
    "weather","forecast","temperature","storm","snow","rain","wind","heat","cold",
    # lifestyle / advice
    "recipe","cook","diet","fitness","beauty","fashion","psychologist","relationship",
    "children","parent","pregnan","doctor recommends","tips","how to"
  ), collapse = "|"),
  ")"
)

article_level <- article_level[!stri_detect_regex(title_lc, exclude_pat)]
article_level[, title_lc := NULL]

gc()
```

## Tokenization

```{r}
corp <- corpus(article_level$doc_text)

toks <- tokens(
  corp,
  remove_punct   = TRUE,
  remove_symbols = TRUE,
  remove_numbers = TRUE
)

toks <- tokens_tolower(toks)

news_stopwords <- c(
  "said","according","earlier","new","one","two","first",
  "also","can","may","time","year","years","reported",
  "found","known","made","way","need","even","many","get","help",
  "people","url","now","however","even","still","today"
)

expert_role_stopwords <- c(
  "expert","experts","specialist","specialists","professor","professors",
  "doctor","doctors","scientist","scientists","researcher","researchers",
  "analyst","analysts","economist","economists","lawyer","lawyers",
  "institute","university","academy","center","centre","department",
  "ministry","director","head"
)

reporting_verbs <- c(
  "said","told","explained","noted","added","stated","called",
  "announced","commented","emphasized","pointed","claimed"
)

toks <- tokens_remove(
  toks,
  c(stopwords("en"), news_stopwords, expert_role_stopwords, reporting_verbs)
)

# Remove ultra-short tokens
toks <- tokens_keep(toks, pattern = "^[a-z]{3,}$", valuetype = "regex")

# Drop documents that are too short after cleaning
keep_docs <- lengths(toks) > 50
toks          <- toks[keep_docs]
article_level <- article_level[keep_docs]

gc()
```

## DFM and Trim

```{r}
dfm_all <- dfm(toks)

dfm_all <- dfm_trim(
  dfm_all,
  min_docfreq = 30,
  max_docfreq = 0.6 * ndoc(dfm_all),
  docfreq_type = "count"
)

non_empty     <- ntoken(dfm_all) > 0
dfm_all       <- dfm_all[non_empty, ]
article_level <- article_level[non_empty]

gc()
```

## LDA Topic Model (K = 15)

```{r}
dtm <- convert(dfm_all, to = "topicmodels")

K <- 15
set.seed(123)

lda_fit <- LDA(
  dtm,
  k      = K,
  method = "Gibbs",
  control = list(iter = 1200, burnin = 200, thin = 100, seed = 123)
)

theta    <- posterior(lda_fit)$topics
theta_dt <- as.data.table(theta)
setnames(theta_dt, paste0("topic_", 1:K))

hardnews_topics_k15_fast <- cbind(
  article_level[, .(row_id, DateParsed, n_mentions)],
  theta_dt
)

print(terms(lda_fit, 15))

setnames(
  hardnews_topics_k15_fast,
  old = paste0("topic_", 1:15),
  new = c(
    "macro_economy",
    "media_society",
    "general_news",
    "housing_market",
    "opinion_discourse",
    "covid_health",
    "development_education",
    "energy_sanctions",
    "military_technology",
    "information_services",
    "kremlin_governance",
    "courts_crime",
    "regions_local",
    "ukraine_war",
    "international_geopolitics"
  )
)

fwrite(hardnews_topics_k15_fast, "hardnews_topics_k15_fast.csv")
```

# Merge Topics and Sentiment into Master Dataset

`mentions_directed_sentiment_full` is loaded from the sentiment analysis pipeline (run separately on the context window CSV produced above).

```{r}
sentiment <- mentions_directed_sentiment_full
topics    <- as.data.table(hardnews_topics_k15_fast)

master_dataset <- merge(sentiment, topics, by = "row_id", all.x = TRUE)

topic_cols <- c(
  "courts_crime", "covid_health", "development_education", "energy_sanctions",
  "general_news", "housing_market", "information_services", "international_geopolitics",
  "kremlin_governance", "macro_economy", "media_society", "military_technology",
  "opinion_discourse", "regions_local", "ukraine_war"
)

# Replace missing topic weights with 0 (articles outside the LDA corpus)
master_dataset[topic_cols] <- lapply(master_dataset[topic_cols], function(x) {
  x[is.na(x)] <- 0; x
})

master_dataset$dominant_topic <- topic_cols[
  max.col(master_dataset[topic_cols], ties.method = "first")
]

master_dataset$dominant_topic[rowSums(master_dataset[topic_cols]) == 0] <- "no_topic"

# Broad topic groups
master_dataset$topic_group <- "other"

master_dataset$topic_group[
  master_dataset$dominant_topic %in%
    c("ukraine_war", "international_geopolitics", "military_technology", "energy_sanctions")
] <- "geopolitics"

master_dataset$topic_group[
  master_dataset$dominant_topic %in% c("macro_economy", "housing_market")
] <- "economy"

master_dataset$topic_group[
  master_dataset$dominant_topic %in%
    c("kremlin_governance", "opinion_discourse", "media_society")
] <- "politics"

master_dataset$topic_group[master_dataset$dominant_topic == "courts_crime"] <- "crime"

table(master_dataset$topic_group)
```

# Standardize and Clean Master Dataset

```{r}
# Lowercase all column names
names(master_dataset) <- tolower(names(master_dataset))

# Clean date: resolve duplicated DateParsed columns from the merge
master_dataset$date <- as.Date(master_dataset$dateparsed.x)
master_dataset$dateparsed.x <- NULL
master_dataset$dateparsed.y <- NULL

master_dataset$year <- as.integer(format(master_dataset$date, "%Y"))

# Rename key variables
names(master_dataset)[names(master_dataset) == "sentence"]        <- "mention_sentence"
names(master_dataset)[names(master_dataset) == "country_final"]   <- "expert_country"
names(master_dataset)[names(master_dataset) == "is_foreign_final"] <- "foreign_expert"
names(master_dataset)[names(master_dataset) == "any_anti_west"]   <- "anti_west"
names(master_dataset)[names(master_dataset) == "any_anti_russia"] <- "anti_russia"
names(master_dataset)[names(master_dataset) == "any_anti_ukraine"] <- "anti_ukraine"

# Re-apply topic columns (now lowercase names) and re-derive dominant topic
topic_cols <- c(
  "courts_crime", "covid_health", "development_education", "energy_sanctions",
  "general_news", "housing_market", "information_services", "international_geopolitics",
  "kremlin_governance", "macro_economy", "media_society", "military_technology",
  "opinion_discourse", "regions_local", "ukraine_war"
)

master_dataset[topic_cols] <- lapply(master_dataset[topic_cols], function(x) {
  x[is.na(x)] <- 0; x
})

master_dataset$dominant_topic <- topic_cols[
  max.col(master_dataset[topic_cols], ties.method = "first")
]
master_dataset$dominant_topic[rowSums(master_dataset[topic_cols]) == 0] <- "no_topic"

# Narrative asymmetry index
master_dataset$anti_west_vs_russia <- master_dataset$anti_west - master_dataset$anti_russia

# Proper types
master_dataset$foreign_expert  <- as.integer(master_dataset$foreign_expert)
master_dataset$topic_group     <- factor(master_dataset$topic_group)
master_dataset$dominant_topic  <- factor(master_dataset$dominant_topic)

# Save
write.csv(
  master_dataset,
  "C:/Users/olemga/OneDrive - PRIO/Documents/MA Thesis/Methods/Data/expert_topic_sentiment_master.csv",
  row.names = FALSE
)

cat("Master dataset saved. Rows:", nrow(master_dataset), "\n")
```
